\section{CTYPEDEFINE Define C Type}

\subsection{Usage}

The \verb|ctypedefine| function allows you to define C types for use
with FreeMat.  Three variants of C types can be used.  You can
use structures, enumerations, and aliases (typedefs).  All three are defined
through a single function \verb|ctypedefine|.  The general syntax for
its use is
\begin{verbatim}
  ctypedefine(typeclass,typename,...)
\end{verbatim}
where \verb|typeclass| is the variant of the type (legal values are
\verb|'struct'|, \verb|'alias'|, \verb|'enum'|).  The second argument is the
name of the C type.  The remaining arguments depend on what the
class of the typedef is.  

To define a C structure, use the \verb|'struct'| type class.  The usage
in this case is:
\begin{verbatim}
  ctypedefine('struct',typename,field1,type1,field2,type2,...)
\end{verbatim}
The argument \verb|typename| must be a valid identifier string.  Each of
of the \verb|field| arguments is also a valid identifier string that 
describe in order, the elements of the C structure.  The \verb|type| arguments
are \verb|typespecs|.  They can be of three types:
\begin{itemize}
\item  Built in types, e.g. \verb|'uint8'| or \verb|'double'| to name a couple of
      examples.

\item  C types that have previously been defined with a call to 
      \verb|ctypedefine|, e.g. \verb|'mytype'| where \verb|'mytype'| has already been
      defined through a call to \verb|ctypedefine|.

\item  Arrays of either built in types or previously defined C types
      with the length of the array coded as an integer in square brackets, 
      for example: \verb|'uint8[10]'| or \verb|'double[1000]'|.

\end{itemize}

To define a C enumeration, use the \verb|'enum'| type class.  The usage
in this case is:
  ctypedefine('enum',typename,name1,value1,name2,value2,...)
@]
The argument \verb|typename| must be a valid identifier string.  Each of the
\verb|name| arguments must also be valid identifier strings that describe
the possible values that the enumeration can take an, and their corresponding
integer values.  Note that the names should be unique.  The behavior of
the various \verb|cenum| functions is undefined if the names are not unique.

To define a C alias (or typedef), use the following form of \verb|ctypedefine|:
\begin{verbatim}
  ctypedefine('alias',typename,aliased_typename)
\end{verbatim}
where \verb|aliased\_typename| is the type that is being aliased to.
