\section{FIGUREPROPERTIES Figure Object Properties}

\subsection{Usage}

Below is a summary of the properties for the axis.
\begin{itemize}
\item  \verb|alphamap| - \verb|vector| - Contains the alpha (transparency) map for the
 figure.  If this is set to a scalar, then all values are mapped to the same 
 transparency.  It defaults to \verb|1|, which is all values being fully opaque.  
 If you set this to a vector, the values of graphics objects will be mapped to 
 different transparency values, based on the setting of their \verb|alphadatamapping|
 property.

\item  \verb|color| - \verb|colorspec| - The background color of the figure (defaults to a
 gray \verb|[0.6,0.6,0.6]|).  During printing, this color is set to white, and then
 is restored.

\item  \verb|colormap| - \verb|color vector| - an \verb|N x 3| matrix of RGB values that
 specifies the colormap for the figure.  Defaults to an \verb|HSV| map.  

\item  \verb|children| - \verb|handle vector| - the handles for objects that are children
 of this figure.  These should be axis objects.

\item  \verb|currentaxes| - \verb|handle| - the handle for the current axes.  Also returned
 by \verb|gca|.

\item  \verb|doublebuffer| - Not used.

\item  \verb|parent| -  Not used.

\item  \verb|position| - Not used.

\item  \verb|type| - \verb|string| - returns the string \verb|'figure'|.

\item  \verb|userdata| - \verb|array| - arbitrary array you can use to store data associated
 with the figure.

\item  \verb|nextplot| - \verb|{'add','replace','replacechildren'}| - If set to \verb|'add'| then
 additional axes are added to the list of children for the current figure.  If set to 
 \verb|'replace'|, then a new axis replaces all of the existing children.

\item  \verb|figsize| - \verb|two vector| - the size of the figure window in pixels (width x height).

\item  \verb|renderer| - \verb|{'painters','opengl'}| - When set to \verb|'painters'| drawing is based
 on the Qt drawing methods (which can handle flat shading of surfaces with transparency).
 If you set the renderer to \verb|'opengl'| then OpenGL is used for rendering.  Support for 
 OpenGL is currently in the alpha stage, and FreeMat does not enable it automatically.
 You can set the renderer mode to \verb|'opengl'| manually to experiment.  Also, OpenGL 
 figures cannot be printed yet.

\end{itemize}
