\section{LINEPROPERTIES Line Series Object Properties}

\subsection{Usage}

Below is a summary of the properties for a line series.
\begin{itemize}
\item  \verb|color| - \verb|colorspec| - The color that is used to 
 draw the line.

\item  \verb|children| - Not used.

\item  \verb|displayname| - The name of this line series as it
 appears in a legend.

\item  \verb|linestyle| - \verb|{'-','--',':','-.','none'}| - The style of the line.

\item  \verb|linewidth| - \verb|scalar| - The width of the line.

\item  \verb|marker| - \verb|{'+','o','*','.','x','square','s','diamond','d','\^','v','>','<'}| - 
 The marker for data points on the line.  Some of these are redundant, as \verb|'square'| 
 \verb|'s'| are synonyms, and \verb|'diamond'| and \verb|'d'| are also synonyms.

\item  \verb|markeredgecolor| - \verb|colorspec| - The color used to draw the marker.  For some
 of the markers (circle, square, etc.) there are two colors used to draw the marker.
 This property controls the edge color (which for unfilled markers) is the primary
 color of the marker.

\item  \verb|markerfacecolor| - \verb|colorspec| - The color used to fill the marker.  For some
 of the markers (circle, square, etc.) there are two colors used to fill the marker.

\item  \verb|markersize| - \verb|scalar| - Control the size of the marker.  Defaults to 6, which
 is effectively the radius (in pixels) of the markers.

\item  \verb|parent| - \verb|handle| - The axis that contains this object.

\item  \verb|tag| - \verb|string| - A string that can be used to tag the object.

\item  \verb|type| - \verb|string| - Returns the string \verb|'line'|.

\item  \verb|visible| - \verb|{'on','off'}| - Controls visibility of the the line.

\item  \verb|xdata| - \verb|vector| - Vector of x coordinates of points on the line.  Must be
 the same size as the \verb|ydata| and \verb|zdata| vectors.

\item  \verb|ydata| - \verb|vector| - Vector of y coordinates of points on the line.  Must be
 the same size as the \verb|xdata| and \verb|zdata| vectors.

\item  \verb|zdata| - \verb|vector| - Vector of z coordinates of points on the line.  Must be
 the same size as the \verb|xdata| and \verb|ydata| vectors.

\item  \verb|xdatamode| - \verb|{'auto','manual'}| - When set to \verb|'auto'| FreeMat will autogenerate
 the x coordinates for the points on the line.  These values will be \verb|1,..,N| where
 \verb|N| is the number of points in the line.

\item  \verb|userdata| - \verb|array| - Available to store any variable you
 want in the handle object.

\end{itemize}
