\section{IMAGEPROPERTIES Image Object Properties}

\subsection{Usage}

Below is a summary of the properties for the axis.
\begin{itemize}
\item  \verb|alphadata| - \verb|vector| - This is a vector that
 should contain as many elements as the image data itself \verb|cdata|,
 or a single scalar.  For a single scalar, all values of the image
 take on the same transparency.  Otherwise, the transparency of
 each pixel is determined by the corresponding value from the \verb|alphadata|
 vector.

\item  \verb|alphadatamapping| - \verb|{'scaled','direct','none'}| - For \verb|none|
 mode (the default), no transparency is applied to the data.  For \verb|direct|
 mode, the vector \verb|alphadata| contains values between @[0,M-1]| where
 \verb|M| is the length of the alpha map stored in the figure.  For \verb|scaled|
 mode, the \verb|alim| vector for the figure is used to linearly rescale the 
 alpha data prior to lookup in the alpha map. 

\item  \verb|cdata| - \verb|array| - This is either a \verb|M x N| array or an 
  \verb|M x N x 3| array.  If the data is \verb|M x N| the image is a scalar
 image (indexed mode), where the color associated with each image pixel
 is computed using the colormap and the \verb|cdatamapping| mode.  If the
 data is \verb|M x N x 3| the image is assumed to be in RGB mode, and the
 colorpanes are taken directly from \verb|cdata| (the colormap is ignored).
 Note that in this case, the data values must be between @[0,1]| for each
 color channel and each pixel.

\item  \verb|cdatamapping| - \verb|{'scaled','direct'}| - For \verb|scaled| (the
 default), the pixel values are scaled using the \verb|clim| vector for the
 figure prior to looking up in the colormap.  For \verb|direct| mode, the
 pixel values must be in the range \verb|[0,N-1| where \verb|N| is the number of
 colors in the colormap if the data is integer type.  For floating point
 data types, values must be in the range \verb|[1,N]|.

\item  \verb|children| - Not used.

\item  \verb|parent| - \verb|handle| - The axis containing the image.

\item  \verb|tag| - \verb|string| - You can set this to any string you want.

\item  \verb|type| - \verb|string| - Set to the string \verb|'image'|.

\item  \verb|xdata| - \verb|two vector| - contains the x coordinates of the
 first and last column (respectively).  Defaults to \verb|[1,C]| where
 \verb|C| is the number of columns in the image.

\item  \verb|ydata| - \verb|two vector| - contains the y coordinates of the
 first and last row (respectively).  Defaults to \verb|[1,R]| where
 \verb|R| is the number of rows in the image.

\item  \verb|userdata| - \verb|array| - Available to store any variable you
 want in the handle object.

\item  \verb|visible| - \verb|{'on','off'}| - Controls whether the image is
 visible or not.

\end{itemize}
