\section{UINT32 Convert to Unsigned 32-bit Integer}

\subsection{Usage}

Converts the argument to an unsigned 32-bit Integer.  The syntax
for its use is
\begin{verbatim}
   y = uint32(x)
\end{verbatim}
where \verb|x| is an \verb|n|-dimensional numerical array.  Conversion
follows saturation rules (e.g., if \verb|x| is outside the normal
range for an unsigned 32-bit integer of \verb|[0,4294967295]|, it is
truncated to that range. Note that both \verb|NaN| and \verb|Inf| both map to 0.
\subsection{Example}

The following piece of code demonstrates several uses of \verb|uint32|.
\begin{verbatim}
--> uint32(200)

ans = 
 200 
\end{verbatim}
In the next example, an integer outside the range of the type is passed in.  
The result is truncated to the maximum value of the data type.
\begin{verbatim}
--> uint32(40e9)

ans = 
 4294967295 
\end{verbatim}
In the next example, a negative integer is passed in.  The result is 
truncated to zero.
\begin{verbatim}
--> uint32(-100)

ans = 
 0 
\end{verbatim}
In the next example, a positive double precision argument is passed in.  
The result is the unsigned integer that is closest to the argument.
\begin{verbatim}
--> uint32(pi)

ans = 
 3 
\end{verbatim}
In the next example, a complex argument is passed in.  The result is the 
complex unsigned integer that is closest to the argument.
\begin{verbatim}
--> uint32(5+2*i)

ans = 
   5.0000 +  2.0000i 
\end{verbatim}
In the next example, a string argument is passed in.  The string argument 
is converted into an integer array corresponding to the ASCII values of each character.
\begin{verbatim}
--> uint32('helo')

ans = 
 104 101 108 111 
\end{verbatim}
In the last example, a cell-array is passed in.  For cell-arrays and 
structure arrays, the result is an error.
\begin{verbatim}
--> uint32({4})
Error: Cannot perform type conversions with this type
\end{verbatim}
