\section{vtkAssemblyNode}

\subsection{Usage}

 vtkAssemblyNode represents a node in an assembly. It is used by
 vtkAssemblyPath to create hierarchical assemblies of props. The
 props can be either 2D or 3D.

 An assembly node refers to a vtkProp, and possibly a vtkMatrix4x4.
 Nodes are used by vtkAssemblyPath to build fully evaluated path
 (matrices are concatenated through the path) that is used by picking
 and other operations involving assemblies.

To create an instance of class vtkAssemblyNode, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkAssemblyNode
\end{verbatim}
\subsection{Methods}

The class vtkAssemblyNode has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkAssemblyNode class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkAssemblyNode = obj.NewInstance ()|

\item  \verb|vtkAssemblyNode = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetViewProp (vtkProp prop)| -  Set/Get the prop that this assembly node refers to.

\item  \verb|vtkProp = obj.GetViewProp ()| -  Set/Get the prop that this assembly node refers to.

\item  \verb|obj.SetMatrix (vtkMatrix4x4 matrix)| -  Specify a transformation matrix associated with the prop.
 Note: if the prop is not a type of vtkProp3D, then the
 transformation matrix is ignored (and expected to be NULL).
 Also, internal to this object the matrix is copied because
 the matrix is used for computation by vtkAssemblyPath.

\item  \verb|vtkMatrix4x4 = obj.GetMatrix ()| -  Specify a transformation matrix associated with the prop.
 Note: if the prop is not a type of vtkProp3D, then the
 transformation matrix is ignored (and expected to be NULL).
 Also, internal to this object the matrix is copied because
 the matrix is used for computation by vtkAssemblyPath.

\item  \verb|long = obj.GetMTime ()| -  Override the standard GetMTime() to check for the modified times
 of the prop and matrix.

\item  \verb|obj.SetProp (vtkProp prop)| -  @deprecated Replaced by vtkAssemblyNode::SetViewProp() as of VTK 5.0.

\item  \verb|vtkProp = obj.GetProp ()| -  @deprecated Replaced by vtkAssemblyNode::GetViewProp() as of VTK 5.0.

\end{itemize}
