\section{vtkStructuredVisibilityConstraint}

\subsection{Usage}

 vtkStructuredVisibilityConstraint is a general class to manage
 a list of points/cell marked as invalid or invisible. Currently,
 it does this by maintaining an unsigned char array associated
 with points/cells. To conserve memory, this array is allocated
 only when it is needed (when Blank() is called the first time).
 Make sure to call Initialize() with the right dimensions before
 calling any methods that set/get visibility.

To create an instance of class vtkStructuredVisibilityConstraint, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkStructuredVisibilityConstraint
\end{verbatim}
\subsection{Methods}

The class vtkStructuredVisibilityConstraint has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkStructuredVisibilityConstraint class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkStructuredVisibilityConstraint = obj.NewInstance ()|

\item  \verb|vtkStructuredVisibilityConstraint = obj.SafeDownCast (vtkObject o)|

\item  \verb|char = obj.IsVisible (vtkIdType id)| -  Returns 1 is the point/cell is visible, 0 otherwise.

\item  \verb|obj.Blank (vtkIdType id)| -  Sets the visibility flag of the given point/cell off.
 The first time blank is called, a new visibility array
 is created if it doesn't exist.

\item  \verb|obj.UnBlank (vtkIdType id)| -  Sets the visibility flag of the given point/cell on.

\item  \verb|int = obj. GetDimensions ()| -  Get the dimensions used to initialize the object.

\item  \verb|obj.Initialize (int dims[3])| -  Set the dimensions and set the Initialized flag to 1. Once
 an object is initialized, it's dimensions can not be
 changed anymore.

\item  \verb|obj.SetVisibilityById (vtkUnsignedCharArray vis)| -  Set/Get the array used to store the visibility flags.

\item  \verb|vtkUnsignedCharArray = obj.GetVisibilityById ()| -  Set/Get the array used to store the visibility flags.

\item  \verb|obj.ShallowCopy (vtkStructuredVisibilityConstraint src)| -  Copies the dimensions, the visibility array pointer
 and the initialized flag.

\item  \verb|obj.DeepCopy (vtkStructuredVisibilityConstraint src)| -  Copies the dimensions, the visibility array
 and the initialized flag.

\item  \verb|char = obj.IsConstrained ()|

\end{itemize}
