\section{vtkIdentityTransform}

\subsection{Usage}

 vtkIdentityTransform is a transformation which will simply pass coordinate
 data unchanged.  All other transform types can also do this, however,
 the vtkIdentityTransform does so with much greater efficiency.

To create an instance of class vtkIdentityTransform, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkIdentityTransform
\end{verbatim}
\subsection{Methods}

The class vtkIdentityTransform has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkIdentityTransform class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkIdentityTransform = obj.NewInstance ()|

\item  \verb|vtkIdentityTransform = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.TransformPoints (vtkPoints inPts, vtkPoints outPts)| -  Apply the transformation to a series of points, and append the
 results to outPts.  

\item  \verb|obj.TransformNormals (vtkDataArray inNms, vtkDataArray outNms)| -  Apply the transformation to a series of normals, and append the
 results to outNms.  

\item  \verb|obj.TransformVectors (vtkDataArray inVrs, vtkDataArray outVrs)| -  Apply the transformation to a series of vectors, and append the
 results to outVrs.  

\item  \verb|obj.TransformPointsNormalsVectors (vtkPoints inPts, vtkPoints outPts, vtkDataArray inNms, vtkDataArray outNms, vtkDataArray inVrs, vtkDataArray outVrs)| -  Apply the transformation to a combination of points, normals
 and vectors.  

\item  \verb|obj.Inverse ()|

\item  \verb|obj.InternalTransformPoint (float in[3], float out[3])| -  This will calculate the transformation without calling Update.
 Meant for use only within other VTK classes.

\item  \verb|obj.InternalTransformPoint (double in[3], double out[3])| -  This will calculate the transformation without calling Update.
 Meant for use only within other VTK classes.

\item  \verb|obj.InternalTransformNormal (float in[3], float out[3])| -  This will calculate the transformation without calling Update.
 Meant for use only within other VTK classes.

\item  \verb|obj.InternalTransformNormal (double in[3], double out[3])| -  This will calculate the transformation without calling Update.
 Meant for use only within other VTK classes.

\item  \verb|obj.InternalTransformVector (float in[3], float out[3])| -  This will calculate the transformation without calling Update.
 Meant for use only within other VTK classes.

\item  \verb|obj.InternalTransformVector (double in[3], double out[3])| -  This will calculate the transformation without calling Update.
 Meant for use only within other VTK classes.

\item  \verb|vtkAbstractTransform = obj.MakeTransform ()| -  Make a transform of the same type.  This will actually
 return the same transform.

\end{itemize}
