\section{vtkPlane}

\subsection{Usage}

 vtkPlane provides methods for various plane computations. These include
 projecting points onto a plane, evaluating the plane equation, and 
 returning plane normal. vtkPlane is a concrete implementation of the 
 abstract class vtkImplicitFunction.

To create an instance of class vtkPlane, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkPlane
\end{verbatim}
\subsection{Methods}

The class vtkPlane has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkPlane class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkPlane = obj.NewInstance ()|

\item  \verb|vtkPlane = obj.SafeDownCast (vtkObject o)|

\item  \verb|double = obj.EvaluateFunction (double x[3])|

\item  \verb|double = obj.EvaluateFunction (double x, double y, double z)|

\item  \verb|obj.EvaluateGradient (double x[3], double g[3])|

\item  \verb|obj.SetNormal (double , double , double )| -  Set/get plane normal. Plane is defined by point and normal.

\item  \verb|obj.SetNormal (double  a[3])| -  Set/get plane normal. Plane is defined by point and normal.

\item  \verb|double = obj. GetNormal ()| -  Set/get plane normal. Plane is defined by point and normal.

\item  \verb|obj.SetOrigin (double , double , double )| -  Set/get point through which plane passes. Plane is defined by point 
 and normal.

\item  \verb|obj.SetOrigin (double  a[3])| -  Set/get point through which plane passes. Plane is defined by point 
 and normal.

\item  \verb|double = obj. GetOrigin ()| -  Set/get point through which plane passes. Plane is defined by point 
 and normal.

\item  \verb|obj.Push (double distance)| -  Translate the plane in the direction of the normal by the
 distance specified.  Negative values move the plane in the
 opposite direction.

\item  \verb|obj.ProjectPoint (double x[3], double xproj[3])|

\item  \verb|obj.GeneralizedProjectPoint (double x[3], double xproj[3])|

\item  \verb|double = obj.DistanceToPlane (double x[3])| -  Return the distance of a point x to a plane defined by n(x-p0) = 0. The
 normal n[3] must be magnitude=1.

\end{itemize}
