\section{vtkInformationDataObjectKey}

\subsection{Usage}

 vtkInformationDataObjectKey is used to represent keys in
 vtkInformation for values that are vtkDataObject instances.

To create an instance of class vtkInformationDataObjectKey, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkInformationDataObjectKey
\end{verbatim}
\subsection{Methods}

The class vtkInformationDataObjectKey has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkInformationDataObjectKey class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkInformationDataObjectKey = obj.NewInstance ()|

\item  \verb|vtkInformationDataObjectKey = obj.SafeDownCast (vtkObject o)|

\item  \verb|vtkInformationDataObjectKey = obj.(string name, string location)|

\item  \verb|~vtkInformationDataObjectKey = obj.()|

\item  \verb|obj.ShallowCopy (vtkInformation from, vtkInformation to)| -  Copy the entry associated with this key from one information
 object to another.  If there is no entry in the first information
 object for this key, the value is removed from the second.

\item  \verb|obj.Report (vtkInformation info, vtkGarbageCollector collector)| -  Report a reference this key has in the given information object.

\end{itemize}
