\section{vtkThreadMessager}

\subsection{Usage}

 vtkMultithreader is a class that provides support for messaging between
 threads multithreaded using pthreads or Windows messaging.

To create an instance of class vtkThreadMessager, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkThreadMessager
\end{verbatim}
\subsection{Methods}

The class vtkThreadMessager has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkThreadMessager class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkThreadMessager = obj.NewInstance ()|

\item  \verb|vtkThreadMessager = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.WaitForMessage ()| -  Wait (block, non-busy) until another thread sends a
 message.

\item  \verb|obj.SendWakeMessage ()| -  Send a message to all threads who are waiting via
 WaitForMessage().

\item  \verb|obj.EnableWaitForReceiver ()| -  pthreads only. If the wait is enabled, the thread who
 is to call WaitForMessage() will block until a receiver
 thread is ready to receive.

\item  \verb|obj.DisableWaitForReceiver ()| -  pthreads only. If the wait is enabled, the thread who
 is to call WaitForMessage() will block until a receiver
 thread is ready to receive.

\item  \verb|obj.WaitForReceiver ()| -  pthreads only.
 If wait is enable, this will block until one thread is ready
 to receive a message.

\item  \verb|obj.SendMessage ()| -  @deprecated Replaced by vtkThreadMessager::SendWakeMessage() as of
 VTK 5.0.

\end{itemize}
