\section{vtkHomogeneousTransform}

\subsection{Usage}

 vtkHomogeneousTransform provides a generic interface for homogeneous 
 transformations, i.e. transformations which can be represented by 
 multiplying a 4x4 matrix with a homogeneous coordinate. 

To create an instance of class vtkHomogeneousTransform, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkHomogeneousTransform
\end{verbatim}
\subsection{Methods}

The class vtkHomogeneousTransform has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkHomogeneousTransform class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkHomogeneousTransform = obj.NewInstance ()|

\item  \verb|vtkHomogeneousTransform = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.TransformPoints (vtkPoints inPts, vtkPoints outPts)| -  Apply the transformation to a series of points, and append the
 results to outPts.  

\item  \verb|obj.TransformPointsNormalsVectors (vtkPoints inPts, vtkPoints outPts, vtkDataArray inNms, vtkDataArray outNms, vtkDataArray inVrs, vtkDataArray outVrs)| -  Apply the transformation to a combination of points, normals
 and vectors.  

\item  \verb|obj.GetMatrix (vtkMatrix4x4 m)| -  Get a copy of the internal transformation matrix.  The
 transform is Updated first, to guarantee that the matrix
 is valid.

\item  \verb|vtkMatrix4x4 = obj.GetMatrix ()| -  Get a pointer to an internal vtkMatrix4x4 that represents
 the transformation.  An Update() is called on the transform
 to ensure that the matrix is up-to-date when you get it.
 You should not store the matrix pointer anywhere because it
 might become stale.

\item  \verb|vtkHomogeneousTransform = obj.GetHomogeneousInverse ()| -  This will calculate the transformation without calling Update.
 Meant for use only within other VTK classes.

\item  \verb|obj.InternalTransformPoint (float in[3], float out[3])| -  This will calculate the transformation without calling Update.
 Meant for use only within other VTK classes.

\item  \verb|obj.InternalTransformPoint (double in[3], double out[3])| -  This will calculate the transformation without calling Update.
 Meant for use only within other VTK classes.

\end{itemize}
