\section{vtkInformationInformationVectorKey}

\subsection{Usage}

 vtkInformationInformationVectorKey is used to represent keys in
 vtkInformation for vectors of other vtkInformation objects.

To create an instance of class vtkInformationInformationVectorKey, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkInformationInformationVectorKey
\end{verbatim}
\subsection{Methods}

The class vtkInformationInformationVectorKey has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkInformationInformationVectorKey class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkInformationInformationVectorKey = obj.NewInstance ()|

\item  \verb|vtkInformationInformationVectorKey = obj.SafeDownCast (vtkObject o)|

\item  \verb|vtkInformationInformationVectorKey = obj.(string name, string location)|

\item  \verb|~vtkInformationInformationVectorKey = obj.()|

\item  \verb|obj.Set (vtkInformation info, vtkInformationVector )| -  Get/Set the value associated with this key in the given
 information object.

\item  \verb|vtkInformationVector = obj.Get (vtkInformation info)| -  Get/Set the value associated with this key in the given
 information object.

\item  \verb|obj.ShallowCopy (vtkInformation from, vtkInformation to)| -  Copy the entry associated with this key from one information
 object to another.  If there is no entry in the first information
 object for this key, the value is removed from the second.

\item  \verb|obj.DeepCopy (vtkInformation from, vtkInformation to)| -  Duplicate (new instance created) the entry associated with this key from
 one information object to another (new instances of any contained
 vtkInformation and vtkInformationVector objects are created).  

\item  \verb|obj.Report (vtkInformation info, vtkGarbageCollector collector)| -  Report a reference this key has in the given information object.

\end{itemize}
