\section{vtkCollectionIterator}

\subsection{Usage}

 vtkCollectionIterator provides an alternative way to traverse
 through the objects in a vtkCollection.  Unlike the collection's
 built in interface, this allows multiple iterators to
 simultaneously traverse the collection.  If items are removed from
 the collection, only the iterators currently pointing to those
 items are invalidated.  Other iterators will still continue to
 function normally.

To create an instance of class vtkCollectionIterator, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkCollectionIterator
\end{verbatim}
\subsection{Methods}

The class vtkCollectionIterator has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkCollectionIterator class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkCollectionIterator = obj.NewInstance ()|

\item  \verb|vtkCollectionIterator = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetCollection (vtkCollection )| -  Set/Get the collection over which to iterate.

\item  \verb|vtkCollection = obj.GetCollection ()| -  Set/Get the collection over which to iterate.

\item  \verb|obj.InitTraversal ()| -  Position the iterator at the first item in the collection.

\item  \verb|obj.GoToFirstItem ()| -  Position the iterator at the first item in the collection.

\item  \verb|obj.GoToNextItem ()| -  Move the iterator to the next item in the collection.

\item  \verb|int = obj.IsDoneWithTraversal ()| -  Test whether the iterator is currently positioned at a valid item.
 Returns 1 for yes, 0 for no.

\item  \verb|vtkObject = obj.GetCurrentObject ()| -  Get the item at the current iterator position.  Valid only when
 IsDoneWithTraversal() returns 1.

\item  \verb|vtkObject = obj.GetObject ()| -  @deprecated Replaced by vtkCollectionIterator::GetCurrentObject() as
 of VTK 5.0.

\end{itemize}
