\section{vtkPriorityQueue}

\subsection{Usage}

 vtkPriorityQueue is a general object for creating and manipulating lists
 of object ids (e.g., point or cell ids). Object ids are sorted according
 to a user-specified priority, where entries at the top of the queue have
 the smallest values.

 This implementation provides a feature beyond the usual ability to insert
 and retrieve (or pop) values from the queue. It is also possible to
 pop any item in the queue given its id number. This allows you to delete
 entries in the queue which can useful for reinserting an item into the
 queue. 


To create an instance of class vtkPriorityQueue, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkPriorityQueue
\end{verbatim}
\subsection{Methods}

The class vtkPriorityQueue has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkPriorityQueue class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkPriorityQueue = obj.NewInstance ()|

\item  \verb|vtkPriorityQueue = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.Allocate (vtkIdType sz, vtkIdType ext)| -  Allocate initial space for priority queue.

\item  \verb|obj.Insert (double priority, vtkIdType id)| -  Insert id with priority specified. The id is generally an
 index like a point id or cell id.

\item  \verb|vtkIdType = obj.Pop (vtkIdType location)| -  Same as above but simplified for easier wrapping into interpreted
 languages.

\item  \verb|vtkIdType = obj.Peek (vtkIdType location)| -  Peek into the queue without actually removing anything. Returns the
 id.

\item  \verb|double = obj.DeleteId (vtkIdType id)| -  Delete entry in queue with specified id. Returns priority value
 associated with that id; or VTK\_DOUBLE\_MAX if not in queue.

\item  \verb|double = obj.GetPriority (vtkIdType id)| -  Get the priority of an entry in the queue with specified id. Returns
 priority value of that id or VTK\_DOUBLE\_MAX if not in queue.

\item  \verb|vtkIdType = obj.GetNumberOfItems ()| -  Return the number of items in this queue.

\item  \verb|obj.Reset ()| -  Empty the queue but without releasing memory. This avoids the
 overhead of memory allocation/deletion.

\end{itemize}
