\section{vtkCellLinks}

\subsection{Usage}

 vtkCellLinks is a supplemental object to vtkCellArray and vtkCellTypes, 
 enabling access from points to the cells using the points. vtkCellLinks is
 a list of Links, each link represents a dynamic list of cell id's using the 
 point. The information provided by this object can be used to determine 
 neighbors and construct other local topological information.

To create an instance of class vtkCellLinks, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkCellLinks
\end{verbatim}
\subsection{Methods}

The class vtkCellLinks has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkCellLinks class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkCellLinks = obj.NewInstance ()|

\item  \verb|vtkCellLinks = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.Allocate (vtkIdType numLinks, vtkIdType ext)| -  Allocate the specified number of links (i.e., number of points) that
 will be built.

\item  \verb|short = obj.GetNcells (vtkIdType ptId)| -  Get the number of cells using the point specified by ptId.

\item  \verb|obj.BuildLinks (vtkDataSet data)| -  Build the link list array.

\item  \verb|obj.BuildLinks (vtkDataSet data, vtkCellArray Connectivity)| -  Build the link list array.

\item  \verb|vtkIdType = obj.GetCells (vtkIdType ptId)| -  Return a list of cell ids using the point.

\item  \verb|vtkIdType = obj.InsertNextPoint (int numLinks)| -  Insert a new point into the cell-links data structure. The size parameter
 is the initial size of the list.

\item  \verb|obj.InsertNextCellReference (vtkIdType ptId, vtkIdType cellId)| -  Insert a cell id into the list of cells (at the end) using the cell id 
 provided. (Make sure to extend the link list (if necessary) using the
 method ResizeCellList().)

\item  \verb|obj.DeletePoint (vtkIdType ptId)| -  Delete point (and storage) by destroying links to using cells.

\item  \verb|obj.RemoveCellReference (vtkIdType cellId, vtkIdType ptId)| -  Delete the reference to the cell (cellId) from the point (ptId). This
 removes the reference to the cellId from the cell list, but does not
 resize the list (recover memory with ResizeCellList(), if necessary).

\item  \verb|obj.AddCellReference (vtkIdType cellId, vtkIdType ptId)| -  Add the reference to the cell (cellId) from the point (ptId). This
 adds a reference to the cellId from the cell list, but does not resize
 the list (extend memory with ResizeCellList(), if necessary).

\item  \verb|obj.ResizeCellList (vtkIdType ptId, int size)| -  Change the length of a point's link list (i.e., list of cells using a
 point) by the size specified.

\item  \verb|obj.Squeeze ()| -  Reclaim any unused memory.

\item  \verb|obj.Reset ()| -  Reset to a state of no entries without freeing the memory.

\item  \verb|long = obj.GetActualMemorySize ()| -  Return the memory in kilobytes consumed by this cell links array. 
 Used to support streaming and reading/writing data. The value 
 returned is guaranteed to be greater than or equal to the memory 
 required to actually represent the data represented by this object. 
 The information returned is valid only after the pipeline has 
 been updated.

\item  \verb|obj.DeepCopy (vtkCellLinks src)| -  Standard DeepCopy method.  Since this object contains no reference
 to other objects, there is no ShallowCopy.

\end{itemize}
