\section{vtkKochanekSpline}

\subsection{Usage}

 Implements the Kochenek interpolating spline described in: Kochanek, D.,
 Bartels, R., ''Interpolating Splines with Local Tension, Continuity, and
 Bias Control,'' Computer Graphics, vol. 18, no. 3, pp. 33-41, July 1984.
 These splines give the user more control over the shape of the curve than
 the cardinal splines implemented in vtkCardinalSpline. Three parameters
 can be specified. All have a range from -1 to 1.
 
 Tension controls how sharply the curve bends at an input point. A
 value of -1 produces more slack in the curve. A value of 1 tightens
 the curve.
 
 Continuity controls the continuity of the first derivative at input
 points. 
 
 Bias controls the direction of the curve at it passes through an input
 point. A value of -1 undershoots the point while a value of 1
 overshoots the point.
 
 These three parameters give the user broad control over the shape of
 the interpolating spline. The original Kochanek paper describes the
 effects nicely and is recommended reading.

To create an instance of class vtkKochanekSpline, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkKochanekSpline
\end{verbatim}
\subsection{Methods}

The class vtkKochanekSpline has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkKochanekSpline class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkKochanekSpline = obj.NewInstance ()|

\item  \verb|vtkKochanekSpline = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.Compute ()| -  Compute Kochanek Spline coefficients.

\item  \verb|double = obj.Evaluate (double t)| -  Evaluate a 1D Kochanek spline.

\item  \verb|obj.SetDefaultBias (double )| -  Set the bias for all points. Default is 0.

\item  \verb|double = obj.GetDefaultBias ()| -  Set the bias for all points. Default is 0.

\item  \verb|obj.SetDefaultTension (double )| -  Set the tension for all points. Default is 0.

\item  \verb|double = obj.GetDefaultTension ()| -  Set the tension for all points. Default is 0.

\item  \verb|obj.SetDefaultContinuity (double )| -  Set the continuity for all points. Default is 0.

\item  \verb|double = obj.GetDefaultContinuity ()| -  Set the continuity for all points. Default is 0.

\item  \verb|obj.DeepCopy (vtkSpline s)| -  Deep copy of cardinal spline data.

\end{itemize}
