\section{vtkDemandDrivenPipeline}

\subsection{Usage}

 vtkDemandDrivenPipeline is an executive that will execute an
 algorithm only when its outputs are out-of-date with respect to its
 inputs.

To create an instance of class vtkDemandDrivenPipeline, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkDemandDrivenPipeline
\end{verbatim}
\subsection{Methods}

The class vtkDemandDrivenPipeline has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkDemandDrivenPipeline class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkDemandDrivenPipeline = obj.NewInstance ()|

\item  \verb|vtkDemandDrivenPipeline = obj.SafeDownCast (vtkObject o)|

\item  \verb|int = obj.Update ()| -  Bring the algorithm's outputs up-to-date.  Returns 1 for success
 and 0 for failure.

\item  \verb|int = obj.Update (int port)| -  Bring the algorithm's outputs up-to-date.  Returns 1 for success
 and 0 for failure.

\item  \verb|long = obj.GetPipelineMTime ()| -  Get the PipelineMTime for this exective.

\item  \verb|int = obj.SetReleaseDataFlag (int port, int n)| -  Set whether the given output port releases data when it is
 consumed.  Returns 1 if the the value changes and 0 otherwise.

\item  \verb|int = obj.GetReleaseDataFlag (int port)| -  Get whether the given output port releases data when it is consumed.

\item  \verb|int = obj.UpdatePipelineMTime ()| -  Bring the PipelineMTime up to date.

\item  \verb|int = obj.UpdateDataObject ()| -  Bring the output data object's existence up to date.  This does
 not actually produce data, but does create the data object that
 will store data produced during the UpdateData step.

\item  \verb|int = obj.UpdateInformation ()| -  Bring the output information up to date.

\item  \verb|int = obj.UpdateData (int outputPort)| -  Bring the output data up to date.  This should be called only
 when information is up to date.  Use the Update method if it is
 not known that the information is up to date.

\end{itemize}
