\section{vtkActor2DCollection}

\subsection{Usage}

 vtkActor2DCollection is a subclass of vtkCollection.  vtkActor2DCollection
 maintains a collection of vtkActor2D objects that is sorted by layer
 number, with lower layer numbers at the start of the list.  This allows
 the vtkActor2D objects to be rendered in the correct order. 

To create an instance of class vtkActor2DCollection, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkActor2DCollection
\end{verbatim}
\subsection{Methods}

The class vtkActor2DCollection has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkActor2DCollection class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkActor2DCollection = obj.NewInstance ()|

\item  \verb|vtkActor2DCollection = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.Sort ()| -  Sorts the vtkActor2DCollection by layer number.  Smaller layer
 numbers are first.  Layer numbers can be any integer value.

\item  \verb|obj.AddItem (vtkActor2D a)| -  Add an actor to the list.  The new actor is inserted in the list
 according to it's layer number.

\item  \verb|int = obj.IsItemPresent (vtkActor2D a)| -  Standard Collection methods

\item  \verb|vtkActor2D = obj.GetNextActor2D ()| -  Standard Collection methods

\item  \verb|vtkActor2D = obj.GetLastActor2D ()| -  Standard Collection methods

\item  \verb|vtkActor2D = obj.GetNextItem ()| -  Access routines that are provided for compatibility with previous
 version of VTK.  Please use the GetNextActor2D(), GetLastActor2D()
 variants where possible.

\item  \verb|vtkActor2D = obj.GetLastItem ()| -  Access routines that are provided for compatibility with previous
 version of VTK.  Please use the GetNextActor2D(), GetLastActor2D()
 variants where possible.

\item  \verb|obj.RenderOverlay (vtkViewport viewport)| -  Sort and then render the collection of 2D actors.  

\end{itemize}
