\section{vtkPlanesIntersection}

\subsection{Usage}

    A subclass of vtkPlanes, this class determines whether it
    intersects an axis aligned box.   This is motivated by the
    need to intersect the axis aligned region of a spacial
    decomposition of volume data with various other regions.
    It uses the algorithm from Graphics Gems IV, page 81.

 .SECTION Caveat
    An instance of vtkPlanes can be redefined by changing the planes,
    but this subclass then will not know if the region vertices are
    up to date.  (Region vertices can be specified in SetRegionVertices
    or computed by the subclass.)  So Delete and recreate if you want
    to change the set of planes.


To create an instance of class vtkPlanesIntersection, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkPlanesIntersection
\end{verbatim}
\subsection{Methods}

The class vtkPlanesIntersection has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkPlanesIntersection class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkPlanesIntersection = obj.NewInstance ()|

\item  \verb|vtkPlanesIntersection = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetRegionVertices (vtkPoints pts)|

\item  \verb|obj.SetRegionVertices (double v, int nvertices)|

\item  \verb|int = obj.GetNumRegionVertices ()|

\item  \verb|int = obj.GetRegionVertices (double v, int nvertices)|

\item  \verb|int = obj.IntersectsRegion (vtkPoints R)|

\end{itemize}
