\section{vtkImplicitBoolean}

\subsection{Usage}

 vtkImplicitBoolean is an implicit function consisting of boolean
 combinations of implicit functions. The class has a list of functions
 (FunctionList) that are combined according to a specified operator
 (VTK\_UNION or VTK\_INTERSECTION or VTK\_DIFFERENCE). You can use nested
 combinations of vtkImplicitFunction's (and/or vtkImplicitBoolean) to create
 elaborate implicit functions.  vtkImplicitBoolean is a concrete
 implementation of vtkImplicitFunction.

 The operators work as follows. The VTK\_UNION operator takes the minimum
 value of all implicit functions. The VTK\_INTERSECTION operator takes the
 maximum value of all implicit functions. The VTK\_DIFFERENCE operator
 subtracts the 2nd through last implicit functions from the first. The
 VTK\_UNION\_OF\_MAGNITUDES takes the minimum absolute value of the 
 implicit functions.

To create an instance of class vtkImplicitBoolean, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkImplicitBoolean
\end{verbatim}
\subsection{Methods}

The class vtkImplicitBoolean has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkImplicitBoolean class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkImplicitBoolean = obj.NewInstance ()|

\item  \verb|vtkImplicitBoolean = obj.SafeDownCast (vtkObject o)|

\item  \verb|double = obj.EvaluateFunction (double x[3])| -  Evaluate boolean combinations of implicit function using current operator.

\item  \verb|double = obj.EvaluateFunction (double x, double y, double z)| -  Evaluate boolean combinations of implicit function using current operator.

\item  \verb|obj.EvaluateGradient (double x[3], double g[3])| -  Evaluate gradient of boolean combination.

\item  \verb|long = obj.GetMTime ()| -  Override modified time retrieval because of object dependencies.

\item  \verb|obj.AddFunction (vtkImplicitFunction in)| -  Add another implicit function to the list of functions.

\item  \verb|obj.RemoveFunction (vtkImplicitFunction in)| -  Remove a function from the list of implicit functions to boolean.

\item  \verb|vtkImplicitFunctionCollection = obj.GetFunction ()| -  Return the collection of implicit functions.

\item  \verb|obj.SetOperationType (int )| -  Specify the type of boolean operation.

\item  \verb|int = obj.GetOperationTypeMinValue ()| -  Specify the type of boolean operation.

\item  \verb|int = obj.GetOperationTypeMaxValue ()| -  Specify the type of boolean operation.

\item  \verb|int = obj.GetOperationType ()| -  Specify the type of boolean operation.

\item  \verb|obj.SetOperationTypeToUnion ()| -  Specify the type of boolean operation.

\item  \verb|obj.SetOperationTypeToIntersection ()| -  Specify the type of boolean operation.

\item  \verb|obj.SetOperationTypeToDifference ()| -  Specify the type of boolean operation.

\item  \verb|obj.SetOperationTypeToUnionOfMagnitudes ()| -  Specify the type of boolean operation.

\item  \verb|string = obj.GetOperationTypeAsString ()| -  Specify the type of boolean operation.

\end{itemize}
