\section{vtkGenericCellIterator}

\subsection{Usage}

 This class (and subclasses) are used to iterate over cells. Use it
 only in conjunction with vtkGenericDataSet (i.e., the adaptor framework).

 Typical use is:
 \begin{verbatim}
 vtkGenericDataSet *dataset;
 vtkGenericCellIterator *it = dataset->NewCellIterator(2);
 for (it->Begin(); !it->IsAtEnd(); it->Next());
   {
   spec=it->GetCell();
   }
 \end{verbatim}

To create an instance of class vtkGenericCellIterator, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkGenericCellIterator
\end{verbatim}
\subsection{Methods}

The class vtkGenericCellIterator has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkGenericCellIterator class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()| -  Standard VTK construction and type macros.

\item  \verb|int = obj.IsA (string name)| -  Standard VTK construction and type macros.

\item  \verb|vtkGenericCellIterator = obj.NewInstance ()| -  Standard VTK construction and type macros.

\item  \verb|vtkGenericCellIterator = obj.SafeDownCast (vtkObject o)| -  Standard VTK construction and type macros.

\item  \verb|obj.Begin ()| -  Move iterator to first position if any (loop initialization).

\item  \verb|int = obj.IsAtEnd ()| -  Is the iterator at the end of traversal?

\item  \verb|vtkGenericAdaptorCell = obj.NewCell ()| -  Create an empty cell. The user is responsible for deleting it.
 

\item  \verb|obj.GetCell (vtkGenericAdaptorCell c)| -  Get the cell at current position. The cell should be instantiated
 with the NewCell() method.
 
 
 THREAD SAFE

\item  \verb|vtkGenericAdaptorCell = obj.GetCell ()| -  Get the cell at the current traversal position.
 NOT THREAD SAFE
 
 

\item  \verb|obj.Next ()| -  Move the iterator to the next position in the list.
 

\end{itemize}
