\section{vtkBiQuadraticQuad}

\subsection{Usage}

 vtkQuadraticQuad is a concrete implementation of vtkNonLinearCell to
 represent a two-dimensional, 9-node isoparametric parabolic quadrilateral
 element with a Centerpoint. The interpolation is the standard finite
 element, quadratic isoparametric shape function. The cell includes a
 mid-edge node for each of the four edges of the cell and a center node at
 the surface. The ordering of the eight points defining the cell are point
 ids (0-3,4-8) where ids 0-3 define the four corner vertices of the quad;
 ids 4-7 define the midedge nodes (0,1), (1,2), (2,3), (3,0) and 8 define
 the face center node.


To create an instance of class vtkBiQuadraticQuad, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkBiQuadraticQuad
\end{verbatim}
\subsection{Methods}

The class vtkBiQuadraticQuad has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkBiQuadraticQuad class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkBiQuadraticQuad = obj.NewInstance ()|

\item  \verb|vtkBiQuadraticQuad = obj.SafeDownCast (vtkObject o)|

\item  \verb|int = obj.GetCellType ()| -  Implement the vtkCell API. See the vtkCell API for descriptions
 of these methods.

\item  \verb|int = obj.GetCellDimension ()| -  Implement the vtkCell API. See the vtkCell API for descriptions
 of these methods.

\item  \verb|int = obj.GetNumberOfEdges ()| -  Implement the vtkCell API. See the vtkCell API for descriptions
 of these methods.

\item  \verb|int = obj.GetNumberOfFaces ()| -  Implement the vtkCell API. See the vtkCell API for descriptions
 of these methods.

\item  \verb|vtkCell = obj.GetEdge (int )| -  Implement the vtkCell API. See the vtkCell API for descriptions
 of these methods.

\item  \verb|vtkCell = obj.GetFace (int )|

\item  \verb|int = obj.CellBoundary (int subId, double pcoords[3], vtkIdList pts)|

\item  \verb|int = obj.Triangulate (int index, vtkIdList ptIds, vtkPoints pts)|

\item  \verb|obj.Derivatives (int subId, double pcoords[3], double values, int dim, double derivs)|

\item  \verb|obj.Contour (double value, vtkDataArray cellScalars, vtkIncrementalPointLocator locator, vtkCellArray verts, vtkCellArray lines, vtkCellArray polys, vtkPointData inPd, vtkPointData outPd, vtkCellData inCd, vtkIdType cellId, vtkCellData outCd)|

\item  \verb|obj.Clip (double value, vtkDataArray cellScalars, vtkIncrementalPointLocator locator, vtkCellArray polys, vtkPointData inPd, vtkPointData outPd, vtkCellData inCd, vtkIdType cellId, vtkCellData outCd, int insideOut)| -  Clip this biquadratic quad using scalar value provided. Like contouring,
 except that it cuts the twi quads to produce linear triangles.

\item  \verb|int = obj.GetParametricCenter (double pcoords[3])| -  Return the center of the pyramid in parametric coordinates.

\item  \verb|obj.InterpolateFunctions (double pcoords[3], double weights[9])| -  Compute the interpolation functions/derivatives
 (aka shape functions/derivatives)

\item  \verb|obj.InterpolateDerivs (double pcoords[3], double derivs[18])|

\end{itemize}
