\section{vtkSelection}

\subsection{Usage}


To create an instance of class vtkSelection, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkSelection
\end{verbatim}
\subsection{Methods}

The class vtkSelection has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkSelection class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkSelection = obj.NewInstance ()|

\item  \verb|vtkSelection = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.Initialize ()| -  Restore data object to initial state,

\item  \verb|int = obj.GetDataObjectType ()| -  Returns the number of nodes in this selection.
 Each node contains information about part of the selection.

\item  \verb|int = obj.GetNumberOfNodes ()| -  Returns the number of nodes in this selection.
 Each node contains information about part of the selection.

\item  \verb|vtkSelectionNode = obj.GetNode (int idx)| -  Returns a node given it's index. Performs bound checking
 and will return 0 if out-of-bounds.

\item  \verb|obj.AddNode (vtkSelectionNode )| -  Adds a selection node.

\item  \verb|obj.RemoveNode (int idx)| -  Removes a selection node.

\item  \verb|obj.RemoveNode (vtkSelectionNode )| -  Removes a selection node.

\item  \verb|obj.RemoveAllNodes ()| -  Removes a selection node.

\item  \verb|obj.DeepCopy (vtkDataObject src)| -  Copy selection nodes of the input.

\item  \verb|obj.ShallowCopy (vtkDataObject src)| -  Copy selection nodes of the input.
 This is a shallow copy: selection lists and pointers in the
 properties are passed by reference.

\item  \verb|obj.Union (vtkSelection selection)| -  Union this selection with the specified selection.
 Attempts to reuse selection nodes in this selection if properties
 match exactly. Otherwise, creates new selection nodes.

\item  \verb|obj.Union (vtkSelectionNode node)| -  Union this selection with the specified selection node.
 Attempts to reuse a selection node in this selection if properties
 match exactly. Otherwise, creates a new selection node.

\item  \verb|long = obj.GetMTime ()| -  Return the MTime taking into account changes to the properties

\item  \verb|obj.Dump ()| -  Dumps the contents of the selection, giving basic information only.

\end{itemize}
