\section{vtkAnnotation}

\subsection{Usage}

 vtkAnnotation is a collection of annotation properties along with
 an associated selection indicating the portion of data the annotation
 refers to.

 .SECTION Thanks
 Timothy M. Shead (tshead@sandia.gov) at Sandia National Laboratories
 contributed code to this class.

To create an instance of class vtkAnnotation, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkAnnotation
\end{verbatim}
\subsection{Methods}

The class vtkAnnotation has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkAnnotation class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkAnnotation = obj.NewInstance ()|

\item  \verb|vtkAnnotation = obj.SafeDownCast (vtkObject o)|

\item  \verb|vtkSelection = obj.GetSelection ()| -  The selection to which this set of annotations will apply.

\item  \verb|obj.SetSelection (vtkSelection selection)| -  The selection to which this set of annotations will apply.

\item  \verb|obj.Initialize ()| -  Initialize the annotation to an empty state.

\item  \verb|obj.ShallowCopy (vtkDataObject other)| -  Make this annotation have the same properties and have
 the same selection of another annotation.

\item  \verb|obj.DeepCopy (vtkDataObject other)| -  Make this annotation have the same properties and have
 a copy of the selection of another annotation.

\item  \verb|long = obj.GetMTime ()| -  Get the modified time of this object.

\end{itemize}
