\section{vtkSelectionNode}

\subsection{Usage}


To create an instance of class vtkSelectionNode, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkSelectionNode
\end{verbatim}
\subsection{Methods}

The class vtkSelectionNode has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkSelectionNode class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkSelectionNode = obj.NewInstance ()|

\item  \verb|vtkSelectionNode = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.Initialize ()| -  Restore data object to initial state,

\item  \verb|obj.SetSelectionList (vtkAbstractArray )| -  Sets the selection list.

\item  \verb|vtkAbstractArray = obj.GetSelectionList ()| -  Sets the selection list.

\item  \verb|obj.SetSelectionData (vtkDataSetAttributes data)| -  Sets the selection table.

\item  \verb|vtkDataSetAttributes = obj.GetSelectionData ()| -  Sets the selection table.

\item  \verb|vtkInformation = obj.GetProperties ()| -  Returns the property map.

\item  \verb|obj.DeepCopy (vtkSelectionNode src)| -  Copy properties, selection list and children of the input.

\item  \verb|obj.ShallowCopy (vtkSelectionNode src)| -  Copy properties, selection list and children of the input.
 This is a shallow copy: selection lists and pointers in the
 properties are passed by reference.

\item  \verb|long = obj.GetMTime ()| -  Return the MTime taking into account changes to the properties

\item  \verb|obj.SetContentType (int type)| -  Get or set the content type of the selection.
 This is the same as setting the CONTENT\_TYPE() key on the property.

\item  \verb|int = obj.GetContentType ()| -  Get or set the content type of the selection.
 This is the same as setting the CONTENT\_TYPE() key on the property.

\item  \verb|obj.SetFieldType (int type)| -  Get or set the field type of the selection.
 This is the same as setting the FIELD\_TYPE() key on the property.

\item  \verb|int = obj.GetFieldType ()| -  Get or set the field type of the selection.
 This is the same as setting the FIELD\_TYPE() key on the property.

\item  \verb|obj.SetSelectedProp (vtkProp prop)| -  Get or set the prop of the selection.
 This is the same as setting the PROP() key on the property.

\item  \verb|vtkProp = obj.GetSelectedProp ()| -  Get or set the prop of the selection.
 This is the same as setting the PROP() key on the property.

\item  \verb|obj.UnionSelectionList (vtkSelectionNode other)| -  Merges the selection list between self and the other. Assumes that both has
 identical properties.

\item  \verb|bool = obj.EqualProperties (vtkSelectionNode other, bool fullcomparetrue)| -  Compares Properties of self and other to ensure that they are exactly same.

\end{itemize}
