\section{vtkImplicitVolume}

\subsection{Usage}

 vtkImplicitVolume treats a volume (e.g., structured point dataset)
 as if it were an implicit function. This means it computes a function
 value and gradient. vtkImplicitVolume is a concrete implementation of 
 vtkImplicitFunction.

 vtkImplicitDataSet computes the function (at the point x) by performing 
 cell interpolation. That is, it finds the cell containing x, and then
 uses the cell's interpolation functions to compute an interpolated
 scalar value at x. (A similar approach is used to find the
 gradient, if requested.) Points outside of the dataset are assigned 
 the value of the ivar OutValue, and the gradient value OutGradient.

To create an instance of class vtkImplicitVolume, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkImplicitVolume
\end{verbatim}
\subsection{Methods}

The class vtkImplicitVolume has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkImplicitVolume class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkImplicitVolume = obj.NewInstance ()|

\item  \verb|vtkImplicitVolume = obj.SafeDownCast (vtkObject o)|

\item  \verb|long = obj.GetMTime ()| -  Returns the mtime also considering the volume.  This also calls Update
 on the volume, and it therefore must be called before the function is
 evaluated.

\item  \verb|double = obj.EvaluateFunction (double x[3])|

\item  \verb|double = obj.EvaluateFunction (double x, double y, double z)|

\item  \verb|obj.EvaluateGradient (double x[3], double n[3])|

\item  \verb|obj.SetVolume (vtkImageData )| -  Specify the volume for the implicit function.

\item  \verb|vtkImageData = obj.GetVolume ()| -  Specify the volume for the implicit function.

\item  \verb|obj.SetOutValue (double )| -  Set the function value to use for points outside of the dataset.

\item  \verb|double = obj.GetOutValue ()| -  Set the function value to use for points outside of the dataset.

\item  \verb|obj.SetOutGradient (double , double , double )| -  Set the function gradient to use for points outside of the dataset.

\item  \verb|obj.SetOutGradient (double  a[3])| -  Set the function gradient to use for points outside of the dataset.

\item  \verb|double = obj. GetOutGradient ()| -  Set the function gradient to use for points outside of the dataset.

\end{itemize}
