\section{vtkBSPIntersections}

\subsection{Usage}

    Given an axis aligned binary spatial partitioning described by a
    vtkBSPCuts object, perform intersection queries on various
    geometric entities with regions of the spatial partitioning.


To create an instance of class vtkBSPIntersections, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkBSPIntersections
\end{verbatim}
\subsection{Methods}

The class vtkBSPIntersections has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkBSPIntersections class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkBSPIntersections = obj.NewInstance ()|

\item  \verb|vtkBSPIntersections = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetCuts (vtkBSPCuts cuts)|

\item  \verb|vtkBSPCuts = obj.GetCuts ()|

\item  \verb|int = obj.GetBounds (double bounds)|

\item  \verb|int = obj.GetNumberOfRegions ()|

\item  \verb|int = obj.GetRegionBounds (int regionID, double bounds[6])|

\item  \verb|int = obj.GetRegionDataBounds (int regionID, double bounds[6])|

\item  \verb|int = obj.IntersectsBox (int regionId, double x)| -     Determine whether a region of the spatial decomposition 
    intersects an axis aligned box.

\item  \verb|int = obj.IntersectsBox (int regionId, double xmin, double xmax, double ymin, double ymax, double zmin, double zmax)| -     Determine whether a region of the spatial decomposition 
    intersects an axis aligned box.

\item  \verb|int = obj.IntersectsBox (int ids, int len, double x)| -     Compute a list of the Ids of all regions that 
    intersect the specified axis aligned box.
    Returns: the number of ids in the list.

\item  \verb|int = obj.IntersectsBox (int ids, int len, double x0, double x1, double y0, double y1, double z0, double z1)| -     Compute a list of the Ids of all regions that 
    intersect the specified axis aligned box.
    Returns: the number of ids in the list.

\item  \verb|int = obj.IntersectsSphere2 (int regionId, double x, double y, double z, double rSquared)| -     Determine whether a region of the spatial decomposition 
    intersects a sphere, given the center of the sphere 
    and the square of it's radius.

\item  \verb|int = obj.IntersectsSphere2 (int ids, int len, double x, double y, double z, double rSquared)| -     Compute a list of the Ids of all regions that 
    intersect the specified sphere.  The sphere is given
    by it's center and the square of it's radius.
    Returns: the number of ids in the list.

\item  \verb|int = obj.IntersectsCell (int regionId, vtkCell cell, int cellRegion)| -     Determine whether a region of the spatial decomposition
    intersects the given cell.  If you already
    know the region that the cell centroid lies in, provide 
    that as the last argument to make the computation quicker.

\item  \verb|int = obj.IntersectsCell (int ids, int len, vtkCell cell, int cellRegion)| -     Compute a list of the Ids of all regions that
    intersect the given cell.  If you alrady
    know the region that the cell centroid lies in, provide
    that as the last argument to make the computation quicker.
    Returns the number of regions the cell intersects.

\item  \verb|int = obj.GetComputeIntersectionsUsingDataBounds ()|

\item  \verb|obj.SetComputeIntersectionsUsingDataBounds (int c)|

\item  \verb|obj.ComputeIntersectionsUsingDataBoundsOn ()|

\item  \verb|obj.ComputeIntersectionsUsingDataBoundsOff ()|

\end{itemize}
