\section{vtkKdTreePointLocator}

\subsection{Usage}

 vtkKdTreePointLocator is a wrapper class that derives from
 vtkAbstractPointLocator and calls the search functions in vtkKdTree.

To create an instance of class vtkKdTreePointLocator, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkKdTreePointLocator
\end{verbatim}
\subsection{Methods}

The class vtkKdTreePointLocator has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkKdTreePointLocator class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkKdTreePointLocator = obj.NewInstance ()|

\item  \verb|vtkKdTreePointLocator = obj.SafeDownCast (vtkObject o)|

\item  \verb|vtkIdType = obj.FindClosestPoint (double x[3])| -  Given a position x, return the id of the point closest to it. Alternative
 method requires separate x-y-z values.
 These methods are thread safe if BuildLocator() is directly or
 indirectly called from a single thread first.

\item  \verb|obj.FindClosestNPoints (int N, double x[3], vtkIdList result)| -  Find the closest N points to a position. This returns the closest
 N points to a position. A faster method could be created that returned
 N close points to a position, but necessarily the exact N closest.
 The returned points are sorted from closest to farthest.
 These methods are thread safe if BuildLocator() is directly or
 indirectly called from a single thread first.

\item  \verb|obj.FindPointsWithinRadius (double R, double x[3], vtkIdList result)| -  Find all points within a specified radius R of position x.
 The result is not sorted in any specific manner.
 These methods are thread safe if BuildLocator() is directly or
 indirectly called from a single thread first.

\item  \verb|obj.FreeSearchStructure ()| -  See vtkLocator interface documentation.
 These methods are not thread safe.

\item  \verb|obj.BuildLocator ()| -  See vtkLocator interface documentation.
 These methods are not thread safe.

\item  \verb|obj.GenerateRepresentation (int level, vtkPolyData pd)| -  See vtkLocator interface documentation.
 These methods are not thread safe.

\end{itemize}
