\section{vtkStructuredGrid}

\subsection{Usage}

 vtkStructuredGrid is a data object that is a concrete implementation of
 vtkDataSet. vtkStructuredGrid represents a geometric structure that is a
 topologically regular array of points. The topology is that of a cube that
 has been subdivided into a regular array of smaller cubes. Each point/cell
 can be addressed with i-j-k indices. Examples include finite difference 
 grids.

 The order and number of points must match that specified by the dimensions
 of the grid. The point order increases in i fastest (from 0<=i<dims[0]),
 then j (0<=j<dims[1]), then k (0<=k<dims[2]) where dims[] are the
 dimensions of the grid in the i-j-k topological directions. The number of
 points is dims[0]*dims[1]*dims[2]. The same is true for the cells of the
 grid. The order and number of cells must match that specified by the
 dimensions of the grid. The cell order increases in i fastest (from
 0<=i<(dims[0]-1)), then j (0<=j<(dims[1]-1)), then k (0<=k<(dims[2]-1))
 The number of cells is (dims[0]-1)*(dims[1]-1)*(dims[2]-1).
 
 A unusual feature of vtkStructuredGrid is the ability to blank, 
 or ''turn-off'' points and cells in the dataset. This is controlled by 
 defining a ''blanking array'' whose values (0,1) specify whether
 a point should be blanked or not.

To create an instance of class vtkStructuredGrid, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkStructuredGrid
\end{verbatim}
\subsection{Methods}

The class vtkStructuredGrid has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkStructuredGrid class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkStructuredGrid = obj.NewInstance ()|

\item  \verb|vtkStructuredGrid = obj.SafeDownCast (vtkObject o)|

\item  \verb|int = obj.GetDataObjectType ()| -  Copy the geometric and topological structure of an input poly data object.

\item  \verb|obj.CopyStructure (vtkDataSet ds)| -  Copy the geometric and topological structure of an input poly data object.

\item  \verb|vtkIdType = obj.GetNumberOfPoints ()| -  Standard vtkDataSet API methods. See vtkDataSet for more information.

\item  \verb|double = obj.GetPoint (vtkIdType ptId)| -  Standard vtkDataSet API methods. See vtkDataSet for more information.

\item  \verb|obj.GetPoint (vtkIdType ptId, double p[3])| -  Standard vtkDataSet API methods. See vtkDataSet for more information.

\item  \verb|vtkCell = obj.GetCell (vtkIdType cellId)| -  Standard vtkDataSet API methods. See vtkDataSet for more information.

\item  \verb|obj.GetCell (vtkIdType cellId, vtkGenericCell cell)| -  Standard vtkDataSet API methods. See vtkDataSet for more information.

\item  \verb|obj.GetCellBounds (vtkIdType cellId, double bounds[6])| -  Standard vtkDataSet API methods. See vtkDataSet for more information.

\item  \verb|int = obj.GetCellType (vtkIdType cellId)| -  Standard vtkDataSet API methods. See vtkDataSet for more information.

\item  \verb|vtkIdType = obj.GetNumberOfCells ()| -  Standard vtkDataSet API methods. See vtkDataSet for more information.

\item  \verb|obj.GetCellPoints (vtkIdType cellId, vtkIdList ptIds)| -  Standard vtkDataSet API methods. See vtkDataSet for more information.

\item  \verb|obj.GetPointCells (vtkIdType ptId, vtkIdList cellIds)| -  Standard vtkDataSet API methods. See vtkDataSet for more information.

\item  \verb|obj.Initialize ()| -  Standard vtkDataSet API methods. See vtkDataSet for more information.

\item  \verb|int = obj.GetMaxCellSize ()| -  Standard vtkDataSet API methods. See vtkDataSet for more information.

\item  \verb|obj.GetCellNeighbors (vtkIdType cellId, vtkIdList ptIds, vtkIdList cellIds)| -  Standard vtkDataSet API methods. See vtkDataSet for more information.

\item  \verb|obj.GetScalarRange (double range[2])| -  Standard vtkDataSet API methods. See vtkDataSet for more information.

\item  \verb|double = obj.GetScalarRange ()| -  following methods are specific to structured grid

\item  \verb|obj.SetDimensions (int i, int j, int k)| -  following methods are specific to structured grid

\item  \verb|obj.SetDimensions (int dim[3])| -  following methods are specific to structured grid

\item  \verb|int = obj.GetDimensions ()| -  Get dimensions of this structured points dataset.

\item  \verb|obj.GetDimensions (int dim[3])| -  Get dimensions of this structured points dataset.

\item  \verb|int = obj.GetDataDimension ()| -  Return the dimensionality of the data.

\item  \verb|obj.SetExtent (int extent[6])| -  Different ways to set the extent of the data array.  The extent
 should be set before the ''Scalars'' are set or allocated.
 The Extent is stored  in the order (X, Y, Z).

\item  \verb|obj.SetExtent (int x1, int x2, int y1, int y2, int z1, int z2)| -  Different ways to set the extent of the data array.  The extent
 should be set before the ''Scalars'' are set or allocated.
 The Extent is stored  in the order (X, Y, Z).

\item  \verb|int = obj. GetExtent ()| -  Different ways to set the extent of the data array.  The extent
 should be set before the ''Scalars'' are set or allocated.
 The Extent is stored  in the order (X, Y, Z).

\item  \verb|long = obj.GetActualMemorySize ()| -  Return the actual size of the data in kilobytes. This number
 is valid only after the pipeline has updated. The memory size
 returned is guaranteed to be greater than or equal to the
 memory required to represent the data (e.g., extra space in
 arrays, etc. are not included in the return value). THIS METHOD
 IS THREAD SAFE.

\item  \verb|obj.ShallowCopy (vtkDataObject src)| -  Shallow and Deep copy.

\item  \verb|obj.DeepCopy (vtkDataObject src)| -  Shallow and Deep copy.

\item  \verb|int = obj.GetExtentType ()| -  Methods for supporting blanking of cells. Blanking turns on or off
 points in the structured grid, and hence the cells connected to them.
 These methods should be called only after the dimensions of the
 grid are set.

\item  \verb|obj.BlankPoint (vtkIdType ptId)| -  Methods for supporting blanking of cells. Blanking turns on or off
 points in the structured grid, and hence the cells connected to them.
 These methods should be called only after the dimensions of the
 grid are set.

\item  \verb|obj.UnBlankPoint (vtkIdType ptId)| -  Methods for supporting blanking of cells. Blanking turns on or off
 points in the structured grid, and hence the cells connected to them.
 These methods should be called only after the dimensions of the
 grid are set.

\item  \verb|obj.BlankCell (vtkIdType ptId)| -  Methods for supporting blanking of cells. Blanking turns on or off
 cells in the structured grid, and hence the cells connected to them.
 These methods should be called only after the dimensions of the
 grid are set.

\item  \verb|obj.UnBlankCell (vtkIdType ptId)| -  Methods for supporting blanking of cells. Blanking turns on or off
 cells in the structured grid, and hence the cells connected to them.
 These methods should be called only after the dimensions of the
 grid are set.

\item  \verb|vtkUnsignedCharArray = obj.GetPointVisibilityArray ()| -  Get the array that defines the blanking (visibility) of each point.

\item  \verb|obj.SetPointVisibilityArray (vtkUnsignedCharArray pointVisibility)| -  Set an array that defines the (blanking) visibility of the points 
 in the grid. Make sure that length of the visibility array matches 
 the number of points in the grid.

\item  \verb|vtkUnsignedCharArray = obj.GetCellVisibilityArray ()| -  Get the array that defines the blanking (visibility) of each cell.

\item  \verb|obj.SetCellVisibilityArray (vtkUnsignedCharArray pointVisibility)| -  Set an array that defines the (blanking) visibility of the cells 
 in the grid. Make sure that length of the visibility array matches 
 the number of points in the grid.

\item  \verb|char = obj.IsPointVisible (vtkIdType ptId)| -  Return non-zero value if specified point is visible.
 These methods should be called only after the dimensions of the
 grid are set.

\item  \verb|char = obj.IsCellVisible (vtkIdType cellId)| -  Return non-zero value if specified point is visible.
 These methods should be called only after the dimensions of the
 grid are set.

\item  \verb|char = obj.GetPointBlanking ()| -  Returns 1 if there is any visibility constraint on the points,
 0 otherwise.

\item  \verb|char = obj.GetCellBlanking ()| -  Returns 1 if there is any visibility constraint on the cells,
 0 otherwise.

\item  \verb|obj.Crop ()| -  Reallocates and copies to set the Extent to the UpdateExtent.
 This is used internally when the exact extent is requested, 
 and the source generated more than the update extent. 

\item  \verb|obj.GetPoint (int i, int j, int k, double p[3], bool adjustForExtenttrue)| -  Get a point in the grid. If adjustForExtent is true, (i,j,k) is 
 interpreted as a position relative to the beginning of the extent.
 If adjustForExtent is false, (i,j,k) is interpreted literally
 and the (i,j,k) point of the grid is returned regardless of the 
 extent beginning.
 The point coordinate is returned in 'p'.
 The default adjustForExtent is true.

\end{itemize}
