\section{vtkCompassWidget}

\subsection{Usage}

 The vtkCompassWidget is used to adjust a scalar value in an 
 application. Note that the actual appearance of the widget depends on
 the specific representation for the widget.
 
 To use this widget, set the widget representation. (the details may
 vary depending on the particulars of the representation). 


 .SECTION Event Bindings
 By default, the widget responds to the following VTK events (i.e., it
 watches the vtkRenderWindowInteractor for these events):
 \begin{verbatim}
 If the slider bead is selected:
   LeftButtonPressEvent - select slider 
   LeftButtonReleaseEvent - release slider 
   MouseMoveEvent - move slider
 \end{verbatim}

 Note that the event bindings described above can be changed using this
 class's vtkWidgetEventTranslator. This class translates VTK events 
 into the vtkCompassWidget's widget events:
 \begin{verbatim}
   vtkWidgetEvent::Select -- some part of the widget has been selected
   vtkWidgetEvent::EndSelect -- the selection process has completed
   vtkWidgetEvent::Move -- a request for slider motion has been invoked
 \end{verbatim}

 In turn, when these widget events are processed, the vtkCompassWidget
 invokes the following VTK events on itself (which observers can listen for):
 \begin{verbatim}
   vtkCommand::StartInteractionEvent (on vtkWidgetEvent::Select)
   vtkCommand::EndInteractionEvent (on vtkWidgetEvent::EndSelect)
   vtkCommand::InteractionEvent (on vtkWidgetEvent::Move)
 \end{verbatim}


To create an instance of class vtkCompassWidget, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkCompassWidget
\end{verbatim}
\subsection{Methods}

The class vtkCompassWidget has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkCompassWidget class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()| -  Standard macros.

\item  \verb|int = obj.IsA (string name)| -  Standard macros.

\item  \verb|vtkCompassWidget = obj.NewInstance ()| -  Standard macros.

\item  \verb|vtkCompassWidget = obj.SafeDownCast (vtkObject o)| -  Standard macros.

\item  \verb|obj.SetRepresentation (vtkCompassRepresentation r)| -  Create the default widget representation if one is not set. 

\item  \verb|obj.CreateDefaultRepresentation ()| -  Create the default widget representation if one is not set. 

\item  \verb|double = obj.GetHeading ()| -  Get the value for this widget. 

\item  \verb|obj.SetHeading (double v)| -  Get the value for this widget. 

\item  \verb|double = obj.GetTilt ()| -  Get the value for this widget. 

\item  \verb|obj.SetTilt (double t)| -  Get the value for this widget. 

\item  \verb|double = obj.GetDistance ()| -  Get the value for this widget. 

\item  \verb|obj.SetDistance (double t)| -  Get the value for this widget. 

\end{itemize}
