\section{vtkOutlineSource}

\subsection{Usage}

 vtkOutlineSource creates a wireframe outline around a
 user-specified bounding box.  The outline may be created aligned
 with the {x,y,z} axis - in which case it is defined by the 6 bounds
 {xmin,xmax,ymin,ymax,zmin,zmax} via SetBounds(). Alternatively, the
 box may be arbitrarily aligned, in which case it should be set via
 the SetCorners() member.

To create an instance of class vtkOutlineSource, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkOutlineSource
\end{verbatim}
\subsection{Methods}

The class vtkOutlineSource has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkOutlineSource class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkOutlineSource = obj.NewInstance ()|

\item  \verb|vtkOutlineSource = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetBoxType (int )| -  Set box type to AxisAligned (default) or Oriented.
 Use the method SetBounds() with AxisAligned mode, and SetCorners() 
 with Oriented mode.

\item  \verb|int = obj.GetBoxType ()| -  Set box type to AxisAligned (default) or Oriented.
 Use the method SetBounds() with AxisAligned mode, and SetCorners() 
 with Oriented mode.

\item  \verb|obj.SetBoxTypeToAxisAligned ()| -  Set box type to AxisAligned (default) or Oriented.
 Use the method SetBounds() with AxisAligned mode, and SetCorners() 
 with Oriented mode.

\item  \verb|obj.SetBoxTypeToOriented ()| -  Specify the bounds of the box to be used in Axis Aligned mode.

\item  \verb|obj.SetBounds (double , double , double , double , double , double )| -  Specify the bounds of the box to be used in Axis Aligned mode.

\item  \verb|obj.SetBounds (double  a[6])| -  Specify the bounds of the box to be used in Axis Aligned mode.

\item  \verb|double = obj. GetBounds ()| -  Specify the bounds of the box to be used in Axis Aligned mode.

\item  \verb|obj.SetCorners (double  [24])| -  Specify the corners of the outline when in Oriented mode, the
 values are supplied as 8*3 double values The correct corner
 ordering is using {x,y,z} convention for the unit cube as follows:
 {0,0,0},{1,0,0},{0,1,0},{1,1,0},{0,0,1},{1,0,1},{0,1,1},{1,1,1}.

\item  \verb|double = obj. GetCorners ()| -  Specify the corners of the outline when in Oriented mode, the
 values are supplied as 8*3 double values The correct corner
 ordering is using {x,y,z} convention for the unit cube as follows:
 {0,0,0},{1,0,0},{0,1,0},{1,1,0},{0,0,1},{1,0,1},{0,1,1},{1,1,1}.

\item  \verb|obj.SetGenerateFaces (int )| -  Generate solid faces for the box. This is off by default.

\item  \verb|obj.GenerateFacesOn ()| -  Generate solid faces for the box. This is off by default.

\item  \verb|obj.GenerateFacesOff ()| -  Generate solid faces for the box. This is off by default.

\item  \verb|int = obj.GetGenerateFaces ()| -  Generate solid faces for the box. This is off by default.

\end{itemize}
