\section{vtkGeoGraticule}

\subsection{Usage}

 This filter generates polydata to illustrate the distortions introduced
 by a map projection. The level parameter specifies the number of lines
 to be drawn. Poles are treated differently than other regions; hence the
 use of a Level parameter instead of a NumberOfLines parameter.
 The latitude and longitude are specified as half-open intervals with units
 of degrees. By default the latitude bounds are [-90,90[ and the longitude
 bounds are [0,180[.

To create an instance of class vtkGeoGraticule, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkGeoGraticule
\end{verbatim}
\subsection{Methods}

The class vtkGeoGraticule has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkGeoGraticule class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkGeoGraticule = obj.NewInstance ()|

\item  \verb|vtkGeoGraticule = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetLatitudeBounds (double , double )| -  The latitude bounds of the graticule.

\item  \verb|obj.SetLatitudeBounds (double  a[2])| -  The latitude bounds of the graticule.

\item  \verb|double = obj. GetLatitudeBounds ()| -  The latitude bounds of the graticule.

\item  \verb|obj.SetLongitudeBounds (double , double )| -  The longitude bounds of the graticule.

\item  \verb|obj.SetLongitudeBounds (double  a[2])| -  The longitude bounds of the graticule.

\item  \verb|double = obj. GetLongitudeBounds ()| -  The longitude bounds of the graticule.

\item  \verb|obj.SetLatitudeLevel (int )| -  The frequency level of latitude lines.

\item  \verb|int = obj.GetLatitudeLevelMinValue ()| -  The frequency level of latitude lines.

\item  \verb|int = obj.GetLatitudeLevelMaxValue ()| -  The frequency level of latitude lines.

\item  \verb|int = obj.GetLatitudeLevel ()| -  The frequency level of latitude lines.

\item  \verb|obj.SetLongitudeLevel (int )| -  The frequency level of longitude lines.

\item  \verb|int = obj.GetLongitudeLevelMinValue ()| -  The frequency level of longitude lines.

\item  \verb|int = obj.GetLongitudeLevelMaxValue ()| -  The frequency level of longitude lines.

\item  \verb|int = obj.GetLongitudeLevel ()| -  The frequency level of longitude lines.

\item  \verb|obj.SetGeometryType (int )| -  Set//get the type(s) of cells that will be
 output by the filter. By default, polylines
 are output. You may also request quadrilaterals. 
 This is a bit vector of GeometryType enums.

\item  \verb|int = obj.GetGeometryType ()| -  Set//get the type(s) of cells that will be
 output by the filter. By default, polylines
 are output. You may also request quadrilaterals. 
 This is a bit vector of GeometryType enums.

\end{itemize}
