\section{vtkTextureMapToPlane}

\subsection{Usage}

 vtkTextureMapToPlane is a filter that generates 2D texture coordinates
 by mapping input dataset points onto a plane. The plane can either be
 user specified or generated automatically. (A least squares method is
 used to generate the plane automatically.)

 There are two ways you can specify the plane. The first is to provide a
 plane normal. In this case the points are projected to a plane, and the
 points are then mapped into the user specified s-t coordinate range. For
 more control, you can specify a plane with three points: an origin and two
 points defining the two axes of the plane. (This is compatible with the
 vtkPlaneSource.) Using the second method, the SRange and TRange vectors
 are ignored, since the presumption is that the user does not want to scale
 the texture coordinates; and you can adjust the origin and axes points to
 achieve the texture coordinate scaling you need. Note also that using the
 three point method the axes do not have to be orthogonal.

To create an instance of class vtkTextureMapToPlane, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkTextureMapToPlane
\end{verbatim}
\subsection{Methods}

The class vtkTextureMapToPlane has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkTextureMapToPlane class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkTextureMapToPlane = obj.NewInstance ()|

\item  \verb|vtkTextureMapToPlane = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetOrigin (double , double , double )| -  Specify a point defining the origin of the plane. Used in conjunction with
 the Point1 and Point2 ivars to specify a map plane.

\item  \verb|obj.SetOrigin (double  a[3])| -  Specify a point defining the origin of the plane. Used in conjunction with
 the Point1 and Point2 ivars to specify a map plane.

\item  \verb|double = obj. GetOrigin ()| -  Specify a point defining the origin of the plane. Used in conjunction with
 the Point1 and Point2 ivars to specify a map plane.

\item  \verb|obj.SetPoint1 (double , double , double )| -  Specify a point defining the first axis of the plane.

\item  \verb|obj.SetPoint1 (double  a[3])| -  Specify a point defining the first axis of the plane.

\item  \verb|double = obj. GetPoint1 ()| -  Specify a point defining the first axis of the plane.

\item  \verb|obj.SetPoint2 (double , double , double )| -  Specify a point defining the second axis of the plane.

\item  \verb|obj.SetPoint2 (double  a[3])| -  Specify a point defining the second axis of the plane.

\item  \verb|double = obj. GetPoint2 ()| -  Specify a point defining the second axis of the plane.

\item  \verb|obj.SetNormal (double , double , double )| -  Specify plane normal. An alternative way to specify a map plane. Using
 this method, the object will scale the resulting texture coordinate
 between the SRange and TRange specified.

\item  \verb|obj.SetNormal (double  a[3])| -  Specify plane normal. An alternative way to specify a map plane. Using
 this method, the object will scale the resulting texture coordinate
 between the SRange and TRange specified.

\item  \verb|double = obj. GetNormal ()| -  Specify plane normal. An alternative way to specify a map plane. Using
 this method, the object will scale the resulting texture coordinate
 between the SRange and TRange specified.

\item  \verb|obj.SetSRange (double , double )| -  Specify s-coordinate range for texture s-t coordinate pair.

\item  \verb|obj.SetSRange (double  a[2])| -  Specify s-coordinate range for texture s-t coordinate pair.

\item  \verb|double = obj. GetSRange ()| -  Specify s-coordinate range for texture s-t coordinate pair.

\item  \verb|obj.SetTRange (double , double )| -  Specify t-coordinate range for texture s-t coordinate pair.

\item  \verb|obj.SetTRange (double  a[2])| -  Specify t-coordinate range for texture s-t coordinate pair.

\item  \verb|double = obj. GetTRange ()| -  Specify t-coordinate range for texture s-t coordinate pair.

\item  \verb|obj.SetAutomaticPlaneGeneration (int )| -  Turn on/off automatic plane generation.

\item  \verb|int = obj.GetAutomaticPlaneGeneration ()| -  Turn on/off automatic plane generation.

\item  \verb|obj.AutomaticPlaneGenerationOn ()| -  Turn on/off automatic plane generation.

\item  \verb|obj.AutomaticPlaneGenerationOff ()| -  Turn on/off automatic plane generation.

\end{itemize}
