\section{vtkReflectionFilter}

\subsection{Usage}

 The vtkReflectionFilter reflects a data set across one of the
 planes formed by the data set's bounding box.
 Since it converts data sets into unstructured grids, it is not effeicient
 for structured data sets.

To create an instance of class vtkReflectionFilter, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkReflectionFilter
\end{verbatim}
\subsection{Methods}

The class vtkReflectionFilter has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkReflectionFilter class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkReflectionFilter = obj.NewInstance ()|

\item  \verb|vtkReflectionFilter = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetPlane (int )| -  Set the normal of the plane to use as mirror.

\item  \verb|int = obj.GetPlaneMinValue ()| -  Set the normal of the plane to use as mirror.

\item  \verb|int = obj.GetPlaneMaxValue ()| -  Set the normal of the plane to use as mirror.

\item  \verb|int = obj.GetPlane ()| -  Set the normal of the plane to use as mirror.

\item  \verb|obj.SetPlaneToX ()| -  Set the normal of the plane to use as mirror.

\item  \verb|obj.SetPlaneToY ()| -  Set the normal of the plane to use as mirror.

\item  \verb|obj.SetPlaneToZ ()| -  Set the normal of the plane to use as mirror.

\item  \verb|obj.SetPlaneToXMin ()| -  Set the normal of the plane to use as mirror.

\item  \verb|obj.SetPlaneToYMin ()| -  Set the normal of the plane to use as mirror.

\item  \verb|obj.SetPlaneToZMin ()| -  Set the normal of the plane to use as mirror.

\item  \verb|obj.SetPlaneToXMax ()| -  Set the normal of the plane to use as mirror.

\item  \verb|obj.SetPlaneToYMax ()| -  Set the normal of the plane to use as mirror.

\item  \verb|obj.SetPlaneToZMax ()| -  Set the normal of the plane to use as mirror.

\item  \verb|obj.SetCenter (double )| -  If the reflection plane is set to X, Y or Z, this variable
 is use to set the position of the plane.

\item  \verb|double = obj.GetCenter ()| -  If the reflection plane is set to X, Y or Z, this variable
 is use to set the position of the plane.

\item  \verb|obj.SetCopyInput (int )| -  If on (the default), copy the input geometry to the output. If off,
 the output will only contain the reflection.

\item  \verb|int = obj.GetCopyInput ()| -  If on (the default), copy the input geometry to the output. If off,
 the output will only contain the reflection.

\item  \verb|obj.CopyInputOn ()| -  If on (the default), copy the input geometry to the output. If off,
 the output will only contain the reflection.

\item  \verb|obj.CopyInputOff ()| -  If on (the default), copy the input geometry to the output. If off,
 the output will only contain the reflection.

\end{itemize}
