\section{vtkGeoInteractorStyle}

\subsection{Usage}

 vtkGeoInteractorStyle contains interaction capabilities for a geographic
 view including orbit, zoom, and tilt. It also includes a compass widget
 for changing view parameters.


To create an instance of class vtkGeoInteractorStyle, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkGeoInteractorStyle
\end{verbatim}
\subsection{Methods}

The class vtkGeoInteractorStyle has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkGeoInteractorStyle class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkGeoInteractorStyle = obj.NewInstance ()|

\item  \verb|vtkGeoInteractorStyle = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.OnEnter ()| -  Event bindings

\item  \verb|obj.OnLeave ()| -  Event bindings

\item  \verb|obj.OnMouseMove ()| -  Event bindings

\item  \verb|obj.OnLeftButtonUp ()| -  Event bindings

\item  \verb|obj.OnMiddleButtonUp ()| -  Event bindings

\item  \verb|obj.OnRightButtonUp ()| -  Event bindings

\item  \verb|obj.OnLeftButtonDown ()| -  Event bindings

\item  \verb|obj.OnMiddleButtonDown ()| -  Event bindings

\item  \verb|obj.OnRightButtonDown ()| -  Event bindings

\item  \verb|obj.OnChar ()| -  Event bindings

\item  \verb|obj.RubberBandZoom ()|

\item  \verb|obj.Pan ()|

\item  \verb|obj.Dolly ()|

\item  \verb|obj.RedrawRectangle ()|

\item  \verb|obj.StartState (int newstate)|

\item  \verb|vtkGeoCamera = obj.GetGeoCamera ()|

\item  \verb|obj.ResetCamera ()| -  This can be used to set the camera to the standard view of the earth.

\item  \verb|obj.WidgetInteraction (vtkObject caller)|

\item  \verb|obj.SetInteractor (vtkRenderWindowInteractor interactor)| -  Set/Get the Interactor wrapper being controlled by this object.
 (Satisfy superclass API.)

\item  \verb|int = obj.GetRayIntersection (double origin[3], double direction[3], double intersection[3])|

\item  \verb|obj.SetCurrentRenderer (vtkRenderer )| -  Override to make the renderer use this camera subclass

\item  \verb|bool = obj.GetLockHeading ()|

\item  \verb|obj.SetLockHeading (bool )|

\item  \verb|obj.LockHeadingOn ()|

\item  \verb|obj.LockHeadingOff ()|

\item  \verb|obj.ResetCameraClippingRange ()|

\end{itemize}
