\section{vtkMergeCells}

\subsection{Usage}

    Designed to work with distributed vtkDataSets, this class will take
    vtkDataSets and merge them back into a single vtkUnstructuredGrid.

    The vtkPoints object of the unstructured grid will have data type
    VTK\_FLOAT, regardless of the data type of the points of the
    input vtkDataSets.  If this is a problem, someone must let me know.

    It is assumed the different DataSets have the same field arrays.  If
    the name of a global point ID array is provided, this class will
    refrain from including duplicate points in the merged Ugrid.  This
    class differs from vtkAppendFilter in these ways: (1) it uses less
    memory than that class (which uses memory equal to twice the size
    of the final Ugrid) but requires that you know the size of the
    final Ugrid in advance (2) this class assumes the individual DataSets have
    the same field arrays, while vtkAppendFilter intersects the field
    arrays (3) this class knows duplicate points may be appearing in
    the DataSets and can filter those out, (4) this class is not a filter.

To create an instance of class vtkMergeCells, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkMergeCells
\end{verbatim}
\subsection{Methods}

The class vtkMergeCells has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkMergeCells class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkMergeCells = obj.NewInstance ()|

\item  \verb|vtkMergeCells = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetUnstructuredGrid (vtkUnstructuredGrid )|

\item  \verb|vtkUnstructuredGrid = obj.GetUnstructuredGrid ()|

\item  \verb|obj.SetTotalNumberOfCells (vtkIdType )|

\item  \verb|vtkIdType = obj.GetTotalNumberOfCells ()|

\item  \verb|obj.SetTotalNumberOfPoints (vtkIdType )|

\item  \verb|vtkIdType = obj.GetTotalNumberOfPoints ()|

\item  \verb|obj.SetUseGlobalIds (int )|

\item  \verb|int = obj.GetUseGlobalIds ()|

\item  \verb|obj.SetPointMergeTolerance (float )|

\item  \verb|float = obj.GetPointMergeToleranceMinValue ()|

\item  \verb|float = obj.GetPointMergeToleranceMaxValue ()|

\item  \verb|float = obj.GetPointMergeTolerance ()|

\item  \verb|obj.SetUseGlobalCellIds (int )|

\item  \verb|int = obj.GetUseGlobalCellIds ()|

\item  \verb|obj.SetMergeDuplicatePoints (int )|

\item  \verb|int = obj.GetMergeDuplicatePoints ()|

\item  \verb|obj.MergeDuplicatePointsOn ()|

\item  \verb|obj.MergeDuplicatePointsOff ()|

\item  \verb|obj.SetTotalNumberOfDataSets (int )|

\item  \verb|int = obj.GetTotalNumberOfDataSets ()|

\item  \verb|int = obj.MergeDataSet (vtkDataSet set)|

\item  \verb|obj.Finish ()|

\end{itemize}
