\section{vtkGeoAdaptiveArcs}

\subsection{Usage}


To create an instance of class vtkGeoAdaptiveArcs, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkGeoAdaptiveArcs
\end{verbatim}
\subsection{Methods}

The class vtkGeoAdaptiveArcs has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkGeoAdaptiveArcs class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkGeoAdaptiveArcs = obj.NewInstance ()|

\item  \verb|vtkGeoAdaptiveArcs = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetGlobeRadius (double )| -  The base radius used to determine the earth's surface.
 Default is the earth's radius in meters.
 TODO: Change this to take in a vtkGeoTerrain to get altitude.

\item  \verb|double = obj.GetGlobeRadius ()| -  The base radius used to determine the earth's surface.
 Default is the earth's radius in meters.
 TODO: Change this to take in a vtkGeoTerrain to get altitude.

\item  \verb|obj.SetMaximumPixelSeparation (double )| -  The maximum number of pixels between points on the arcs.
 If two adjacent points are farther than the threshold,
 the line segment will be subdivided such that each point
 is separated by at most the threshold.

\item  \verb|double = obj.GetMaximumPixelSeparation ()| -  The maximum number of pixels between points on the arcs.
 If two adjacent points are farther than the threshold,
 the line segment will be subdivided such that each point
 is separated by at most the threshold.

\item  \verb|obj.SetMinimumPixelSeparation (double )| -  The minimum number of pixels between points on the arcs.
 Points closer than the threshold will be skipped until
 a point farther than the minimum threshold is reached.

\item  \verb|double = obj.GetMinimumPixelSeparation ()| -  The minimum number of pixels between points on the arcs.
 Points closer than the threshold will be skipped until
 a point farther than the minimum threshold is reached.

\item  \verb|obj.SetRenderer (vtkRenderer ren)| -  The renderer used to estimate the number of pixels between
 points.

\item  \verb|vtkRenderer = obj.GetRenderer ()| -  The renderer used to estimate the number of pixels between
 points.

\item  \verb|long = obj.GetMTime ()| -  Return the modified time of this object.

\end{itemize}
