\section{vtkAssignAttribute}

\subsection{Usage}

 vtkAssignAttribute is use to label a field (vtkDataArray) as an attribute.
 A field name or an attribute to labeled can be specified. For example:
 @verbatim
 aa->Assign(''foo'', vtkDataSetAttributes::SCALARS, 
            vtkAssignAttribute::POINT\_DATA);
 @endverbatim
 tells vtkAssignAttribute to make the array in the point data called
 ''foo'' the active scalars. On the other hand,
 @verbatim
 aa->Assign(vtkDataSetAttributes::VECTORS, vtkDataSetAttributes::SCALARS, 
            vtkAssignAttribute::POINT\_DATA);
 @endverbatim
 tells vtkAssignAttribute to make the active vectors also the active
 scalars. The same can be done more easily from Tcl by using the Assign()
 method which takes strings:
 @verbatim
 aa Assign ''foo'' SCALARS POINT\_DATA 
 or
 aa Assign SCALARS VECTORS POINT\_DATA

 AttributeTypes: SCALARS, VECTORS, NORMALS, TCOORDS, TENSORS
 Attribute locations: POINT\_DATA, CELL\_DATA
 @endverbatim

To create an instance of class vtkAssignAttribute, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkAssignAttribute
\end{verbatim}
\subsection{Methods}

The class vtkAssignAttribute has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkAssignAttribute class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkAssignAttribute = obj.NewInstance ()|

\item  \verb|vtkAssignAttribute = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.Assign (int inputAttributeType, int attributeType, int attributeLoc)| -  Label an attribute as another attribute.

\item  \verb|obj.Assign (string fieldName, int attributeType, int attributeLoc)| -  Label an array as an attribute.

\item  \verb|obj.Assign (string name, string attributeType, string attributeLoc)| -  Helper method used by other language bindings. Allows the caller to
 specify arguments as strings instead of enums.

\end{itemize}
