\section{vtkDiskSource}

\subsection{Usage}

 vtkDiskSource creates a polygonal disk with a hole in the center. The 
 disk has zero height. The user can specify the inner and outer radius
 of the disk, and the radial and circumferential resolution of the 
 polygonal representation. 

To create an instance of class vtkDiskSource, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkDiskSource
\end{verbatim}
\subsection{Methods}

The class vtkDiskSource has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkDiskSource class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkDiskSource = obj.NewInstance ()|

\item  \verb|vtkDiskSource = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetInnerRadius (double )| -  Specify inner radius of hole in disc.

\item  \verb|double = obj.GetInnerRadiusMinValue ()| -  Specify inner radius of hole in disc.

\item  \verb|double = obj.GetInnerRadiusMaxValue ()| -  Specify inner radius of hole in disc.

\item  \verb|double = obj.GetInnerRadius ()| -  Specify inner radius of hole in disc.

\item  \verb|obj.SetOuterRadius (double )| -  Specify outer radius of disc.

\item  \verb|double = obj.GetOuterRadiusMinValue ()| -  Specify outer radius of disc.

\item  \verb|double = obj.GetOuterRadiusMaxValue ()| -  Specify outer radius of disc.

\item  \verb|double = obj.GetOuterRadius ()| -  Specify outer radius of disc.

\item  \verb|obj.SetRadialResolution (int )| -  Set the number of points in radius direction.

\item  \verb|int = obj.GetRadialResolutionMinValue ()| -  Set the number of points in radius direction.

\item  \verb|int = obj.GetRadialResolutionMaxValue ()| -  Set the number of points in radius direction.

\item  \verb|int = obj.GetRadialResolution ()| -  Set the number of points in radius direction.

\item  \verb|obj.SetCircumferentialResolution (int )| -  Set the number of points in circumferential direction.

\item  \verb|int = obj.GetCircumferentialResolutionMinValue ()| -  Set the number of points in circumferential direction.

\item  \verb|int = obj.GetCircumferentialResolutionMaxValue ()| -  Set the number of points in circumferential direction.

\item  \verb|int = obj.GetCircumferentialResolution ()| -  Set the number of points in circumferential direction.

\end{itemize}
