\section{vtkPlatonicSolidSource}

\subsection{Usage}

 vtkPlatonicSolidSource can generate each of the five Platonic solids:
 tetrahedron, cube, octahedron, icosahedron, and dodecahedron. Each of the
 solids is placed inside a sphere centered at the origin with radius 1.0.
 To use this class, simply specify the solid to create. Note that this
 source object creates cell scalars that are (integral value) face numbers.

To create an instance of class vtkPlatonicSolidSource, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkPlatonicSolidSource
\end{verbatim}
\subsection{Methods}

The class vtkPlatonicSolidSource has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkPlatonicSolidSource class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkPlatonicSolidSource = obj.NewInstance ()|

\item  \verb|vtkPlatonicSolidSource = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetSolidType (int )| -  Specify the type of PlatonicSolid solid to create.

\item  \verb|int = obj.GetSolidTypeMinValue ()| -  Specify the type of PlatonicSolid solid to create.

\item  \verb|int = obj.GetSolidTypeMaxValue ()| -  Specify the type of PlatonicSolid solid to create.

\item  \verb|int = obj.GetSolidType ()| -  Specify the type of PlatonicSolid solid to create.

\item  \verb|obj.SetSolidTypeToTetrahedron ()| -  Specify the type of PlatonicSolid solid to create.

\item  \verb|obj.SetSolidTypeToCube ()| -  Specify the type of PlatonicSolid solid to create.

\item  \verb|obj.SetSolidTypeToOctahedron ()| -  Specify the type of PlatonicSolid solid to create.

\item  \verb|obj.SetSolidTypeToIcosahedron ()| -  Specify the type of PlatonicSolid solid to create.

\item  \verb|obj.SetSolidTypeToDodecahedron ()|

\end{itemize}
