\section{vtkAppendCompositeDataLeaves}

\subsection{Usage}

 vtkAppendCompositeDataLeaves is a filter that takes input composite datasets with the same
 structure: (1) the same number of entries and -- if any children are composites -- the
 same constraint holds from them; and (2) the same type of dataset at each position.
 It then creates an output dataset with the same structure whose leaves contain all the
 cells from the datasets at the corresponding leaves of the input datasets.

 Currently, only input polydata and unstructured grids are handled; other types of
 leaf datasets will be ignored and their positions in the output dataset will be NULL pointers.
 Point attributes (i.e., scalars, vectors, normals, field data, etc.) are extracted 
 and appended only if all datasets have the point attributes available. 
 (For example, if one dataset has scalars but another does not, scalars will 
 not be appended.)


To create an instance of class vtkAppendCompositeDataLeaves, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkAppendCompositeDataLeaves
\end{verbatim}
\subsection{Methods}

The class vtkAppendCompositeDataLeaves has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkAppendCompositeDataLeaves class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkAppendCompositeDataLeaves = obj.NewInstance ()|

\item  \verb|vtkAppendCompositeDataLeaves = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.RemoveInput (vtkDataSet in)| -  Remove a dataset from the list of data to append.

\item  \verb|obj.SetAppendFieldData (int )| -  Set/get whether the field data of each dataset in the composite dataset is copied to the output.
 If AppendFieldData is non-zero, then field data arrays from all the inputs are added
 to the output. If there are duplicates, the array on the first input encountered is taken.

\item  \verb|int = obj.GetAppendFieldData ()| -  Set/get whether the field data of each dataset in the composite dataset is copied to the output.
 If AppendFieldData is non-zero, then field data arrays from all the inputs are added
 to the output. If there are duplicates, the array on the first input encountered is taken.

\item  \verb|obj.AppendFieldDataOn ()| -  Set/get whether the field data of each dataset in the composite dataset is copied to the output.
 If AppendFieldData is non-zero, then field data arrays from all the inputs are added
 to the output. If there are duplicates, the array on the first input encountered is taken.

\item  \verb|obj.AppendFieldDataOff ()| -  Set/get whether the field data of each dataset in the composite dataset is copied to the output.
 If AppendFieldData is non-zero, then field data arrays from all the inputs are added
 to the output. If there are duplicates, the array on the first input encountered is taken.

\end{itemize}
