\section{vtkProgrammableSource}

\subsection{Usage}

 vtkProgrammableSource is a source object that is programmable by the
 user. To use this object, you must specify a function that creates the
 output.  It is possible to generate an output dataset of any (concrete) 
 type; it is up to the function to properly initialize and define the 
 output. Typically, you use one of the methods to get a concrete output 
 type (e.g., GetPolyDataOutput() or GetStructuredPointsOutput()), and 
 then manipulate the output in the user-specified function.

 Example use of this include writing a function to read a data file or
 interface to another system. (You might want to do this in favor of
 deriving a new class.) Another important use of this class is that it
 allows users of interpreters (e.g., Tcl or Java) the ability to write
 source objects without having to recompile C++ code or generate new
 libraries.

To create an instance of class vtkProgrammableSource, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkProgrammableSource
\end{verbatim}
\subsection{Methods}

The class vtkProgrammableSource has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkProgrammableSource class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkProgrammableSource = obj.NewInstance ()|

\item  \verb|vtkProgrammableSource = obj.SafeDownCast (vtkObject o)|

\item  \verb|vtkPolyData = obj.GetPolyDataOutput ()| -  Get the output as a concrete type. This method is typically used by the
 writer of the source function to get the output as a particular type
 (i.e., it essentially does type casting). It is the users responsibility
 to know the correct type of the output data.

\item  \verb|vtkStructuredPoints = obj.GetStructuredPointsOutput ()| -  Get the output as a concrete type.

\item  \verb|vtkStructuredGrid = obj.GetStructuredGridOutput ()| -  Get the output as a concrete type.

\item  \verb|vtkUnstructuredGrid = obj.GetUnstructuredGridOutput ()| -  Get the output as a concrete type.

\item  \verb|vtkRectilinearGrid = obj.GetRectilinearGridOutput ()| -  Get the output as a concrete type.

\end{itemize}
