\section{vtkYoungsMaterialInterface}

\subsection{Usage}

 Reconstructs material interfaces from a mesh containing mixed cells (where several materials are mixed)
 this implementation is based on the youngs algorithm, generalized to arbitrary cell types and works
 on both 2D and 3D meshes. the main advantage of the youngs algorithm is it guarantees the material volume correctness.
 for 2D meshes, the AxisSymetric flag allows to switch between a pure 2D (plannar) algorithm and an axis symetric 2D algorithm
 handling volumes of revolution.

 .SECTION Thanks
 This file is part of the generalized Youngs material interface reconstruction algorithm contributed by <br>
 CEA/DIF - Commissariat a l'Energie Atomique, Centre DAM Ile-De-France <br>
 BP12, F-91297 Arpajon, France. <br>
 Implementation by Thierry Carrard (thierry.carrard@cea.fr)

To create an instance of class vtkYoungsMaterialInterface, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkYoungsMaterialInterface
\end{verbatim}
\subsection{Methods}

The class vtkYoungsMaterialInterface has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkYoungsMaterialInterface class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkYoungsMaterialInterface = obj.NewInstance ()|

\item  \verb|vtkYoungsMaterialInterface = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetInverseNormal (int )| -  Set/Get wether the normal vector has to be flipped.

\item  \verb|int = obj.GetInverseNormal ()| -  Set/Get wether the normal vector has to be flipped.

\item  \verb|obj.InverseNormalOn ()| -  Set/Get wether the normal vector has to be flipped.

\item  \verb|obj.InverseNormalOff ()| -  Set/Get wether the normal vector has to be flipped.

\item  \verb|obj.SetReverseMaterialOrder (int )| -  If this flag is on, material order in reversed. 
 Otherwise, materials are sorted in ascending order depending on the given ordering array.

\item  \verb|int = obj.GetReverseMaterialOrder ()| -  If this flag is on, material order in reversed. 
 Otherwise, materials are sorted in ascending order depending on the given ordering array.

\item  \verb|obj.ReverseMaterialOrderOn ()| -  If this flag is on, material order in reversed. 
 Otherwise, materials are sorted in ascending order depending on the given ordering array.

\item  \verb|obj.ReverseMaterialOrderOff ()| -  If this flag is on, material order in reversed. 
 Otherwise, materials are sorted in ascending order depending on the given ordering array.

\item  \verb|obj.SetOnionPeel (int )| -  Set/Get OnionPeel flag. if this flag is on, the normal vector of the first 
 material (which depends on material ordering) is used for all materials.

\item  \verb|int = obj.GetOnionPeel ()| -  Set/Get OnionPeel flag. if this flag is on, the normal vector of the first 
 material (which depends on material ordering) is used for all materials.

\item  \verb|obj.OnionPeelOn ()| -  Set/Get OnionPeel flag. if this flag is on, the normal vector of the first 
 material (which depends on material ordering) is used for all materials.

\item  \verb|obj.OnionPeelOff ()| -  Set/Get OnionPeel flag. if this flag is on, the normal vector of the first 
 material (which depends on material ordering) is used for all materials.

\item  \verb|obj.SetAxisSymetric (int )| -  Turns on/off AxisSymetric computation of 2D interfaces. 
 in axis symetric mode, 2D meshes are understood as volumes of revolution.

\item  \verb|int = obj.GetAxisSymetric ()| -  Turns on/off AxisSymetric computation of 2D interfaces. 
 in axis symetric mode, 2D meshes are understood as volumes of revolution.

\item  \verb|obj.AxisSymetricOn ()| -  Turns on/off AxisSymetric computation of 2D interfaces. 
 in axis symetric mode, 2D meshes are understood as volumes of revolution.

\item  \verb|obj.AxisSymetricOff ()| -  Turns on/off AxisSymetric computation of 2D interfaces. 
 in axis symetric mode, 2D meshes are understood as volumes of revolution.

\item  \verb|obj.SetUseFractionAsDistance (int )| -  when UseFractionAsDistance is true, the volume fraction is interpreted as the distance
 of the cutting plane from the origin.
 in axis symetric mode, 2D meshes are understood as volumes of revolution.

\item  \verb|int = obj.GetUseFractionAsDistance ()| -  when UseFractionAsDistance is true, the volume fraction is interpreted as the distance
 of the cutting plane from the origin.
 in axis symetric mode, 2D meshes are understood as volumes of revolution.

\item  \verb|obj.UseFractionAsDistanceOn ()| -  when UseFractionAsDistance is true, the volume fraction is interpreted as the distance
 of the cutting plane from the origin.
 in axis symetric mode, 2D meshes are understood as volumes of revolution.

\item  \verb|obj.UseFractionAsDistanceOff ()| -  when UseFractionAsDistance is true, the volume fraction is interpreted as the distance
 of the cutting plane from the origin.
 in axis symetric mode, 2D meshes are understood as volumes of revolution.

\item  \verb|obj.SetFillMaterial (int )| -  When FillMaterial is set to 1, the volume containing material is output and not only the interface surface.

\item  \verb|int = obj.GetFillMaterial ()| -  When FillMaterial is set to 1, the volume containing material is output and not only the interface surface.

\item  \verb|obj.FillMaterialOn ()| -  When FillMaterial is set to 1, the volume containing material is output and not only the interface surface.

\item  \verb|obj.FillMaterialOff ()| -  When FillMaterial is set to 1, the volume containing material is output and not only the interface surface.

\item  \verb|obj.SetTwoMaterialsOptimization (int )| -  Triggers some additional optimizations for cells containing only two materials. This option might produce different result than expected if the sum of volume fractions is not 1.

\item  \verb|int = obj.GetTwoMaterialsOptimization ()| -  Triggers some additional optimizations for cells containing only two materials. This option might produce different result than expected if the sum of volume fractions is not 1.

\item  \verb|obj.TwoMaterialsOptimizationOn ()| -  Triggers some additional optimizations for cells containing only two materials. This option might produce different result than expected if the sum of volume fractions is not 1.

\item  \verb|obj.TwoMaterialsOptimizationOff ()| -  Triggers some additional optimizations for cells containing only two materials. This option might produce different result than expected if the sum of volume fractions is not 1.

\item  \verb|obj.SetVolumeFractionRange (double , double )| -  Set/Get minimum and maximum volume fraction value. if a material fills a volume above the minimum value, the material is considered to be void. if a material fills a volume fraction beyond the maximum value it is considered as filling the whole volume.

\item  \verb|obj.SetVolumeFractionRange (double  a[2])| -  Set/Get minimum and maximum volume fraction value. if a material fills a volume above the minimum value, the material is considered to be void. if a material fills a volume fraction beyond the maximum value it is considered as filling the whole volume.

\item  \verb|double = obj. GetVolumeFractionRange ()| -  Set/Get minimum and maximum volume fraction value. if a material fills a volume above the minimum value, the material is considered to be void. if a material fills a volume fraction beyond the maximum value it is considered as filling the whole volume.

\item  \verb|obj.SetNumberOfMaterials (int n)| -  Sets/Gets the number of materials.

\item  \verb|int = obj.GetNumberOfMaterials ()| -  Sets/Gets the number of materials.

\item  \verb|obj.SetMaterialArrays (int i, string volumeFraction, string interfaceNormal, string materialOrdering)| -  Set ith Material arrays to be used as volume fraction, interface normal and material ordering. Each parameter name a cell array.

\item  \verb|obj.SetMaterialVolumeFractionArray (int i, string volume)| -  Set ith Material arrays to be used as volume fraction, interface normal and material ordering. Each parameter name a cell array.

\item  \verb|obj.SetMaterialNormalArray (int i, string normal)| -  Set ith Material arrays to be used as volume fraction, interface normal and material ordering. Each parameter name a cell array.

\item  \verb|obj.SetMaterialOrderingArray (int i, string ordering)| -  Set ith Material arrays to be used as volume fraction, interface normal and material ordering. Each parameter name a cell array.

\item  \verb|obj.RemoveAllMaterials ()| -  Removes all meterials previously added.

\end{itemize}
