\section{vtkAxes}

\subsection{Usage}

 vtkAxes creates three lines that form an x-y-z axes. The origin of the
 axes is user specified (0,0,0 is default), and the size is specified with
 a scale factor. Three scalar values are generated for the three lines and
 can be used (via color map) to indicate a particular coordinate axis.

To create an instance of class vtkAxes, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkAxes
\end{verbatim}
\subsection{Methods}

The class vtkAxes has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkAxes class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkAxes = obj.NewInstance ()|

\item  \verb|vtkAxes = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetOrigin (double , double , double )| -  Set the origin of the axes.

\item  \verb|obj.SetOrigin (double  a[3])| -  Set the origin of the axes.

\item  \verb|double = obj. GetOrigin ()| -  Set the origin of the axes.

\item  \verb|obj.SetScaleFactor (double )| -  Set the scale factor of the axes. Used to control size.

\item  \verb|double = obj.GetScaleFactor ()| -  Set the scale factor of the axes. Used to control size.

\item  \verb|obj.SetSymmetric (int )| -  If Symetric is on, the the axis continue to negative values.

\item  \verb|int = obj.GetSymmetric ()| -  If Symetric is on, the the axis continue to negative values.

\item  \verb|obj.SymmetricOn ()| -  If Symetric is on, the the axis continue to negative values.

\item  \verb|obj.SymmetricOff ()| -  If Symetric is on, the the axis continue to negative values.

\item  \verb|obj.SetComputeNormals (int )| -  Option for computing normals.  By default they are computed.

\item  \verb|int = obj.GetComputeNormals ()| -  Option for computing normals.  By default they are computed.

\item  \verb|obj.ComputeNormalsOn ()| -  Option for computing normals.  By default they are computed.

\item  \verb|obj.ComputeNormalsOff ()| -  Option for computing normals.  By default they are computed.

\end{itemize}
