\section{vtkThresholdTextureCoords}

\subsection{Usage}

 vtkThresholdTextureCoords is a filter that generates texture coordinates for
 any input dataset type given a threshold criterion. The criterion can take 
 three forms: 1) greater than a particular value (ThresholdByUpper()); 
 2) less than a particular value (ThresholdByLower(); or 3) between two 
 values (ThresholdBetween(). If the threshold criterion is satisfied, 
 the ''in'' texture coordinate will be set (this can be specified by the
 user). If the threshold criterion is not satisfied the ''out'' is set.

To create an instance of class vtkThresholdTextureCoords, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkThresholdTextureCoords
\end{verbatim}
\subsection{Methods}

The class vtkThresholdTextureCoords has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkThresholdTextureCoords class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkThresholdTextureCoords = obj.NewInstance ()|

\item  \verb|vtkThresholdTextureCoords = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.ThresholdByLower (double lower)| -  Criterion is cells whose scalars are less than lower threshold.

\item  \verb|obj.ThresholdByUpper (double upper)| -  Criterion is cells whose scalars are less than upper threshold.

\item  \verb|obj.ThresholdBetween (double lower, double upper)| -  Criterion is cells whose scalars are between lower and upper thresholds.

\item  \verb|double = obj.GetUpperThreshold ()| -  Return the upper and lower thresholds.

\item  \verb|double = obj.GetLowerThreshold ()| -  Return the upper and lower thresholds.

\item  \verb|obj.SetTextureDimension (int )| -  Set the desired dimension of the texture map.

\item  \verb|int = obj.GetTextureDimensionMinValue ()| -  Set the desired dimension of the texture map.

\item  \verb|int = obj.GetTextureDimensionMaxValue ()| -  Set the desired dimension of the texture map.

\item  \verb|int = obj.GetTextureDimension ()| -  Set the desired dimension of the texture map.

\item  \verb|obj.SetInTextureCoord (double , double , double )| -  Set the texture coordinate value for point satisfying threshold criterion.

\item  \verb|obj.SetInTextureCoord (double  a[3])| -  Set the texture coordinate value for point satisfying threshold criterion.

\item  \verb|double = obj. GetInTextureCoord ()| -  Set the texture coordinate value for point satisfying threshold criterion.

\item  \verb|obj.SetOutTextureCoord (double , double , double )| -  Set the texture coordinate value for point NOT satisfying threshold
  criterion.

\item  \verb|obj.SetOutTextureCoord (double  a[3])| -  Set the texture coordinate value for point NOT satisfying threshold
  criterion.

\item  \verb|double = obj. GetOutTextureCoord ()| -  Set the texture coordinate value for point NOT satisfying threshold
  criterion.

\end{itemize}
