\section{vtkDashedStreamLine}

\subsection{Usage}

 vtkDashedStreamLine is a filter that generates a ''dashed'' streamline for 
 an arbitrary dataset. The streamline consists of a series of dashes, each 
 of which represents (approximately) a constant time increment. Thus, in the
 resulting visual representation, relatively long dashes represent areas of 
 high velocity, and small dashes represent areas of low velocity.

 vtkDashedStreamLine introduces the instance variable DashFactor. 
 DashFactor interacts with its superclass' instance variable StepLength to
 create the dashes. DashFactor is the percentage of the StepLength line 
 segment that is visible. Thus, if the DashFactor=0.75, the dashes will be 
 ''three-quarters on'' and ''one-quarter off''.

To create an instance of class vtkDashedStreamLine, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkDashedStreamLine
\end{verbatim}
\subsection{Methods}

The class vtkDashedStreamLine has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkDashedStreamLine class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkDashedStreamLine = obj.NewInstance ()|

\item  \verb|vtkDashedStreamLine = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetDashFactor (double )| -  For each dash, specify the fraction of the dash that is ''on''. A factor
 of 1.0 will result in a continuous line, a factor of 0.5 will result in 
 dashed that are half on and half off.

\item  \verb|double = obj.GetDashFactorMinValue ()| -  For each dash, specify the fraction of the dash that is ''on''. A factor
 of 1.0 will result in a continuous line, a factor of 0.5 will result in 
 dashed that are half on and half off.

\item  \verb|double = obj.GetDashFactorMaxValue ()| -  For each dash, specify the fraction of the dash that is ''on''. A factor
 of 1.0 will result in a continuous line, a factor of 0.5 will result in 
 dashed that are half on and half off.

\item  \verb|double = obj.GetDashFactor ()| -  For each dash, specify the fraction of the dash that is ''on''. A factor
 of 1.0 will result in a continuous line, a factor of 0.5 will result in 
 dashed that are half on and half off.

\end{itemize}
