\section{vtkRearrangeFields}

\subsection{Usage}

 vtkRearrangeFields is used to copy/move fields (vtkDataArrays) between
 data object's field data, point data and cell data. To specify which
 fields are copied/moved, the user adds operations. There are two types
 of operations: 1. the type which copies/moves an attribute's data
 (i.e. the field will be copied but will not be an attribute in the
 target), 2. the type which copies/moves fields by name. For example:
 @verbatim
 rf->AddOperation(vtkRearrangeFields::COPY, ''foo'', 
                  vtkRearrangeFields::DATA\_OBJECT, 
                  vtkRearrangeFields::POINT\_DATA);
 @endverbatim
 adds an operation which copies a field (data array) called foo from
 the data object's field data to point data.
 From Tcl, the same operation can be added as follows:
 @verbatim
 rf AddOperation COPY foo DATA\_OBJECT POINT\_DATA
 @endverbatim
 The same can be done using Python and Java bindings by passing
 strings as arguments.
 @verbatim
 Operation types: COPY, MOVE
 AttributeTypes: SCALARS, VECTORS, NORMALS, TCOORDS, TENSORS
 Field data locations: DATA\_OBJECT, POINT\_DATA, CELL\_DATA
 @endverbatim

To create an instance of class vtkRearrangeFields, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkRearrangeFields
\end{verbatim}
\subsection{Methods}

The class vtkRearrangeFields has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkRearrangeFields class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkRearrangeFields = obj.NewInstance ()|

\item  \verb|vtkRearrangeFields = obj.SafeDownCast (vtkObject o)|

\item  \verb|int = obj.AddOperation (int operationType, int attributeType, int fromFieldLoc, int toFieldLoc)| -  Add an operation which copies an attribute's field (data array) from
 one field data to another. Returns an operation id which can later
 be used to remove the operation.

\item  \verb|int = obj.AddOperation (int operationType, string name, int fromFieldLoc, int toFieldLoc)| -  Add an operation which copies a field (data array) from one field 
 data to another. Returns an operation id which can later
 be used to remove the operation.

\item  \verb|int = obj.AddOperation (string operationType, string attributeType, string fromFieldLoc, string toFieldLoc)| -  Helper method used by other language bindings. Allows the caller to
 specify arguments as strings instead of enums.Returns an operation id 
 which can later be used to remove the operation.

\item  \verb|int = obj.RemoveOperation (int operationId)| -  Remove an operation with the given id.

\item  \verb|int = obj.RemoveOperation (int operationType, int attributeType, int fromFieldLoc, int toFieldLoc)| -  Remove an operation with the given signature. See AddOperation
 for details.

\item  \verb|int = obj.RemoveOperation (int operationType, string name, int fromFieldLoc, int toFieldLoc)| -  Remove an operation with the given signature. See AddOperation
 for details.

\item  \verb|int = obj.RemoveOperation (string operationType, string attributeType, string fromFieldLoc, string toFieldLoc)| -  Remove an operation with the given signature. See AddOperation
 for details.

\item  \verb|obj.RemoveAllOperations ()|

\end{itemize}
