\section{vtkAnnotationLink}

\subsection{Usage}

 vtkAnnotationLink is a simple source filter which outputs the
 vtkAnnotationLayers object stored internally.  Multiple objects may share
 the same annotation link filter and connect it to an internal pipeline so
 that if one object changes the annotation set, it will be pulled into all
 the other objects when their pipelines update.

 The shared vtkAnnotationLayers object (a collection of annotations) is
 shallow copied to output port 0.

 vtkAnnotationLink can also store a set of domain maps. A domain map is
 simply a table associating values between domains. The domain of each
 column is defined by the array name of the column. The domain maps are
 sent to a multi-block dataset in output port 1.

 Output ports 0 and 1 can be set as input ports 0 and 1 to
 vtkConvertSelectionDomain, which can use the domain maps to convert the
 domains of selections in the vtkAnnotationLayers to match a particular
 data object (set as port 2 on vtkConvertSelectionDomain).

 The shared vtkAnnotationLayers object also stores a ''current selection''
 normally interpreted as the interactive selection of an application.
 As a convenience, this selection is sent to output port 2 so that it
 can be connected to pipelines requiring a vtkSelection.

To create an instance of class vtkAnnotationLink, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkAnnotationLink
\end{verbatim}
\subsection{Methods}

The class vtkAnnotationLink has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkAnnotationLink class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkAnnotationLink = obj.NewInstance ()|

\item  \verb|vtkAnnotationLink = obj.SafeDownCast (vtkObject o)|

\item  \verb|vtkAnnotationLayers = obj.GetAnnotationLayers ()| -  The annotations to be shared.

\item  \verb|obj.SetAnnotationLayers (vtkAnnotationLayers layers)| -  The annotations to be shared.

\item  \verb|obj.SetCurrentSelection (vtkSelection sel)| -  Set or get the current selection in the annotation layers.

\item  \verb|vtkSelection = obj.GetCurrentSelection ()| -  Set or get the current selection in the annotation layers.

\item  \verb|obj.AddDomainMap (vtkTable map)| -  The domain mappings.

\item  \verb|obj.RemoveDomainMap (vtkTable map)| -  The domain mappings.

\item  \verb|obj.RemoveAllDomainMaps ()| -  The domain mappings.

\item  \verb|int = obj.GetNumberOfDomainMaps ()| -  The domain mappings.

\item  \verb|vtkTable = obj.GetDomainMap (int i)| -  The domain mappings.

\item  \verb|long = obj.GetMTime ()| -  Get the mtime of this object.

\end{itemize}
