\section{vtkRegularPolygonSource}

\subsection{Usage}

 vtkRegularPolygonSource is a source object that creates a single n-sided polygon and/or 
 polyline. The polygon is centered at a specified point, orthogonal to
 a specified normal, and with a circumscribing radius set by the user. The user can
 also specify the number of sides of the polygon ranging from [3,N].

 This object can be used for seeding streamlines or defining regions for clipping/cutting.

To create an instance of class vtkRegularPolygonSource, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkRegularPolygonSource
\end{verbatim}
\subsection{Methods}

The class vtkRegularPolygonSource has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkRegularPolygonSource class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()| -  Standard methods for instantiation, obtaining type and printing instance values.

\item  \verb|int = obj.IsA (string name)| -  Standard methods for instantiation, obtaining type and printing instance values.

\item  \verb|vtkRegularPolygonSource = obj.NewInstance ()| -  Standard methods for instantiation, obtaining type and printing instance values.

\item  \verb|vtkRegularPolygonSource = obj.SafeDownCast (vtkObject o)| -  Standard methods for instantiation, obtaining type and printing instance values.

\item  \verb|obj.SetNumberOfSides (int )| -  Set/Get the number of sides of the polygon. By default, the number of sides
 is set to six.

\item  \verb|int = obj.GetNumberOfSidesMinValue ()| -  Set/Get the number of sides of the polygon. By default, the number of sides
 is set to six.

\item  \verb|int = obj.GetNumberOfSidesMaxValue ()| -  Set/Get the number of sides of the polygon. By default, the number of sides
 is set to six.

\item  \verb|int = obj.GetNumberOfSides ()| -  Set/Get the number of sides of the polygon. By default, the number of sides
 is set to six.

\item  \verb|obj.SetCenter (double , double , double )| -  Set/Get the center of the polygon. By default, the center is set at the
 origin (0,0,0).

\item  \verb|obj.SetCenter (double  a[3])| -  Set/Get the center of the polygon. By default, the center is set at the
 origin (0,0,0).

\item  \verb|double = obj. GetCenter ()| -  Set/Get the center of the polygon. By default, the center is set at the
 origin (0,0,0).

\item  \verb|obj.SetNormal (double , double , double )| -  Set/Get the normal to the polygon. The ordering of the polygon will be
 counter-clockwise around the normal (i.e., using the right-hand rule).
 By default, the normal is set to (0,0,1).

\item  \verb|obj.SetNormal (double  a[3])| -  Set/Get the normal to the polygon. The ordering of the polygon will be
 counter-clockwise around the normal (i.e., using the right-hand rule).
 By default, the normal is set to (0,0,1).

\item  \verb|double = obj. GetNormal ()| -  Set/Get the normal to the polygon. The ordering of the polygon will be
 counter-clockwise around the normal (i.e., using the right-hand rule).
 By default, the normal is set to (0,0,1).

\item  \verb|obj.SetRadius (double )| -  Set/Get the radius of the polygon. By default, the radius is set to 0.5.

\item  \verb|double = obj.GetRadius ()| -  Set/Get the radius of the polygon. By default, the radius is set to 0.5.

\item  \verb|obj.SetGeneratePolygon (int )| -  Control whether a polygon is produced. By default, GeneratePolygon is enabled.

\item  \verb|int = obj.GetGeneratePolygon ()| -  Control whether a polygon is produced. By default, GeneratePolygon is enabled.

\item  \verb|obj.GeneratePolygonOn ()| -  Control whether a polygon is produced. By default, GeneratePolygon is enabled.

\item  \verb|obj.GeneratePolygonOff ()| -  Control whether a polygon is produced. By default, GeneratePolygon is enabled.

\item  \verb|obj.SetGeneratePolyline (int )| -  Control whether a polyline is produced. By default, GeneratePolyline is enabled.

\item  \verb|int = obj.GetGeneratePolyline ()| -  Control whether a polyline is produced. By default, GeneratePolyline is enabled.

\item  \verb|obj.GeneratePolylineOn ()| -  Control whether a polyline is produced. By default, GeneratePolyline is enabled.

\item  \verb|obj.GeneratePolylineOff ()| -  Control whether a polyline is produced. By default, GeneratePolyline is enabled.

\end{itemize}
