\section{vtkDataObjectGenerator}

\subsection{Usage}

 vtkDataObjectGenerator parses a string and produces dataobjects from the
 dataobject template names it sees in the string. For example, if the string
 contains ''ID1'' the generator will create a vtkImageData. ''UF1'', ''RG1'', 
 ''SG1'', ''PD1'', and ''UG1'' will produce vtkUniformGrid, vtkRectilinearGrid,
 vtkStructuredGrid, vtkPolyData and vtkUnstructuredGrid respectively.
 ''PD2'' will produce an alternate vtkPolyData. You 
 can compose composite datasets from the atomic ones listed above
 by placing them within one of the two composite dataset identifiers
 - ''MB{}'' or ''HB[]''. ''MB{ ID1 PD1 MB{} }'' for example will create a 
 vtkMultiBlockDataSet consisting of three blocks: image data, poly data, 
 multi-block (empty). Hierarchical Box data sets additionally require
 the notion of groups, declared within ''()'' braces, to specify AMR depth.
 ''HB[ (UF1)(UF1)(UF1) ]'' will create a vtkHierarchicalBoxDataSet representing
 an octree that is three levels deep, in which the firstmost cell in each level
 is refined.

To create an instance of class vtkDataObjectGenerator, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkDataObjectGenerator
\end{verbatim}
\subsection{Methods}

The class vtkDataObjectGenerator has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkDataObjectGenerator class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkDataObjectGenerator = obj.NewInstance ()|

\item  \verb|vtkDataObjectGenerator = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetProgram (string )| -  The string that will be parsed to specify a dataobject structure.

\item  \verb|string = obj.GetProgram ()| -  The string that will be parsed to specify a dataobject structure.

\end{itemize}
