\section{vtkIdFilter}

\subsection{Usage}

 vtkIdFilter is a filter to that generates scalars or field data
 using cell and point ids. That is, the point attribute data scalars
 or field data are generated from the point ids, and the cell
 attribute data scalars or field data are generated from the the
 cell ids.

 Typically this filter is used with vtkLabeledDataMapper (and possibly
 vtkSelectVisiblePoints) to create labels for points and cells, or labels
 for the point or cell data scalar values.

To create an instance of class vtkIdFilter, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkIdFilter
\end{verbatim}
\subsection{Methods}

The class vtkIdFilter has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkIdFilter class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkIdFilter = obj.NewInstance ()|

\item  \verb|vtkIdFilter = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetPointIds (int )| -  Enable/disable the generation of point ids. Default is on.

\item  \verb|int = obj.GetPointIds ()| -  Enable/disable the generation of point ids. Default is on.

\item  \verb|obj.PointIdsOn ()| -  Enable/disable the generation of point ids. Default is on.

\item  \verb|obj.PointIdsOff ()| -  Enable/disable the generation of point ids. Default is on.

\item  \verb|obj.SetCellIds (int )| -  Enable/disable the generation of point ids. Default is on.

\item  \verb|int = obj.GetCellIds ()| -  Enable/disable the generation of point ids. Default is on.

\item  \verb|obj.CellIdsOn ()| -  Enable/disable the generation of point ids. Default is on.

\item  \verb|obj.CellIdsOff ()| -  Enable/disable the generation of point ids. Default is on.

\item  \verb|obj.SetFieldData (int )| -  Set/Get the flag which controls whether to generate scalar data
 or field data. If this flag is off, scalar data is generated.
 Otherwise, field data is generated. Default is off.

\item  \verb|int = obj.GetFieldData ()| -  Set/Get the flag which controls whether to generate scalar data
 or field data. If this flag is off, scalar data is generated.
 Otherwise, field data is generated. Default is off.

\item  \verb|obj.FieldDataOn ()| -  Set/Get the flag which controls whether to generate scalar data
 or field data. If this flag is off, scalar data is generated.
 Otherwise, field data is generated. Default is off.

\item  \verb|obj.FieldDataOff ()| -  Set/Get the flag which controls whether to generate scalar data
 or field data. If this flag is off, scalar data is generated.
 Otherwise, field data is generated. Default is off.

\item  \verb|obj.SetIdsArrayName (string )| -  Set/Get the name of the Ids array if generated. By default the Ids
 are named ''vtkIdFilter\_Ids'', but this can be changed with this function.

\item  \verb|string = obj.GetIdsArrayName ()| -  Set/Get the name of the Ids array if generated. By default the Ids
 are named ''vtkIdFilter\_Ids'', but this can be changed with this function.

\end{itemize}
