\section{vtkCylinderSource}

\subsection{Usage}

 vtkCylinderSource creates a polygonal cylinder centered at Center;
 The axis of the cylinder is aligned along the global y-axis.
 The height and radius of the cylinder can be specified, as well as the
 number of sides. It is also possible to control whether the cylinder is
 open-ended or capped.

To create an instance of class vtkCylinderSource, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkCylinderSource
\end{verbatim}
\subsection{Methods}

The class vtkCylinderSource has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkCylinderSource class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkCylinderSource = obj.NewInstance ()|

\item  \verb|vtkCylinderSource = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetHeight (double )| -  Set the height of the cylinder. Initial value is 1.

\item  \verb|double = obj.GetHeightMinValue ()| -  Set the height of the cylinder. Initial value is 1.

\item  \verb|double = obj.GetHeightMaxValue ()| -  Set the height of the cylinder. Initial value is 1.

\item  \verb|double = obj.GetHeight ()| -  Set the height of the cylinder. Initial value is 1.

\item  \verb|obj.SetRadius (double )| -  Set the radius of the cylinder. Initial value is 0.5

\item  \verb|double = obj.GetRadiusMinValue ()| -  Set the radius of the cylinder. Initial value is 0.5

\item  \verb|double = obj.GetRadiusMaxValue ()| -  Set the radius of the cylinder. Initial value is 0.5

\item  \verb|double = obj.GetRadius ()| -  Set the radius of the cylinder. Initial value is 0.5

\item  \verb|obj.SetCenter (double , double , double )| -  Set/Get cylinder center. Initial value is (0.0,0.0,0.0)

\item  \verb|obj.SetCenter (double  a[3])| -  Set/Get cylinder center. Initial value is (0.0,0.0,0.0)

\item  \verb|double = obj. GetCenter ()| -  Set/Get cylinder center. Initial value is (0.0,0.0,0.0)

\item  \verb|obj.SetResolution (int )| -  Set the number of facets used to define cylinder. Initial value is 6.

\item  \verb|int = obj.GetResolutionMinValue ()| -  Set the number of facets used to define cylinder. Initial value is 6.

\item  \verb|int = obj.GetResolutionMaxValue ()| -  Set the number of facets used to define cylinder. Initial value is 6.

\item  \verb|int = obj.GetResolution ()| -  Set the number of facets used to define cylinder. Initial value is 6.

\item  \verb|obj.SetCapping (int )| -  Turn on/off whether to cap cylinder with polygons. Initial value is true.

\item  \verb|int = obj.GetCapping ()| -  Turn on/off whether to cap cylinder with polygons. Initial value is true.

\item  \verb|obj.CappingOn ()| -  Turn on/off whether to cap cylinder with polygons. Initial value is true.

\item  \verb|obj.CappingOff ()| -  Turn on/off whether to cap cylinder with polygons. Initial value is true.

\end{itemize}
