\section{vtkDataSetToDataObjectFilter}

\subsection{Usage}

 vtkDataSetToDataObjectFilter is an class that transforms a dataset into
 data object (i.e., a field). The field will have labeled data arrays
 corresponding to the topology, geometry, field data, and point and cell
 attribute data.

 You can control what portions of the dataset are converted into the
 output data object's field data. The instance variables Geometry,
 Topology, FieldData, PointData, and CellData are flags that control
 whether the dataset's geometry (e.g., points, spacing, origin);
 topology (e.g., cell connectivity, dimensions); the field data
 associated with the dataset's superclass data object; the dataset's
 point data attributes; and the dataset's cell data attributes. (Note:
 the data attributes include scalars, vectors, tensors, normals, texture
 coordinates, and field data.)

 The names used to create the field data are as follows. For vtkPolyData, 
 ''Points'', ''Verts'', ''Lines'', ''Polys'', and ''Strips''. For vtkUnstructuredGrid,
 ''Cells'' and ''CellTypes''. For vtkStructuredPoints, ''Dimensions'', ''Spacing'', 
 and ''Origin''. For vtkStructuredGrid, ''Points'' and ''Dimensions''. For
 vtkRectilinearGrid, ''XCoordinates'', ''YCoordinates'', and ''ZCoordinates''.
 for point attribute data, ''PointScalars'', ''PointVectors'', etc. For cell
 attribute data, ''CellScalars'', ''CellVectors'', etc. Field data arrays retain
 their original name.

To create an instance of class vtkDataSetToDataObjectFilter, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkDataSetToDataObjectFilter
\end{verbatim}
\subsection{Methods}

The class vtkDataSetToDataObjectFilter has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkDataSetToDataObjectFilter class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkDataSetToDataObjectFilter = obj.NewInstance ()|

\item  \verb|vtkDataSetToDataObjectFilter = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetGeometry (int )| -  Turn on/off the conversion of dataset geometry to a data object.

\item  \verb|int = obj.GetGeometry ()| -  Turn on/off the conversion of dataset geometry to a data object.

\item  \verb|obj.GeometryOn ()| -  Turn on/off the conversion of dataset geometry to a data object.

\item  \verb|obj.GeometryOff ()| -  Turn on/off the conversion of dataset geometry to a data object.

\item  \verb|obj.SetTopology (int )| -  Turn on/off the conversion of dataset topology to a data object.

\item  \verb|int = obj.GetTopology ()| -  Turn on/off the conversion of dataset topology to a data object.

\item  \verb|obj.TopologyOn ()| -  Turn on/off the conversion of dataset topology to a data object.

\item  \verb|obj.TopologyOff ()| -  Turn on/off the conversion of dataset topology to a data object.

\item  \verb|obj.SetFieldData (int )| -  Turn on/off the conversion of dataset field data to a data object.

\item  \verb|int = obj.GetFieldData ()| -  Turn on/off the conversion of dataset field data to a data object.

\item  \verb|obj.FieldDataOn ()| -  Turn on/off the conversion of dataset field data to a data object.

\item  \verb|obj.FieldDataOff ()| -  Turn on/off the conversion of dataset field data to a data object.

\item  \verb|obj.SetPointData (int )| -  Turn on/off the conversion of dataset point data to a data object.

\item  \verb|int = obj.GetPointData ()| -  Turn on/off the conversion of dataset point data to a data object.

\item  \verb|obj.PointDataOn ()| -  Turn on/off the conversion of dataset point data to a data object.

\item  \verb|obj.PointDataOff ()| -  Turn on/off the conversion of dataset point data to a data object.

\item  \verb|obj.SetCellData (int )| -  Turn on/off the conversion of dataset cell data to a data object.

\item  \verb|int = obj.GetCellData ()| -  Turn on/off the conversion of dataset cell data to a data object.

\item  \verb|obj.CellDataOn ()| -  Turn on/off the conversion of dataset cell data to a data object.

\item  \verb|obj.CellDataOff ()| -  Turn on/off the conversion of dataset cell data to a data object.

\end{itemize}
