\section{vtkGeoAlignedImageSource}

\subsection{Usage}

 vtkGeoAlignedImageSource uses a high resolution image to generate tiles
 at multiple resolutions in a hierarchy. It should be used as a source in
 vtkGeoAlignedImageRepresentation.

To create an instance of class vtkGeoAlignedImageSource, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkGeoAlignedImageSource
\end{verbatim}
\subsection{Methods}

The class vtkGeoAlignedImageSource has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkGeoAlignedImageSource class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkGeoAlignedImageSource = obj.NewInstance ()|

\item  \verb|vtkGeoAlignedImageSource = obj.SafeDownCast (vtkObject o)|

\item  \verb|bool = obj.FetchRoot (vtkGeoTreeNode node)| -  Fetch the root image.

\item  \verb|bool = obj.FetchChild (vtkGeoTreeNode parent, int index, vtkGeoTreeNode child)| -  Fetch a child image.

\item  \verb|vtkImageData = obj.GetImage ()| -  The high-resolution image to be used to cover the globe.

\item  \verb|obj.SetImage (vtkImageData image)| -  The high-resolution image to be used to cover the globe.

\item  \verb|obj.SetLatitudeRange (double , double )| -  The range of the input hi-res image.

\item  \verb|obj.SetLatitudeRange (double  a[2])| -  The range of the input hi-res image.

\item  \verb|double = obj. GetLatitudeRange ()| -  The range of the input hi-res image.

\item  \verb|obj.SetLongitudeRange (double , double )| -  The range of the input hi-res image.

\item  \verb|obj.SetLongitudeRange (double  a[2])| -  The range of the input hi-res image.

\item  \verb|double = obj. GetLongitudeRange ()| -  The range of the input hi-res image.

\item  \verb|obj.SetOverlap (double )| -  The overlap of adjacent tiles.

\item  \verb|double = obj.GetOverlapMinValue ()| -  The overlap of adjacent tiles.

\item  \verb|double = obj.GetOverlapMaxValue ()| -  The overlap of adjacent tiles.

\item  \verb|double = obj.GetOverlap ()| -  The overlap of adjacent tiles.

\item  \verb|obj.SetPowerOfTwoSize (bool )| -  Whether to force image sizes to a power of two.

\item  \verb|bool = obj.GetPowerOfTwoSize ()| -  Whether to force image sizes to a power of two.

\item  \verb|obj.PowerOfTwoSizeOn ()| -  Whether to force image sizes to a power of two.

\item  \verb|obj.PowerOfTwoSizeOff ()| -  Whether to force image sizes to a power of two.

\end{itemize}
