\section{vtkWarpLens}

\subsection{Usage}

 vtkWarpLens is a filter that modifies point coordinates by moving
 in accord with a lens distortion model.

To create an instance of class vtkWarpLens, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkWarpLens
\end{verbatim}
\subsection{Methods}

The class vtkWarpLens has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkWarpLens class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkWarpLens = obj.NewInstance ()|

\item  \verb|vtkWarpLens = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetKappa (double kappa)| -  Specify second order symmetric radial lens distortion parameter.
 This is obsoleted by newer instance variables.

\item  \verb|double = obj.GetKappa ()| -  Specify second order symmetric radial lens distortion parameter.
 This is obsoleted by newer instance variables.

\item  \verb|obj.SetCenter (double centerX, double centerY)| -  Specify the center of radial distortion in pixels.
 This is obsoleted by newer instance variables.

\item  \verb|double = obj.GetCenter ()| -  Specify the center of radial distortion in pixels.
 This is obsoleted by newer instance variables.

\item  \verb|obj.SetPrincipalPoint (double , double )| -  Specify the calibrated principal point of the camera/lens

\item  \verb|obj.SetPrincipalPoint (double  a[2])| -  Specify the calibrated principal point of the camera/lens

\item  \verb|double = obj. GetPrincipalPoint ()| -  Specify the calibrated principal point of the camera/lens

\item  \verb|obj.SetK1 (double )| -  Specify the symmetric radial distortion parameters for the lens

\item  \verb|double = obj.GetK1 ()| -  Specify the symmetric radial distortion parameters for the lens

\item  \verb|obj.SetK2 (double )| -  Specify the symmetric radial distortion parameters for the lens

\item  \verb|double = obj.GetK2 ()| -  Specify the symmetric radial distortion parameters for the lens

\item  \verb|obj.SetP1 (double )| -  Specify the decentering distortion parameters for the lens

\item  \verb|double = obj.GetP1 ()| -  Specify the decentering distortion parameters for the lens

\item  \verb|obj.SetP2 (double )| -  Specify the decentering distortion parameters for the lens

\item  \verb|double = obj.GetP2 ()| -  Specify the decentering distortion parameters for the lens

\item  \verb|obj.SetFormatWidth (double )| -  Specify the imager format width / height in mm

\item  \verb|double = obj.GetFormatWidth ()| -  Specify the imager format width / height in mm

\item  \verb|obj.SetFormatHeight (double )| -  Specify the imager format width / height in mm

\item  \verb|double = obj.GetFormatHeight ()| -  Specify the imager format width / height in mm

\item  \verb|obj.SetImageWidth (int )| -  Specify the image width / height in pixels

\item  \verb|int = obj.GetImageWidth ()| -  Specify the image width / height in pixels

\item  \verb|obj.SetImageHeight (int )| -  Specify the image width / height in pixels

\item  \verb|int = obj.GetImageHeight ()| -  Specify the image width / height in pixels

\end{itemize}
