\section{vtkTransformToGrid}

\subsection{Usage}

 vtkTransformToGrid takes any transform as input and produces a grid
 for use by a vtkGridTransform.  This can be used, for example, to 
 invert a grid transform, concatenate two grid transforms, or to
 convert a thin plate spline transform into a grid transform.

To create an instance of class vtkTransformToGrid, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkTransformToGrid
\end{verbatim}
\subsection{Methods}

The class vtkTransformToGrid has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkTransformToGrid class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkTransformToGrid = obj.NewInstance ()|

\item  \verb|vtkTransformToGrid = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetInput (vtkAbstractTransform )| -  Set/Get the transform which will be converted into a grid.

\item  \verb|vtkAbstractTransform = obj.GetInput ()| -  Set/Get the transform which will be converted into a grid.

\item  \verb|obj.SetGridExtent (int , int , int , int , int , int )| -  Get/Set the extent of the grid.

\item  \verb|obj.SetGridExtent (int  a[6])| -  Get/Set the extent of the grid.

\item  \verb|int = obj. GetGridExtent ()| -  Get/Set the extent of the grid.

\item  \verb|obj.SetGridOrigin (double , double , double )| -  Get/Set the origin of the grid.

\item  \verb|obj.SetGridOrigin (double  a[3])| -  Get/Set the origin of the grid.

\item  \verb|double = obj. GetGridOrigin ()| -  Get/Set the origin of the grid.

\item  \verb|obj.SetGridSpacing (double , double , double )| -  Get/Set the spacing between samples in the grid.

\item  \verb|obj.SetGridSpacing (double  a[3])| -  Get/Set the spacing between samples in the grid.

\item  \verb|double = obj. GetGridSpacing ()| -  Get/Set the spacing between samples in the grid.

\item  \verb|obj.SetGridScalarType (int )| -  Get/Set the scalar type of the grid.  The default is
 double.

\item  \verb|int = obj.GetGridScalarType ()| -  Get/Set the scalar type of the grid.  The default is
 double.

\item  \verb|obj.SetGridScalarTypeToFloat ()| -  Get/Set the scalar type of the grid.  The default is
 double.

\item  \verb|obj.SetGridScalarTypeToShort ()| -  Get/Set the scalar type of the grid.  The default is
 double.

\item  \verb|obj.SetGridScalarTypeToUnsignedShort ()| -  Get/Set the scalar type of the grid.  The default is
 double.

\item  \verb|obj.SetGridScalarTypeToUnsignedChar ()| -  Get/Set the scalar type of the grid.  The default is
 double.

\item  \verb|obj.SetGridScalarTypeToChar ()| -  Get/Set the scalar type of the grid.  The default is
 double.

\item  \verb|double = obj.GetDisplacementScale ()| -  Get the scale and shift to convert integer grid elements into
 real values:  dx = scale*di + shift.  If the grid is of double type,
 then scale = 1 and shift = 0.

\item  \verb|double = obj.GetDisplacementShift ()| -  Get the scale and shift to convert integer grid elements into
 real values:  dx = scale*di + shift.  If the grid is of double type,
 then scale = 1 and shift = 0.

\item  \verb|vtkImageData = obj.GetOutput ()| -  Get the output data object for a port on this algorithm.

\end{itemize}
