\section{vtkX3DExporter}

\subsection{Usage}

 vtkX3DExporter is a render window exporter which writes out the renderered
 scene into an X3D file. X3D is an XML-based format for representation 
 3D scenes (similar to VRML). Check out http://www.web3d.org/x3d/ for more
 details.
 .SECTION Thanks
 X3DExporter is contributed by Christophe Mouton at EDF.

To create an instance of class vtkX3DExporter, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkX3DExporter
\end{verbatim}
\subsection{Methods}

The class vtkX3DExporter has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkX3DExporter class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkX3DExporter = obj.NewInstance ()|

\item  \verb|vtkX3DExporter = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetFileName (string )| -  Set/Get the output file name.

\item  \verb|string = obj.GetFileName ()| -  Set/Get the output file name.

\item  \verb|obj.SetSpeed (double )| -  Specify the Speed of navigation. Default is 4.

\item  \verb|double = obj.GetSpeed ()| -  Specify the Speed of navigation. Default is 4.

\item  \verb|obj.SetBinary (int )| -  Turn on binary mode

\item  \verb|int = obj.GetBinaryMinValue ()| -  Turn on binary mode

\item  \verb|int = obj.GetBinaryMaxValue ()| -  Turn on binary mode

\item  \verb|obj.BinaryOn ()| -  Turn on binary mode

\item  \verb|obj.BinaryOff ()| -  Turn on binary mode

\item  \verb|int = obj.GetBinary ()| -  Turn on binary mode

\item  \verb|obj.SetFastest (int )| -  In binary mode use fastest instead of best compression

\item  \verb|int = obj.GetFastestMinValue ()| -  In binary mode use fastest instead of best compression

\item  \verb|int = obj.GetFastestMaxValue ()| -  In binary mode use fastest instead of best compression

\item  \verb|obj.FastestOn ()| -  In binary mode use fastest instead of best compression

\item  \verb|obj.FastestOff ()| -  In binary mode use fastest instead of best compression

\item  \verb|int = obj.GetFastest ()| -  In binary mode use fastest instead of best compression

\end{itemize}
