\section{vtkExodusModel}

\subsection{Usage}


   A vtkUnstructuredGrid output by vtkExodusReader or vtkPExodusReader
   is missing a great deal of initialization and static model data 
   that is in an Exodus II file.  (Global variables, properties,
   node sets, side sets, and so on.)  This data can be stored in a 
   vtkModelMetadata object, which can be initialized using
   this vtkExodusModel class.

   This class can be initialized with a file handle for an open Exodus 
   file, and the vtkUnstructuredGrid derived from that file.  The methods 
   used would be SetGlobalInformation, SetLocalInformation, 
   AddUGridElementVariable and AddUGridNodeVariable.  The vtkExodusReader
   does this.

   It can also be initialized (using UnpackExodusModel) from a 
   vtkUnstructuredGrid that has had metadata packed into it's field 
   arrays with PackExodusModel.   The vtkExodusIIWriter does this.

   If you plan to write out the Exodus file (with vtkExodusIIWriter), 
   you should direct the Exodus reader to create a vtkExodusModel object.
   This will be used by the Exodus writer to create a correct Exodus II 
   file on output.  In addition, the vtkDistributedDataFilter is 
   cognizant of the ExodusModel object and will unpack, extract, merge, 
   and pack these objects associated with the grids it is partitioning.

 .SECTION See also
   vtkExodusReader  vtkPExodusReader vtkExodusIIWriter vtkModelMetadata
   vtkDistributedDataFilter

To create an instance of class vtkExodusModel, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkExodusModel
\end{verbatim}
\subsection{Methods}

The class vtkExodusModel has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkExodusModel class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkExodusModel = obj.NewInstance ()|

\item  \verb|vtkExodusModel = obj.SafeDownCast (vtkObject o)|

\item  \verb|int = obj.SetGlobalInformation (int fid, int compute\_word\_size)|

\item  \verb|int = obj.AddUGridElementVariable (string ugridVarName, string origName, int numComponents)|

\item  \verb|int = obj.RemoveUGridElementVariable (string ugridVarName)|

\item  \verb|int = obj.AddUGridNodeVariable (string ugridVarName, string origName, int numComponents)|

\item  \verb|int = obj.RemoveUGridNodeVariable (string ugridVarName)|

\item  \verb|int = obj.SetLocalInformation (vtkUnstructuredGrid ugrid, int fid, int timeStep, int newGeometry, int compute\_word\_size)|

\item  \verb|vtkModelMetadata = obj.GetModelMetadata ()|

\item  \verb|obj.SetModelMetadata (vtkModelMetadata emData)|

\item  \verb|int = obj.UnpackExodusModel (vtkUnstructuredGrid grid, int deleteIt)|

\item  \verb|int = obj.MergeExodusModel (vtkExodusModel em)|

\item  \verb|vtkExodusModel = obj.ExtractExodusModel (vtkIdTypeArray globalCellIdList, vtkUnstructuredGrid grid)|

\item  \verb|obj.PackExodusModel (vtkUnstructuredGrid grid)|

\item  \verb|obj.Reset ()|

\end{itemize}
