\section{vtkAnnotatedCubeActor}

\subsection{Usage}

 vtkAnnotatedCubeActor is a hybrid 3D actor used to represent an anatomical
 orientation marker in a scene.  The class consists of a 3D unit cube centered
 on the origin with each face labelled in correspondance to a particular
 coordinate direction.  For example, with Cartesian directions, the user
 defined text labels could be: +X, -X, +Y, -Y, +Z, -Z, while for anatomical
 directions: A, P, L, R, S, I.  Text is automatically centered on each cube
 face and is not restriceted to single characters. In addition to or in
 replace of a solid text label representation, the outline edges of the labels
 can be displayed.  The individual properties of the cube, face labels
 and text outlines can be manipulated as can their visibility.

To create an instance of class vtkAnnotatedCubeActor, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkAnnotatedCubeActor
\end{verbatim}
\subsection{Methods}

The class vtkAnnotatedCubeActor has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkAnnotatedCubeActor class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkAnnotatedCubeActor = obj.NewInstance ()|

\item  \verb|vtkAnnotatedCubeActor = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.GetActors (vtkPropCollection )| -  For some exporters and other other operations we must be
 able to collect all the actors or volumes. These methods
 are used in that process.

\item  \verb|int = obj.RenderOpaqueGeometry (vtkViewport viewport)| -  Support the standard render methods.

\item  \verb|int = obj.RenderTranslucentPolygonalGeometry (vtkViewport viewport)| -  Support the standard render methods.

\item  \verb|int = obj.HasTranslucentPolygonalGeometry ()| -  Does this prop have some translucent polygonal geometry?

\item  \verb|obj.ShallowCopy (vtkProp prop)| -  Shallow copy of an axes actor. Overloads the virtual vtkProp method.

\item  \verb|obj.ReleaseGraphicsResources (vtkWindow )| -  Release any graphics resources that are being consumed by this actor.
 The parameter window could be used to determine which graphic
 resources to release.

\item  \verb|obj.GetBounds (double bounds[6])| -  Get the bounds for this Actor as (Xmin,Xmax,Ymin,Ymax,Zmin,Zmax). (The
 method GetBounds(double bounds[6]) is available from the superclass.)

\item  \verb|double = obj.GetBounds ()| -  Get the bounds for this Actor as (Xmin,Xmax,Ymin,Ymax,Zmin,Zmax). (The
 method GetBounds(double bounds[6]) is available from the superclass.)

\item  \verb|long = obj.GetMTime ()| -  Get the actors mtime plus consider its properties and texture if set.

\item  \verb|obj.SetFaceTextScale (double )| -  Set/Get the scale factor for the face text

\item  \verb|double = obj.GetFaceTextScale ()| -  Set/Get the scale factor for the face text

\item  \verb|vtkProperty = obj.GetXPlusFaceProperty ()| -  Get the individual face text properties.

\item  \verb|vtkProperty = obj.GetXMinusFaceProperty ()| -  Get the individual face text properties.

\item  \verb|vtkProperty = obj.GetYPlusFaceProperty ()| -  Get the individual face text properties.

\item  \verb|vtkProperty = obj.GetYMinusFaceProperty ()| -  Get the individual face text properties.

\item  \verb|vtkProperty = obj.GetZPlusFaceProperty ()| -  Get the individual face text properties.

\item  \verb|vtkProperty = obj.GetZMinusFaceProperty ()| -  Get the individual face text properties.

\item  \verb|vtkProperty = obj.GetCubeProperty ()| -  Get the cube properties.

\item  \verb|vtkProperty = obj.GetTextEdgesProperty ()| -  Get the text edges properties.

\item  \verb|obj.SetXPlusFaceText (string )| -  Set/get the face text.

\item  \verb|string = obj.GetXPlusFaceText ()| -  Set/get the face text.

\item  \verb|obj.SetXMinusFaceText (string )| -  Set/get the face text.

\item  \verb|string = obj.GetXMinusFaceText ()| -  Set/get the face text.

\item  \verb|obj.SetYPlusFaceText (string )| -  Set/get the face text.

\item  \verb|string = obj.GetYPlusFaceText ()| -  Set/get the face text.

\item  \verb|obj.SetYMinusFaceText (string )| -  Set/get the face text.

\item  \verb|string = obj.GetYMinusFaceText ()| -  Set/get the face text.

\item  \verb|obj.SetZPlusFaceText (string )| -  Set/get the face text.

\item  \verb|string = obj.GetZPlusFaceText ()| -  Set/get the face text.

\item  \verb|obj.SetZMinusFaceText (string )| -  Set/get the face text.

\item  \verb|string = obj.GetZMinusFaceText ()| -  Set/get the face text.

\item  \verb|obj.SetTextEdgesVisibility (int )| -  Enable/disable drawing the vector text edges.

\item  \verb|int = obj.GetTextEdgesVisibility ()| -  Enable/disable drawing the vector text edges.

\item  \verb|obj.SetCubeVisibility (int )| -  Enable/disable drawing the cube.

\item  \verb|int = obj.GetCubeVisibility ()| -  Enable/disable drawing the cube.

\item  \verb|obj.SetFaceTextVisibility (int )| -  Enable/disable drawing the vector text.

\item  \verb|int = obj.GetFaceTextVisibility ()| -  Enable/disable drawing the vector text.

\item  \verb|obj.SetXFaceTextRotation (double )| -  Augment individual face text orientations.

\item  \verb|double = obj.GetXFaceTextRotation ()| -  Augment individual face text orientations.

\item  \verb|obj.SetYFaceTextRotation (double )| -  Augment individual face text orientations.

\item  \verb|double = obj.GetYFaceTextRotation ()| -  Augment individual face text orientations.

\item  \verb|obj.SetZFaceTextRotation (double )| -  Augment individual face text orientations.

\item  \verb|double = obj.GetZFaceTextRotation ()| -  Augment individual face text orientations.

\item  \verb|vtkAssembly = obj.GetAssembly ()|

\end{itemize}
