\section{vtkXMLStructuredDataWriter}

\subsection{Usage}

 vtkXMLStructuredDataWriter provides VTK XML writing functionality that
 is common among all the structured data formats.

To create an instance of class vtkXMLStructuredDataWriter, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkXMLStructuredDataWriter
\end{verbatim}
\subsection{Methods}

The class vtkXMLStructuredDataWriter has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkXMLStructuredDataWriter class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkXMLStructuredDataWriter = obj.NewInstance ()|

\item  \verb|vtkXMLStructuredDataWriter = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetNumberOfPieces (int )| -  Get/Set the number of pieces used to stream the image through the
 pipeline while writing to the file.

\item  \verb|int = obj.GetNumberOfPieces ()| -  Get/Set the number of pieces used to stream the image through the
 pipeline while writing to the file.

\item  \verb|obj.SetWriteExtent (int , int , int , int , int , int )| -  Get/Set the extent of the input that should be treated as the
 WholeExtent in the output file.  The default is the WholeExtent
 of the input.

\item  \verb|obj.SetWriteExtent (int  a[6])| -  Get/Set the extent of the input that should be treated as the
 WholeExtent in the output file.  The default is the WholeExtent
 of the input.

\item  \verb|int = obj. GetWriteExtent ()| -  Get/Set the extent of the input that should be treated as the
 WholeExtent in the output file.  The default is the WholeExtent
 of the input.

\item  \verb|obj.SetExtentTranslator (vtkExtentTranslator )| -  Get/Set the extent translator used for streaming.

\item  \verb|vtkExtentTranslator = obj.GetExtentTranslator ()| -  Get/Set the extent translator used for streaming.

\end{itemize}
