\section{vtkXMLPDataWriter}

\subsection{Usage}

 vtkXMLPDataWriter is the superclass for all XML parallel data set
 writers.  It provides functionality needed for writing parallel
 formats, such as the selection of which writer writes the summary
 file and what range of pieces are assigned to each serial writer.

To create an instance of class vtkXMLPDataWriter, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkXMLPDataWriter
\end{verbatim}
\subsection{Methods}

The class vtkXMLPDataWriter has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkXMLPDataWriter class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkXMLPDataWriter = obj.NewInstance ()|

\item  \verb|vtkXMLPDataWriter = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetNumberOfPieces (int )| -  Get/Set the number of pieces that are being written in parallel.

\item  \verb|int = obj.GetNumberOfPieces ()| -  Get/Set the number of pieces that are being written in parallel.

\item  \verb|obj.SetStartPiece (int )| -  Get/Set the range of pieces assigned to this writer.

\item  \verb|int = obj.GetStartPiece ()| -  Get/Set the range of pieces assigned to this writer.

\item  \verb|obj.SetEndPiece (int )| -  Get/Set the range of pieces assigned to this writer.

\item  \verb|int = obj.GetEndPiece ()| -  Get/Set the range of pieces assigned to this writer.

\item  \verb|obj.SetGhostLevel (int )| -  Get/Set the ghost level used for this writer's piece.

\item  \verb|int = obj.GetGhostLevel ()| -  Get/Set the ghost level used for this writer's piece.

\item  \verb|obj.SetWriteSummaryFile (int flag)| -  Get/Set whether this instance of the writer should write the
 summary file that refers to all of the pieces' individual files.
 Default is yes only for piece 0 writer.

\item  \verb|int = obj.GetWriteSummaryFile ()| -  Get/Set whether this instance of the writer should write the
 summary file that refers to all of the pieces' individual files.
 Default is yes only for piece 0 writer.

\item  \verb|obj.WriteSummaryFileOn ()| -  Get/Set whether this instance of the writer should write the
 summary file that refers to all of the pieces' individual files.
 Default is yes only for piece 0 writer.

\item  \verb|obj.WriteSummaryFileOff ()| -  Get/Set whether this instance of the writer should write the
 summary file that refers to all of the pieces' individual files.
 Default is yes only for piece 0 writer.

\end{itemize}
