\section{vtkImageCast}

\subsection{Usage}

 vtkImageCast filter casts the input type to match the output type in
 the image processing pipeline.  The filter does nothing if the input
 already has the correct type.  To specify the ''CastTo'' type,
 use ''SetOutputScalarType'' method.

To create an instance of class vtkImageCast, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkImageCast
\end{verbatim}
\subsection{Methods}

The class vtkImageCast has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkImageCast class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkImageCast = obj.NewInstance ()|

\item  \verb|vtkImageCast = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetOutputScalarType (int )| -  Set the desired output scalar type to cast to.

\item  \verb|int = obj.GetOutputScalarType ()| -  Set the desired output scalar type to cast to.

\item  \verb|obj.SetOutputScalarTypeToFloat ()| -  Set the desired output scalar type to cast to.

\item  \verb|obj.SetOutputScalarTypeToDouble ()| -  Set the desired output scalar type to cast to.

\item  \verb|obj.SetOutputScalarTypeToInt ()| -  Set the desired output scalar type to cast to.

\item  \verb|obj.SetOutputScalarTypeToUnsignedInt ()| -  Set the desired output scalar type to cast to.

\item  \verb|obj.SetOutputScalarTypeToLong ()| -  Set the desired output scalar type to cast to.

\item  \verb|obj.SetOutputScalarTypeToUnsignedLong ()| -  Set the desired output scalar type to cast to.

\item  \verb|obj.SetOutputScalarTypeToShort ()| -  Set the desired output scalar type to cast to.

\item  \verb|obj.SetOutputScalarTypeToUnsignedShort ()| -  Set the desired output scalar type to cast to.

\item  \verb|obj.SetOutputScalarTypeToUnsignedChar ()| -  Set the desired output scalar type to cast to.

\item  \verb|obj.SetOutputScalarTypeToChar ()| -  Set the desired output scalar type to cast to.

\item  \verb|obj.SetClampOverflow (int )| -  When the ClampOverflow flag is on, the data is thresholded so that
 the output value does not exceed the max or min of the data type.
 By default ClampOverflow is off.

\item  \verb|int = obj.GetClampOverflow ()| -  When the ClampOverflow flag is on, the data is thresholded so that
 the output value does not exceed the max or min of the data type.
 By default ClampOverflow is off.

\item  \verb|obj.ClampOverflowOn ()| -  When the ClampOverflow flag is on, the data is thresholded so that
 the output value does not exceed the max or min of the data type.
 By default ClampOverflow is off.

\item  \verb|obj.ClampOverflowOff ()| -  When the ClampOverflow flag is on, the data is thresholded so that
 the output value does not exceed the max or min of the data type.
 By default ClampOverflow is off.

\end{itemize}
