\section{vtkMedicalImageReader2}

\subsection{Usage}

 vtkMedicalImageReader2 is a parent class for medical image readers.
 It provides a place to store patient information that may be stored
 in the image header.

To create an instance of class vtkMedicalImageReader2, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkMedicalImageReader2
\end{verbatim}
\subsection{Methods}

The class vtkMedicalImageReader2 has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkMedicalImageReader2 class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkMedicalImageReader2 = obj.NewInstance ()|

\item  \verb|vtkMedicalImageReader2 = obj.SafeDownCast (vtkObject o)|

\item  \verb|vtkMedicalImageProperties = obj.GetMedicalImageProperties ()| -  Get the medical image properties object

\item  \verb|obj.SetPatientName (string )| -  For backward compatibility, propagate calls to the MedicalImageProperties
 object.

\item  \verb|string = obj.GetPatientName ()| -  For backward compatibility, propagate calls to the MedicalImageProperties
 object.

\item  \verb|obj.SetPatientID (string )| -  For backward compatibility, propagate calls to the MedicalImageProperties
 object.

\item  \verb|string = obj.GetPatientID ()| -  For backward compatibility, propagate calls to the MedicalImageProperties
 object.

\item  \verb|obj.SetDate (string )| -  For backward compatibility, propagate calls to the MedicalImageProperties
 object.

\item  \verb|string = obj.GetDate ()| -  For backward compatibility, propagate calls to the MedicalImageProperties
 object.

\item  \verb|obj.SetSeries (string )| -  For backward compatibility, propagate calls to the MedicalImageProperties
 object.

\item  \verb|string = obj.GetSeries ()| -  For backward compatibility, propagate calls to the MedicalImageProperties
 object.

\item  \verb|obj.SetStudy (string )| -  For backward compatibility, propagate calls to the MedicalImageProperties
 object.

\item  \verb|string = obj.GetStudy ()| -  For backward compatibility, propagate calls to the MedicalImageProperties
 object.

\item  \verb|obj.SetImageNumber (string )| -  For backward compatibility, propagate calls to the MedicalImageProperties
 object.

\item  \verb|string = obj.GetImageNumber ()| -  For backward compatibility, propagate calls to the MedicalImageProperties
 object.

\item  \verb|obj.SetModality (string )| -  For backward compatibility, propagate calls to the MedicalImageProperties
 object.

\item  \verb|string = obj.GetModality ()| -  For backward compatibility, propagate calls to the MedicalImageProperties
 object.

\end{itemize}
