\section{vtkImageStencil}

\subsection{Usage}

 vtkImageStencil will combine two images together using a stencil.
 The stencil should be provided in the form of a vtkImageStencilData,

To create an instance of class vtkImageStencil, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkImageStencil
\end{verbatim}
\subsection{Methods}

The class vtkImageStencil has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkImageStencil class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkImageStencil = obj.NewInstance ()|

\item  \verb|vtkImageStencil = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetStencil (vtkImageStencilData stencil)| -  Specify the stencil to use.  The stencil can be created
 from a vtkImplicitFunction or a vtkPolyData.

\item  \verb|vtkImageStencilData = obj.GetStencil ()| -  Specify the stencil to use.  The stencil can be created
 from a vtkImplicitFunction or a vtkPolyData.

\item  \verb|obj.SetReverseStencil (int )| -  Reverse the stencil.

\item  \verb|obj.ReverseStencilOn ()| -  Reverse the stencil.

\item  \verb|obj.ReverseStencilOff ()| -  Reverse the stencil.

\item  \verb|int = obj.GetReverseStencil ()| -  Reverse the stencil.

\item  \verb|obj.SetBackgroundInput (vtkImageData input)| -  NOTE: Not yet implemented, use SetBackgroundValue instead.
 Set the second input.  This image will be used for the 'outside' of the
 stencil.  If not set, the output voxels will be filled with
 BackgroundValue instead.

\item  \verb|vtkImageData = obj.GetBackgroundInput ()| -  NOTE: Not yet implemented, use SetBackgroundValue instead.
 Set the second input.  This image will be used for the 'outside' of the
 stencil.  If not set, the output voxels will be filled with
 BackgroundValue instead.

\item  \verb|obj.SetBackgroundValue (double val)| -  Set the default output value to use when the second input is not set.

\item  \verb|double = obj.GetBackgroundValue ()| -  Set the default output value to use when the second input is not set.

\item  \verb|obj.SetBackgroundColor (double , double , double , double )| -  Set the default color to use when the second input is not set.
 This is like SetBackgroundValue, but for multi-component images.

\item  \verb|obj.SetBackgroundColor (double  a[4])| -  Set the default color to use when the second input is not set.
 This is like SetBackgroundValue, but for multi-component images.

\item  \verb|double = obj. GetBackgroundColor ()| -  Set the default color to use when the second input is not set.
 This is like SetBackgroundValue, but for multi-component images.

\end{itemize}
