\section{vtkImageMapToWindowLevelColors}

\subsection{Usage}

 The vtkImageMapToWindowLevelColors filter will take an input image of any
 valid scalar type, and map the first component of the image through a
 lookup table.  This resulting color will be modulated with value obtained
 by a window / level operation. The result is an image of type 
 VTK\_UNSIGNED\_CHAR. If the lookup table is not set, or is set to NULL, then 
 the input data will be passed through if it is already of type 
 UNSIGNED\_CHAR.


To create an instance of class vtkImageMapToWindowLevelColors, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkImageMapToWindowLevelColors
\end{verbatim}
\subsection{Methods}

The class vtkImageMapToWindowLevelColors has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkImageMapToWindowLevelColors class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkImageMapToWindowLevelColors = obj.NewInstance ()|

\item  \verb|vtkImageMapToWindowLevelColors = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetWindow (double )| -  Set / Get the Window to use -> modulation will be performed on the 
 color based on (S - (L - W/2))/W where S is the scalar value, L is
 the level and W is the window.

\item  \verb|double = obj.GetWindow ()| -  Set / Get the Window to use -> modulation will be performed on the 
 color based on (S - (L - W/2))/W where S is the scalar value, L is
 the level and W is the window.

\item  \verb|obj.SetLevel (double )| -  Set / Get the Level to use -> modulation will be performed on the 
 color based on (S - (L - W/2))/W where S is the scalar value, L is
 the level and W is the window.

\item  \verb|double = obj.GetLevel ()| -  Set / Get the Level to use -> modulation will be performed on the 
 color based on (S - (L - W/2))/W where S is the scalar value, L is
 the level and W is the window.

\end{itemize}
