\section{vtkSQLiteDatabase}

\subsection{Usage}


 SQLite (http://www.sqlite.org) is a public-domain SQL database
 written in C++.  It's small, fast, and can be easily embedded
 inside other applications.  Its databases are stored in files.

 This class provides a VTK interface to SQLite.  You do not need to
 download any external libraries: we include a copy of SQLite 3.3.16
 in VTK/Utilities/vtksqlite.  

 If you want to open a database that stays in memory and never gets
 written to disk, pass in the URL 'sqlite://:memory:'; otherwise,
 specifiy the file path by passing the URL 'sqlite://<file\_path>'.

 .SECTION Thanks
 Thanks to Andrew Wilson and Philippe Pebay from Sandia National 
 Laboratories for implementing this class.


To create an instance of class vtkSQLiteDatabase, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkSQLiteDatabase
\end{verbatim}
\subsection{Methods}

The class vtkSQLiteDatabase has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkSQLiteDatabase class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkSQLiteDatabase = obj.NewInstance ()|

\item  \verb|vtkSQLiteDatabase = obj.SafeDownCast (vtkObject o)|

\item  \verb|bool = obj.Open (string password)| -  Open a new connection to the database.  You need to set the
 filename before calling this function.  Returns true if the
 database was opened successfully; false otherwise.
 - USE\_EXISTING (default) - Fail if the file does not exist.
 - USE\_EXISTING\_OR\_CREATE - Create a new file if necessary.
 - CREATE\_OR\_CLEAR - Create new or clear existing file.
 - CREATE - Create new, fail if file exists.

\item  \verb|bool = obj.Open (string password, int mode)| -  Open a new connection to the database.  You need to set the
 filename before calling this function.  Returns true if the
 database was opened successfully; false otherwise.
 - USE\_EXISTING (default) - Fail if the file does not exist.
 - USE\_EXISTING\_OR\_CREATE - Create a new file if necessary.
 - CREATE\_OR\_CLEAR - Create new or clear existing file.
 - CREATE - Create new, fail if file exists.

\item  \verb|obj.Close ()| -  Close the connection to the database.

\item  \verb|bool = obj.IsOpen ()| -  Return whether the database has an open connection

\item  \verb|vtkSQLQuery = obj.GetQueryInstance ()| -  Return an empty query on this database.

\item  \verb|vtkStringArray = obj.GetTables ()| -  Get the list of tables from the database

\item  \verb|vtkStringArray = obj.GetRecord (string table)| -  Get the list of fields for a particular table

\item  \verb|bool = obj.IsSupported (int feature)| -  Return whether a feature is supported by the database.

\item  \verb|bool = obj.HasError ()| -  Did the last operation generate an error

\item  \verb|string = obj.GetLastErrorText ()| -  Get the last error text from the database

\item  \verb|string = obj.GetDatabaseType ()| -  String representing database type (e.g. ''sqlite'').

\item  \verb|string = obj.GetDatabaseFileName ()| -  String representing the database filename.

\item  \verb|obj.SetDatabaseFileName (string )| -  String representing the database filename.

\item  \verb|vtkStdString = obj.GetURL ()| -  Get the URL of the database.

\item  \verb|vtkStdString = obj.GetColumnSpecification (vtkSQLDatabaseSchema schema, int tblHandle, int colHandle)| -  Return the SQL string with the syntax to create a column inside a
 ''CREATE TABLE'' SQL statement.
 NB: this method implements the SQLite-specific syntax:
 <column name> <column type> <column attributes>

\end{itemize}
