\section{vtkTIFFWriter}

\subsection{Usage}

 vtkTIFFWriter writes image data as a TIFF data file. Data can be written
 uncompressed or compressed. Several forms of compression are supported
 including packed bits, JPEG, deflation, and LZW. (Note: LZW compression
 is currently under patent in the US and is disabled until the patent
 expires. However, the mechanism for supporting this compression is available
 for those with a valid license or to whom the patent does not apply.)

To create an instance of class vtkTIFFWriter, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkTIFFWriter
\end{verbatim}
\subsection{Methods}

The class vtkTIFFWriter has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkTIFFWriter class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkTIFFWriter = obj.NewInstance ()|

\item  \verb|vtkTIFFWriter = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetCompression (int )| -  Set compression type. Sinze LZW compression is patented outside US, the
 additional work steps have to be taken in order to use that compression.

\item  \verb|int = obj.GetCompressionMinValue ()| -  Set compression type. Sinze LZW compression is patented outside US, the
 additional work steps have to be taken in order to use that compression.

\item  \verb|int = obj.GetCompressionMaxValue ()| -  Set compression type. Sinze LZW compression is patented outside US, the
 additional work steps have to be taken in order to use that compression.

\item  \verb|int = obj.GetCompression ()| -  Set compression type. Sinze LZW compression is patented outside US, the
 additional work steps have to be taken in order to use that compression.

\item  \verb|obj.SetCompressionToNoCompression ()| -  Set compression type. Sinze LZW compression is patented outside US, the
 additional work steps have to be taken in order to use that compression.

\item  \verb|obj.SetCompressionToPackBits ()| -  Set compression type. Sinze LZW compression is patented outside US, the
 additional work steps have to be taken in order to use that compression.

\item  \verb|obj.SetCompressionToJPEG ()| -  Set compression type. Sinze LZW compression is patented outside US, the
 additional work steps have to be taken in order to use that compression.

\item  \verb|obj.SetCompressionToDeflate ()| -  Set compression type. Sinze LZW compression is patented outside US, the
 additional work steps have to be taken in order to use that compression.

\item  \verb|obj.SetCompressionToLZW ()|

\end{itemize}
