\section{vtkImageIslandRemoval2D}

\subsection{Usage}

 vtkImageIslandRemoval2D computes the area of separate islands in 
 a mask image.  It removes any island that has less than AreaThreshold
 pixels.  Output has the same ScalarType as input.  It generates
 the whole 2D output image for any output request.

To create an instance of class vtkImageIslandRemoval2D, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkImageIslandRemoval2D
\end{verbatim}
\subsection{Methods}

The class vtkImageIslandRemoval2D has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkImageIslandRemoval2D class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()| -  Constructor: Sets default filter to be identity.

\item  \verb|int = obj.IsA (string name)| -  Constructor: Sets default filter to be identity.

\item  \verb|vtkImageIslandRemoval2D = obj.NewInstance ()| -  Constructor: Sets default filter to be identity.

\item  \verb|vtkImageIslandRemoval2D = obj.SafeDownCast (vtkObject o)| -  Constructor: Sets default filter to be identity.

\item  \verb|obj.SetAreaThreshold (int )| -  Set/Get the cutoff area for removal

\item  \verb|int = obj.GetAreaThreshold ()| -  Set/Get the cutoff area for removal

\item  \verb|obj.SetSquareNeighborhood (int )| -  Set/Get whether to use 4 or 8 neighbors

\item  \verb|int = obj.GetSquareNeighborhood ()| -  Set/Get whether to use 4 or 8 neighbors

\item  \verb|obj.SquareNeighborhoodOn ()| -  Set/Get whether to use 4 or 8 neighbors

\item  \verb|obj.SquareNeighborhoodOff ()| -  Set/Get whether to use 4 or 8 neighbors

\item  \verb|obj.SetIslandValue (double )| -  Set/Get the value to remove.

\item  \verb|double = obj.GetIslandValue ()| -  Set/Get the value to remove.

\item  \verb|obj.SetReplaceValue (double )| -  Set/Get the value to put in the place of removed pixels.

\item  \verb|double = obj.GetReplaceValue ()| -  Set/Get the value to put in the place of removed pixels.

\end{itemize}
