\section{vtkImageSeedConnectivity}

\subsection{Usage}

 vtkImageSeedConnectivity marks pixels connected to user supplied seeds.
 The input must be unsigned char, and the output is also unsigned char.  If
 a seed supplied by the user does not have pixel value ''InputTrueValue'',
 then the image is scanned +x, +y, +z until a pixel is encountered with
 value ''InputTrueValue''.  This new pixel is used as the seed .  Any pixel
 with out value ''InputTrueValue'' is consider off.  The output pixels values
 are 0 for any off pixel in input, ''OutputTrueValue'' for any pixels
 connected to seeds, and ''OutputUnconnectedValue'' for any on pixels not
 connected to seeds.  The same seeds are used for all images in the image
 set.

To create an instance of class vtkImageSeedConnectivity, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkImageSeedConnectivity
\end{verbatim}
\subsection{Methods}

The class vtkImageSeedConnectivity has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkImageSeedConnectivity class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkImageSeedConnectivity = obj.NewInstance ()|

\item  \verb|vtkImageSeedConnectivity = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.RemoveAllSeeds ()| -  Methods for manipulating the seed pixels.

\item  \verb|obj.AddSeed (int num, int index)| -  Methods for manipulating the seed pixels.

\item  \verb|obj.AddSeed (int i0, int i1, int i2)| -  Methods for manipulating the seed pixels.

\item  \verb|obj.AddSeed (int i0, int i1)| -  Methods for manipulating the seed pixels.

\item  \verb|obj.SetInputConnectValue (int )| -  Set/Get what value is considered as connecting pixels.

\item  \verb|int = obj.GetInputConnectValue ()| -  Set/Get what value is considered as connecting pixels.

\item  \verb|obj.SetOutputConnectedValue (int )| -  Set/Get the value to set connected pixels to.

\item  \verb|int = obj.GetOutputConnectedValue ()| -  Set/Get the value to set connected pixels to.

\item  \verb|obj.SetOutputUnconnectedValue (int )| -  Set/Get the value to set unconnected pixels to.

\item  \verb|int = obj.GetOutputUnconnectedValue ()| -  Set/Get the value to set unconnected pixels to.

\item  \verb|vtkImageConnector = obj.GetConnector ()| -  Get the vtkImageCOnnector used by this filter.

\item  \verb|obj.SetDimensionality (int )| -  Set the number of axes to use in connectivity.

\item  \verb|int = obj.GetDimensionality ()| -  Set the number of axes to use in connectivity.

\end{itemize}
