\section{vtkGraphLayoutStrategy}

\subsection{Usage}

 All graph layouts should subclass from this class.  vtkGraphLayoutStrategy
 works as a plug-in to the vtkGraphLayout algorithm.  The Layout()
 function should perform some reasonable ''chunk'' of the layout.
 This allows the user to be able to see the progress of the layout.
 Use IsLayoutComplete() to tell the user when there is no more layout
 to perform.

 .SECTION Thanks
 Thanks to Brian Wylie from Sandia National Laboratories for adding incremental
 layout capabilities.

To create an instance of class vtkGraphLayoutStrategy, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkGraphLayoutStrategy
\end{verbatim}
\subsection{Methods}

The class vtkGraphLayoutStrategy has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkGraphLayoutStrategy class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkGraphLayoutStrategy = obj.NewInstance ()|

\item  \verb|vtkGraphLayoutStrategy = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetGraph (vtkGraph graph)| -  Setting the graph for the layout strategy

\item  \verb|obj.Initialize ()| -  This method allows the layout strategy to
 do initialization of data structures
 or whatever else it might want to do. 

\item  \verb|obj.Layout ()| -  This is the layout method where the graph that was
 set in SetGraph() is laid out. The method can either
 entirely layout the graph or iteratively lay out the
 graph. If you have an iterative layout please implement
 the IsLayoutComplete() method.

\item  \verb|int = obj.IsLayoutComplete ()| -  Whether to use edge weights in the layout or not.

\item  \verb|obj.SetWeightEdges (bool state)| -  Whether to use edge weights in the layout or not.

\item  \verb|bool = obj.GetWeightEdges ()| -  Whether to use edge weights in the layout or not.

\item  \verb|obj.SetEdgeWeightField (string field)| -  Set/Get the field to use for the edge weights.

\item  \verb|string = obj.GetEdgeWeightField ()| -  Set/Get the field to use for the edge weights.

\end{itemize}
