\section{vtkStringToNumeric}

\subsection{Usage}

 vtkStringToNumeric is a filter for converting a string array
 into a numeric arrays.

To create an instance of class vtkStringToNumeric, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkStringToNumeric
\end{verbatim}
\subsection{Methods}

The class vtkStringToNumeric has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkStringToNumeric class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkStringToNumeric = obj.NewInstance ()|

\item  \verb|vtkStringToNumeric = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetConvertFieldData (bool )| -  Whether to detect and convert field data arrays.  Default is on.

\item  \verb|bool = obj.GetConvertFieldData ()| -  Whether to detect and convert field data arrays.  Default is on.

\item  \verb|obj.ConvertFieldDataOn ()| -  Whether to detect and convert field data arrays.  Default is on.

\item  \verb|obj.ConvertFieldDataOff ()| -  Whether to detect and convert field data arrays.  Default is on.

\item  \verb|obj.SetConvertPointData (bool )| -  Whether to detect and convert cell data arrays.  Default is on.

\item  \verb|bool = obj.GetConvertPointData ()| -  Whether to detect and convert cell data arrays.  Default is on.

\item  \verb|obj.ConvertPointDataOn ()| -  Whether to detect and convert cell data arrays.  Default is on.

\item  \verb|obj.ConvertPointDataOff ()| -  Whether to detect and convert cell data arrays.  Default is on.

\item  \verb|obj.SetConvertCellData (bool )| -  Whether to detect and convert point data arrays.  Default is on.

\item  \verb|bool = obj.GetConvertCellData ()| -  Whether to detect and convert point data arrays.  Default is on.

\item  \verb|obj.ConvertCellDataOn ()| -  Whether to detect and convert point data arrays.  Default is on.

\item  \verb|obj.ConvertCellDataOff ()| -  Whether to detect and convert point data arrays.  Default is on.

\item  \verb|obj.SetConvertVertexData (bool b)| -  Whether to detect and convert vertex data arrays.  Default is on.

\item  \verb|bool = obj.GetConvertVertexData ()| -  Whether to detect and convert vertex data arrays.  Default is on.

\item  \verb|obj.ConvertVertexDataOn ()| -  Whether to detect and convert vertex data arrays.  Default is on.

\item  \verb|obj.ConvertVertexDataOff ()| -  Whether to detect and convert vertex data arrays.  Default is on.

\item  \verb|obj.SetConvertEdgeData (bool b)| -  Whether to detect and convert edge data arrays.  Default is on.

\item  \verb|bool = obj.GetConvertEdgeData ()| -  Whether to detect and convert edge data arrays.  Default is on.

\item  \verb|obj.ConvertEdgeDataOn ()| -  Whether to detect and convert edge data arrays.  Default is on.

\item  \verb|obj.ConvertEdgeDataOff ()| -  Whether to detect and convert edge data arrays.  Default is on.

\item  \verb|obj.SetConvertRowData (bool b)| -  Whether to detect and convert row data arrays.  Default is on.

\item  \verb|bool = obj.GetConvertRowData ()| -  Whether to detect and convert row data arrays.  Default is on.

\item  \verb|obj.ConvertRowDataOn ()| -  Whether to detect and convert row data arrays.  Default is on.

\item  \verb|obj.ConvertRowDataOff ()| -  Whether to detect and convert row data arrays.  Default is on.

\end{itemize}
