\section{vtkStrahlerMetric}

\subsection{Usage}

 The Strahler metric is a value assigned to each vertex of a 
 tree that characterizes the structural complexity of the 
 sub-tree rooted at that node.  The metric originated in the
 study of river systems, but has been applied to other tree-
 structured systes,  Details of the metric and the rationale 
 for using it in infovis can be found in:
 
 Tree Visualization and Navigation Clues for Information
 Visualization, I. Herman, M. Delest, and G. Melancon,
 Computer Graphics Forum, Vol 17(2), Blackwell, 1998.

 The input tree is copied to the output, but with a new array
 added to the output vertex data.

 .SECTION Thanks
 Thanks to David Duke from the University of Leeds for providing this 
 implementation.

To create an instance of class vtkStrahlerMetric, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkStrahlerMetric
\end{verbatim}
\subsection{Methods}

The class vtkStrahlerMetric has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkStrahlerMetric class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkStrahlerMetric = obj.NewInstance ()|

\item  \verb|vtkStrahlerMetric = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetMetricArrayName (string )| -  Set the name of the array in which the Strahler values will
 be stored within the output vertex data.
 Default is ''Strahler''

\item  \verb|obj.SetNormalize (int )| -  Set/get setting of normalize flag.  If this is set, the
 Strahler values are scaled into the range [0..1].
 Default is for normalization to be OFF.

\item  \verb|int = obj.GetNormalize ()| -  Set/get setting of normalize flag.  If this is set, the
 Strahler values are scaled into the range [0..1].
 Default is for normalization to be OFF.

\item  \verb|obj.NormalizeOn ()| -  Set/get setting of normalize flag.  If this is set, the
 Strahler values are scaled into the range [0..1].
 Default is for normalization to be OFF.

\item  \verb|obj.NormalizeOff ()| -  Set/get setting of normalize flag.  If this is set, the
 Strahler values are scaled into the range [0..1].
 Default is for normalization to be OFF.

\item  \verb|float = obj.GetMaxStrahler ()| -  Get the maximum strahler value for the tree.

\end{itemize}
