\section{vtkBooleanTexture}

\subsection{Usage}

 vtkBooleanTexture is a filter to generate a 2D texture map based on 
 combinations of inside, outside, and on region boundary. The ''region'' is
 implicitly represented via 2D texture coordinates. These texture 
 coordinates are normally generated using a filter like 
 vtkImplicitTextureCoords, which generates the texture coordinates for 
 any implicit function.

 vtkBooleanTexture generates the map according to the s-t texture
 coordinates plus the notion of being in, on, or outside of a
 region. An in region is when the texture coordinate is between
 (0,0.5-thickness/2).  An out region is where the texture coordinate
 is (0.5+thickness/2). An on region is between
 (0.5-thickness/2,0.5+thickness/2). The combination in, on, and out
 for each of the s-t texture coordinates results in 16 possible
 combinations (see text). For each combination, a different value of 
 intensity and transparency can be assigned. To assign maximum intensity
 and/or opacity use the value 255. A minimum value of 0 results in
 a black region (for intensity) and a fully transparent region (for
 transparency).

To create an instance of class vtkBooleanTexture, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkBooleanTexture
\end{verbatim}
\subsection{Methods}

The class vtkBooleanTexture has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkBooleanTexture class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkBooleanTexture = obj.NewInstance ()|

\item  \verb|vtkBooleanTexture = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetXSize (int )| -  Set the X texture map dimension.

\item  \verb|int = obj.GetXSize ()| -  Set the X texture map dimension.

\item  \verb|obj.SetYSize (int )| -  Set the Y texture map dimension.

\item  \verb|int = obj.GetYSize ()| -  Set the Y texture map dimension.

\item  \verb|obj.SetThickness (int )| -  Set the thickness of the ''on'' region.

\item  \verb|int = obj.GetThickness ()| -  Set the thickness of the ''on'' region.

\item  \verb|obj.SetInIn (char , char )| -  Specify intensity/transparency for ''in/in'' region.

\item  \verb|obj.SetInIn (char  a[2])| -  Specify intensity/transparency for ''in/in'' region.

\item  \verb|char = obj. GetInIn ()| -  Specify intensity/transparency for ''in/in'' region.

\item  \verb|obj.SetInOut (char , char )| -  Specify intensity/transparency for ''in/out'' region.

\item  \verb|obj.SetInOut (char  a[2])| -  Specify intensity/transparency for ''in/out'' region.

\item  \verb|char = obj. GetInOut ()| -  Specify intensity/transparency for ''in/out'' region.

\item  \verb|obj.SetOutIn (char , char )| -  Specify intensity/transparency for ''out/in'' region.

\item  \verb|obj.SetOutIn (char  a[2])| -  Specify intensity/transparency for ''out/in'' region.

\item  \verb|char = obj. GetOutIn ()| -  Specify intensity/transparency for ''out/in'' region.

\item  \verb|obj.SetOutOut (char , char )| -  Specify intensity/transparency for ''out/out'' region.

\item  \verb|obj.SetOutOut (char  a[2])| -  Specify intensity/transparency for ''out/out'' region.

\item  \verb|char = obj. GetOutOut ()| -  Specify intensity/transparency for ''out/out'' region.

\item  \verb|obj.SetOnOn (char , char )| -  Specify intensity/transparency for ''on/on'' region.

\item  \verb|obj.SetOnOn (char  a[2])| -  Specify intensity/transparency for ''on/on'' region.

\item  \verb|char = obj. GetOnOn ()| -  Specify intensity/transparency for ''on/on'' region.

\item  \verb|obj.SetOnIn (char , char )| -  Specify intensity/transparency for ''on/in'' region.

\item  \verb|obj.SetOnIn (char  a[2])| -  Specify intensity/transparency for ''on/in'' region.

\item  \verb|char = obj. GetOnIn ()| -  Specify intensity/transparency for ''on/in'' region.

\item  \verb|obj.SetOnOut (char , char )| -  Specify intensity/transparency for ''on/out'' region.

\item  \verb|obj.SetOnOut (char  a[2])| -  Specify intensity/transparency for ''on/out'' region.

\item  \verb|char = obj. GetOnOut ()| -  Specify intensity/transparency for ''on/out'' region.

\item  \verb|obj.SetInOn (char , char )| -  Specify intensity/transparency for ''in/on'' region.

\item  \verb|obj.SetInOn (char  a[2])| -  Specify intensity/transparency for ''in/on'' region.

\item  \verb|char = obj. GetInOn ()| -  Specify intensity/transparency for ''in/on'' region.

\item  \verb|obj.SetOutOn (char , char )| -  Specify intensity/transparency for ''out/on'' region.

\item  \verb|obj.SetOutOn (char  a[2])| -  Specify intensity/transparency for ''out/on'' region.

\item  \verb|char = obj. GetOutOn ()| -  Specify intensity/transparency for ''out/on'' region.

\end{itemize}
