\section{vtkChacoReader}

\subsection{Usage}

 vtkChacoReader is an unstructured grid source object that reads Chaco
 files.  The reader DOES NOT respond to piece requests. Chaco
 is a graph partitioning package developed at Sandia National Laboratories
 in the early 1990s.  (http://www.cs.sandia.gov/~bahendr/chaco.html)

 Note that the Chaco ''edges'' become VTK ''cells'', and the Chaco
 ''vertices'' become VTK ''points''.

To create an instance of class vtkChacoReader, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkChacoReader
\end{verbatim}
\subsection{Methods}

The class vtkChacoReader has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkChacoReader class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkChacoReader = obj.NewInstance ()|

\item  \verb|vtkChacoReader = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetBaseName (string )|

\item  \verb|string = obj.GetBaseName ()|

\item  \verb|obj.SetGenerateGlobalElementIdArray (int )|

\item  \verb|int = obj.GetGenerateGlobalElementIdArray ()|

\item  \verb|obj.GenerateGlobalElementIdArrayOn ()|

\item  \verb|obj.GenerateGlobalElementIdArrayOff ()|

\item  \verb|obj.SetGenerateGlobalNodeIdArray (int )|

\item  \verb|int = obj.GetGenerateGlobalNodeIdArray ()|

\item  \verb|obj.GenerateGlobalNodeIdArrayOn ()|

\item  \verb|obj.GenerateGlobalNodeIdArrayOff ()|

\item  \verb|obj.SetGenerateVertexWeightArrays (int )|

\item  \verb|int = obj.GetGenerateVertexWeightArrays ()|

\item  \verb|obj.GenerateVertexWeightArraysOn ()|

\item  \verb|obj.GenerateVertexWeightArraysOff ()|

\item  \verb|int = obj.GetNumberOfVertexWeights ()|

\item  \verb|string = obj.GetVertexWeightArrayName (int weight)|

\item  \verb|obj.SetGenerateEdgeWeightArrays (int )|

\item  \verb|int = obj.GetGenerateEdgeWeightArrays ()|

\item  \verb|obj.GenerateEdgeWeightArraysOn ()|

\item  \verb|obj.GenerateEdgeWeightArraysOff ()|

\item  \verb|int = obj.GetNumberOfEdgeWeights ()|

\item  \verb|string = obj.GetEdgeWeightArrayName (int weight)|

\item  \verb|int = obj.GetDimensionality ()| -  Access to meta data generated by RequestInformation.

\item  \verb|vtkIdType = obj.GetNumberOfEdges ()| -  Access to meta data generated by RequestInformation.

\item  \verb|vtkIdType = obj.GetNumberOfVertices ()| -  Access to meta data generated by RequestInformation.

\item  \verb|int = obj.GetNumberOfCellWeightArrays ()|

\item  \verb|int = obj.GetNumberOfPointWeightArrays ()|

\end{itemize}
