\section{vtkDataWriter}

\subsection{Usage}

 vtkDataWriter is a helper class that opens and writes the vtk header and 
 point data (e.g., scalars, vectors, normals, etc.) from a vtk data file. 
 See text for various formats.

To create an instance of class vtkDataWriter, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkDataWriter
\end{verbatim}
\subsection{Methods}

The class vtkDataWriter has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkDataWriter class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkDataWriter = obj.NewInstance ()|

\item  \verb|vtkDataWriter = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetFileName (string )| -  Specify file name of vtk polygon data file to write.

\item  \verb|string = obj.GetFileName ()| -  Specify file name of vtk polygon data file to write.

\item  \verb|obj.SetWriteToOutputString (int )| -  Enable writing to an OutputString instead of the default, a file.

\item  \verb|int = obj.GetWriteToOutputString ()| -  Enable writing to an OutputString instead of the default, a file.

\item  \verb|obj.WriteToOutputStringOn ()| -  Enable writing to an OutputString instead of the default, a file.

\item  \verb|obj.WriteToOutputStringOff ()| -  Enable writing to an OutputString instead of the default, a file.

\item  \verb|int = obj.GetOutputStringLength ()| -  When WriteToOutputString in on, then a string is allocated, written to,
 and can be retrieved with these methods.  The string is deleted during
 the next call to write ...

\item  \verb|string = obj.GetOutputString ()| -  When WriteToOutputString in on, then a string is allocated, written to,
 and can be retrieved with these methods.  The string is deleted during
 the next call to write ...

\item  \verb|string = obj.RegisterAndGetOutputString ()| -  This convenience method returns the string, sets the IVAR to NULL,
 so that the user is responsible for deleting the string.
 I am not sure what the name should be, so it may change in the future.

\item  \verb|obj.SetHeader (string )| -  Specify the header for the vtk data file.

\item  \verb|string = obj.GetHeader ()| -  Specify the header for the vtk data file.

\item  \verb|obj.SetFileType (int )| -  Specify file type (ASCII or BINARY) for vtk data file.

\item  \verb|int = obj.GetFileTypeMinValue ()| -  Specify file type (ASCII or BINARY) for vtk data file.

\item  \verb|int = obj.GetFileTypeMaxValue ()| -  Specify file type (ASCII or BINARY) for vtk data file.

\item  \verb|int = obj.GetFileType ()| -  Specify file type (ASCII or BINARY) for vtk data file.

\item  \verb|obj.SetFileTypeToASCII ()| -  Specify file type (ASCII or BINARY) for vtk data file.

\item  \verb|obj.SetFileTypeToBinary ()| -  Specify file type (ASCII or BINARY) for vtk data file.

\item  \verb|obj.SetScalarsName (string )| -  Give a name to the scalar data. If not specified, uses default
 name ''scalars''.

\item  \verb|string = obj.GetScalarsName ()| -  Give a name to the scalar data. If not specified, uses default
 name ''scalars''.

\item  \verb|obj.SetVectorsName (string )| -  Give a name to the vector data. If not specified, uses default
 name ''vectors''.

\item  \verb|string = obj.GetVectorsName ()| -  Give a name to the vector data. If not specified, uses default
 name ''vectors''.

\item  \verb|obj.SetTensorsName (string )| -  Give a name to the tensors data. If not specified, uses default
 name ''tensors''.

\item  \verb|string = obj.GetTensorsName ()| -  Give a name to the tensors data. If not specified, uses default
 name ''tensors''.

\item  \verb|obj.SetNormalsName (string )| -  Give a name to the normals data. If not specified, uses default
 name ''normals''.

\item  \verb|string = obj.GetNormalsName ()| -  Give a name to the normals data. If not specified, uses default
 name ''normals''.

\item  \verb|obj.SetTCoordsName (string )| -  Give a name to the texture coordinates data. If not specified, uses 
 default name ''textureCoords''.

\item  \verb|string = obj.GetTCoordsName ()| -  Give a name to the texture coordinates data. If not specified, uses 
 default name ''textureCoords''.

\item  \verb|obj.SetGlobalIdsName (string )| -  Give a name to the global ids data. If not specified, uses 
 default name ''global\_ids''.

\item  \verb|string = obj.GetGlobalIdsName ()| -  Give a name to the global ids data. If not specified, uses 
 default name ''global\_ids''.

\item  \verb|obj.SetPedigreeIdsName (string )| -  Give a name to the pedigree ids data. If not specified, uses 
 default name ''pedigree\_ids''.

\item  \verb|string = obj.GetPedigreeIdsName ()| -  Give a name to the pedigree ids data. If not specified, uses 
 default name ''pedigree\_ids''.

\item  \verb|obj.SetLookupTableName (string )| -  Give a name to the lookup table. If not specified, uses default
 name ''lookupTable''.

\item  \verb|string = obj.GetLookupTableName ()| -  Give a name to the lookup table. If not specified, uses default
 name ''lookupTable''.

\item  \verb|obj.SetFieldDataName (string )| -  Give a name to the field data. If not specified, uses default 
 name ''field''.

\item  \verb|string = obj.GetFieldDataName ()| -  Give a name to the field data. If not specified, uses default 
 name ''field''.

\end{itemize}
