\section{vtkSQLDatabaseGraphSource}

\subsection{Usage}

 This class combines vtkSQLDatabase, vtkSQLQuery, and vtkQueryToGraph to
 provide a convenience class for generating graphs from databases. 
 Also this class can be easily wrapped and used within ParaView / OverView.

To create an instance of class vtkSQLDatabaseGraphSource, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkSQLDatabaseGraphSource
\end{verbatim}
\subsection{Methods}

The class vtkSQLDatabaseGraphSource has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkSQLDatabaseGraphSource class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkSQLDatabaseGraphSource = obj.NewInstance ()|

\item  \verb|vtkSQLDatabaseGraphSource = obj.SafeDownCast (vtkObject o)|

\item  \verb|vtkStdString = obj.GetURL ()|

\item  \verb|obj.SetURL (vtkStdString \&url)|

\item  \verb|obj.SetPassword (vtkStdString \&password)|

\item  \verb|vtkStdString = obj.GetEdgeQuery ()|

\item  \verb|obj.SetEdgeQuery (vtkStdString \&query)|

\item  \verb|vtkStdString = obj.GetVertexQuery ()|

\item  \verb|obj.SetVertexQuery (vtkStdString \&query)|

\item  \verb|obj.AddLinkVertex (string column, string domain, int hidden)|

\item  \verb|obj.ClearLinkVertices ()|

\item  \verb|obj.AddLinkEdge (string column1, string column2)|

\item  \verb|obj.ClearLinkEdges ()|

\item  \verb|bool = obj.GetGenerateEdgePedigreeIds ()| -  If on (default), generate edge pedigree ids.
 If off, assign an array to be edge pedigree ids.

\item  \verb|obj.SetGenerateEdgePedigreeIds (bool )| -  If on (default), generate edge pedigree ids.
 If off, assign an array to be edge pedigree ids.

\item  \verb|obj.GenerateEdgePedigreeIdsOn ()| -  If on (default), generate edge pedigree ids.
 If off, assign an array to be edge pedigree ids.

\item  \verb|obj.GenerateEdgePedigreeIdsOff ()| -  If on (default), generate edge pedigree ids.
 If off, assign an array to be edge pedigree ids.

\item  \verb|obj.SetEdgePedigreeIdArrayName (string )| -  Use this array name for setting or generating edge pedigree ids.

\item  \verb|string = obj.GetEdgePedigreeIdArrayName ()| -  Use this array name for setting or generating edge pedigree ids.

\item  \verb|obj.SetDirected (bool )| -  If on (default), generate a directed output graph.
 If off, generate an undirected output graph.

\item  \verb|bool = obj.GetDirected ()| -  If on (default), generate a directed output graph.
 If off, generate an undirected output graph.

\item  \verb|obj.DirectedOn ()| -  If on (default), generate a directed output graph.
 If off, generate an undirected output graph.

\item  \verb|obj.DirectedOff ()| -  If on (default), generate a directed output graph.
 If off, generate an undirected output graph.

\end{itemize}
