\section{vtkGenerateIndexArray}

\subsection{Usage}

 Generates a new vtkIdTypeArray containing zero-base indices.

 vtkGenerateIndexArray operates in one of two distinct ''modes''.
 By default, it simply generates an index array containing
 monotonically-increasing integers in the range [0, N), where N
 is appropriately sized for the field type that will store the
 results.  This mode is useful for generating a unique ID field
 for datasets that have none.

 The second ''mode'' uses an existing array from the input data
 object as a ''reference''.  Distinct values from the reference
 array are sorted in ascending order, and an integer index in
 the range [0, N) is assigned to each.  The resulting map is
 used to populate the output index array, mapping each value
 in the reference array to its corresponding index and storing
 the result in the output array.  This mode is especially
 useful when generating tensors, since it allows us to ''map''
 from an array with arbitrary contents to an index that can
 be used as tensor coordinates.

To create an instance of class vtkGenerateIndexArray, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkGenerateIndexArray
\end{verbatim}
\subsection{Methods}

The class vtkGenerateIndexArray has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkGenerateIndexArray class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkGenerateIndexArray = obj.NewInstance ()|

\item  \verb|vtkGenerateIndexArray = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetArrayName (string )| -  Control the output index array name.  Default: ''index''. 

\item  \verb|string = obj.GetArrayName ()| -  Control the output index array name.  Default: ''index''. 

\item  \verb|obj.SetFieldType (int )| -  Control the location where the index array will be stored.

\item  \verb|int = obj.GetFieldType ()| -  Control the location where the index array will be stored.

\item  \verb|obj.SetReferenceArrayName (string )| -  Specifies an optional reference array for index-generation.

\item  \verb|string = obj.GetReferenceArrayName ()| -  Specifies an optional reference array for index-generation.

\item  \verb|obj.SetPedigreeID (int )| -  Specifies whether the index array should be marked as
 pedigree ids.  Default: false.

\item  \verb|int = obj.GetPedigreeID ()| -  Specifies whether the index array should be marked as
 pedigree ids.  Default: false.

\end{itemize}
