\section{vtkExtractSelectedGraph}

\subsection{Usage}

 The first input is a vtkGraph to take a subgraph from.
 The second input (optional) is a vtkSelection containing selected 
 indices. The third input (optional) is a vtkAnnotationsLayers whose 
 annotations contain selected specifying selected indices.
 The vtkSelection may have FIELD\_TYPE set to POINTS (a vertex selection)
 or CELLS (an edge selection).  A vertex selection preserves all edges
 that connect selected vertices.  An edge selection preserves all vertices
 that are adjacent to at least one selected edge.  Alternately, you may
 indicate that an edge selection should maintain the full set of vertices,
 by turning RemoveIsolatedVertices off.

To create an instance of class vtkExtractSelectedGraph, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkExtractSelectedGraph
\end{verbatim}
\subsection{Methods}

The class vtkExtractSelectedGraph has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkExtractSelectedGraph class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkExtractSelectedGraph = obj.NewInstance ()|

\item  \verb|vtkExtractSelectedGraph = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetSelectionConnection (vtkAlgorithmOutput in)| -  A convenience method for setting the second input (i.e. the selection).

\item  \verb|obj.SetAnnotationLayersConnection (vtkAlgorithmOutput in)| -  A convenience method for setting the third input (i.e. the annotation layers).

\item  \verb|obj.SetRemoveIsolatedVertices (bool )| -  If set, removes vertices with no adjacent edges in an edge selection.
 A vertex selection ignores this flag and always returns the full set 
 of selected vertices.  Default is on.

\item  \verb|bool = obj.GetRemoveIsolatedVertices ()| -  If set, removes vertices with no adjacent edges in an edge selection.
 A vertex selection ignores this flag and always returns the full set 
 of selected vertices.  Default is on.

\item  \verb|obj.RemoveIsolatedVerticesOn ()| -  If set, removes vertices with no adjacent edges in an edge selection.
 A vertex selection ignores this flag and always returns the full set 
 of selected vertices.  Default is on.

\item  \verb|obj.RemoveIsolatedVerticesOff ()| -  If set, removes vertices with no adjacent edges in an edge selection.
 A vertex selection ignores this flag and always returns the full set 
 of selected vertices.  Default is on.

\item  \verb|int = obj.FillInputPortInformation (int port, vtkInformation info)| -  Specify the first vtkGraph input and the second vtkSelection input.

\end{itemize}
