\section{vtkFixedWidthTextReader}

\subsection{Usage}


 vtkFixedWidthTextReader reads in a table from a text file where
 each column occupies a certain number of characters.
 
 This class emits ProgressEvent for every 100 lines it reads.
 

To create an instance of class vtkFixedWidthTextReader, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkFixedWidthTextReader
\end{verbatim}
\subsection{Methods}

The class vtkFixedWidthTextReader has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkFixedWidthTextReader class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkFixedWidthTextReader = obj.NewInstance ()|

\item  \verb|vtkFixedWidthTextReader = obj.SafeDownCast (vtkObject o)|

\item  \verb|string = obj.GetFileName ()|

\item  \verb|obj.SetFileName (string )|

\item  \verb|obj.SetFieldWidth (int )| -  Set/get the field width

\item  \verb|int = obj.GetFieldWidth ()| -  Set/get the field width

\item  \verb|obj.SetStripWhiteSpace (bool )| -  If set, this flag will cause the reader to strip whitespace from
 the beginning and ending of each field.  Defaults to off.

\item  \verb|bool = obj.GetStripWhiteSpace ()| -  If set, this flag will cause the reader to strip whitespace from
 the beginning and ending of each field.  Defaults to off.

\item  \verb|obj.StripWhiteSpaceOn ()| -  If set, this flag will cause the reader to strip whitespace from
 the beginning and ending of each field.  Defaults to off.

\item  \verb|obj.StripWhiteSpaceOff ()| -  If set, this flag will cause the reader to strip whitespace from
 the beginning and ending of each field.  Defaults to off.

\item  \verb|bool = obj.GetHaveHeaders ()| -  Set/get whether to treat the first line of the file as headers.

\item  \verb|obj.SetHaveHeaders (bool )| -  Set/get whether to treat the first line of the file as headers.

\item  \verb|obj.HaveHeadersOn ()| -  Set/get whether to treat the first line of the file as headers.

\item  \verb|obj.HaveHeadersOff ()| -  Set/get whether to treat the first line of the file as headers.

\end{itemize}
