\section{vtkImageEllipsoidSource}

\subsection{Usage}

 vtkImageEllipsoidSource creates a binary image of a ellipsoid.  It was created
 as an example of a simple source, and to test the mask filter.
 It is also used internally in vtkImageDilateErode3D.

To create an instance of class vtkImageEllipsoidSource, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkImageEllipsoidSource
\end{verbatim}
\subsection{Methods}

The class vtkImageEllipsoidSource has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkImageEllipsoidSource class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkImageEllipsoidSource = obj.NewInstance ()|

\item  \verb|vtkImageEllipsoidSource = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetWholeExtent (int extent[6])| -  Set/Get the extent of the whole output image.

\item  \verb|obj.SetWholeExtent (int minX, int maxX, int minY, int maxY, int minZ, int maxZ)| -  Set/Get the extent of the whole output image.

\item  \verb|obj.GetWholeExtent (int extent[6])| -  Set/Get the extent of the whole output image.

\item  \verb|int = obj.GetWholeExtent ()| -  Set/Get the center of the ellipsoid.

\item  \verb|obj.SetCenter (double , double , double )| -  Set/Get the center of the ellipsoid.

\item  \verb|obj.SetCenter (double  a[3])| -  Set/Get the center of the ellipsoid.

\item  \verb|double = obj. GetCenter ()| -  Set/Get the center of the ellipsoid.

\item  \verb|obj.SetRadius (double , double , double )| -  Set/Get the radius of the ellipsoid.

\item  \verb|obj.SetRadius (double  a[3])| -  Set/Get the radius of the ellipsoid.

\item  \verb|double = obj. GetRadius ()| -  Set/Get the radius of the ellipsoid.

\item  \verb|obj.SetInValue (double )| -  Set/Get the inside pixel values.

\item  \verb|double = obj.GetInValue ()| -  Set/Get the inside pixel values.

\item  \verb|obj.SetOutValue (double )| -  Set/Get the outside pixel values.

\item  \verb|double = obj.GetOutValue ()| -  Set/Get the outside pixel values.

\item  \verb|obj.SetOutputScalarType (int )| -  Set what type of scalar data this source should generate.

\item  \verb|int = obj.GetOutputScalarType ()| -  Set what type of scalar data this source should generate.

\item  \verb|obj.SetOutputScalarTypeToFloat ()| -  Set what type of scalar data this source should generate.

\item  \verb|obj.SetOutputScalarTypeToDouble ()| -  Set what type of scalar data this source should generate.

\item  \verb|obj.SetOutputScalarTypeToLong ()| -  Set what type of scalar data this source should generate.

\item  \verb|obj.SetOutputScalarTypeToUnsignedLong ()| -  Set what type of scalar data this source should generate.

\item  \verb|obj.SetOutputScalarTypeToInt ()| -  Set what type of scalar data this source should generate.

\item  \verb|obj.SetOutputScalarTypeToUnsignedInt ()| -  Set what type of scalar data this source should generate.

\item  \verb|obj.SetOutputScalarTypeToShort ()| -  Set what type of scalar data this source should generate.

\item  \verb|obj.SetOutputScalarTypeToUnsignedShort ()| -  Set what type of scalar data this source should generate.

\item  \verb|obj.SetOutputScalarTypeToChar ()| -  Set what type of scalar data this source should generate.

\item  \verb|obj.SetOutputScalarTypeToUnsignedChar ()|

\end{itemize}
