\section{vtkImageGridSource}

\subsection{Usage}

 vtkImageGridSource produces an image of a grid.  The
 default output type is double.

To create an instance of class vtkImageGridSource, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkImageGridSource
\end{verbatim}
\subsection{Methods}

The class vtkImageGridSource has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkImageGridSource class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkImageGridSource = obj.NewInstance ()|

\item  \verb|vtkImageGridSource = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetGridSpacing (int , int , int )| -  Set/Get the grid spacing in pixel units.  Default (10,10,0).
 A value of zero means no grid.

\item  \verb|obj.SetGridSpacing (int  a[3])| -  Set/Get the grid spacing in pixel units.  Default (10,10,0).
 A value of zero means no grid.

\item  \verb|int = obj. GetGridSpacing ()| -  Set/Get the grid spacing in pixel units.  Default (10,10,0).
 A value of zero means no grid.

\item  \verb|obj.SetGridOrigin (int , int , int )| -  Set/Get the grid origin, in ijk integer values.  Default (0,0,0).

\item  \verb|obj.SetGridOrigin (int  a[3])| -  Set/Get the grid origin, in ijk integer values.  Default (0,0,0).

\item  \verb|int = obj. GetGridOrigin ()| -  Set/Get the grid origin, in ijk integer values.  Default (0,0,0).

\item  \verb|obj.SetLineValue (double )| -  Set the grey level of the lines. Default 1.0.

\item  \verb|double = obj.GetLineValue ()| -  Set the grey level of the lines. Default 1.0.

\item  \verb|obj.SetFillValue (double )| -  Set the grey level of the fill. Default 0.0.

\item  \verb|double = obj.GetFillValue ()| -  Set the grey level of the fill. Default 0.0.

\item  \verb|obj.SetDataScalarType (int )| -  Set/Get the data type of pixels in the imported data.
 As a convenience, the OutputScalarType is set to the same value.

\item  \verb|obj.SetDataScalarTypeToDouble ()| -  Set/Get the data type of pixels in the imported data.
 As a convenience, the OutputScalarType is set to the same value.

\item  \verb|obj.SetDataScalarTypeToInt ()| -  Set/Get the data type of pixels in the imported data.
 As a convenience, the OutputScalarType is set to the same value.

\item  \verb|obj.SetDataScalarTypeToShort ()| -  Set/Get the data type of pixels in the imported data.
 As a convenience, the OutputScalarType is set to the same value.

\item  \verb|obj.SetDataScalarTypeToUnsignedShort ()| -  Set/Get the data type of pixels in the imported data.
 As a convenience, the OutputScalarType is set to the same value.

\item  \verb|obj.SetDataScalarTypeToUnsignedChar ()| -  Set/Get the data type of pixels in the imported data.
 As a convenience, the OutputScalarType is set to the same value.

\item  \verb|int = obj.GetDataScalarType ()| -  Set/Get the data type of pixels in the imported data.
 As a convenience, the OutputScalarType is set to the same value.

\item  \verb|string = obj.GetDataScalarTypeAsString ()| -  Set/Get the extent of the whole output image,
 Default: (0,255,0,255,0,0)

\item  \verb|obj.SetDataExtent (int , int , int , int , int , int )| -  Set/Get the extent of the whole output image,
 Default: (0,255,0,255,0,0)

\item  \verb|obj.SetDataExtent (int  a[6])| -  Set/Get the extent of the whole output image,
 Default: (0,255,0,255,0,0)

\item  \verb|int = obj. GetDataExtent ()| -  Set/Get the extent of the whole output image,
 Default: (0,255,0,255,0,0)

\item  \verb|obj.SetDataSpacing (double , double , double )| -  Set/Get the pixel spacing.

\item  \verb|obj.SetDataSpacing (double  a[3])| -  Set/Get the pixel spacing.

\item  \verb|double = obj. GetDataSpacing ()| -  Set/Get the pixel spacing.

\item  \verb|obj.SetDataOrigin (double , double , double )| -  Set/Get the origin of the data.

\item  \verb|obj.SetDataOrigin (double  a[3])| -  Set/Get the origin of the data.

\item  \verb|double = obj. GetDataOrigin ()| -  Set/Get the origin of the data.

\end{itemize}
