\section{vtkBYUReader}

\subsection{Usage}

 vtkBYUReader is a source object that reads MOVIE.BYU polygon files.
 These files consist of a geometry file (.g), a scalar file (.s), a 
 displacement or vector file (.d), and a 2D texture coordinate file
 (.t).

To create an instance of class vtkBYUReader, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkBYUReader
\end{verbatim}
\subsection{Methods}

The class vtkBYUReader has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkBYUReader class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkBYUReader = obj.NewInstance ()|

\item  \verb|vtkBYUReader = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetGeometryFileName (string )| -  Specify name of geometry FileName.

\item  \verb|string = obj.GetGeometryFileName ()| -  Specify name of geometry FileName.

\item  \verb|obj.SetFileName (string f)| -  Specify name of geometry FileName (alias).

\item  \verb|string = obj.GetFileName ()| -  Specify name of displacement FileName.

\item  \verb|obj.SetDisplacementFileName (string )| -  Specify name of displacement FileName.

\item  \verb|string = obj.GetDisplacementFileName ()| -  Specify name of displacement FileName.

\item  \verb|obj.SetScalarFileName (string )| -  Specify name of scalar FileName.

\item  \verb|string = obj.GetScalarFileName ()| -  Specify name of scalar FileName.

\item  \verb|obj.SetTextureFileName (string )| -  Specify name of texture coordinates FileName.

\item  \verb|string = obj.GetTextureFileName ()| -  Specify name of texture coordinates FileName.

\item  \verb|obj.SetReadDisplacement (int )| -  Turn on/off the reading of the displacement file.

\item  \verb|int = obj.GetReadDisplacement ()| -  Turn on/off the reading of the displacement file.

\item  \verb|obj.ReadDisplacementOn ()| -  Turn on/off the reading of the displacement file.

\item  \verb|obj.ReadDisplacementOff ()| -  Turn on/off the reading of the displacement file.

\item  \verb|obj.SetReadScalar (int )| -  Turn on/off the reading of the scalar file.

\item  \verb|int = obj.GetReadScalar ()| -  Turn on/off the reading of the scalar file.

\item  \verb|obj.ReadScalarOn ()| -  Turn on/off the reading of the scalar file.

\item  \verb|obj.ReadScalarOff ()| -  Turn on/off the reading of the scalar file.

\item  \verb|obj.SetReadTexture (int )| -  Turn on/off the reading of the texture coordinate file.
 Specify name of geometry FileName.

\item  \verb|int = obj.GetReadTexture ()| -  Turn on/off the reading of the texture coordinate file.
 Specify name of geometry FileName.

\item  \verb|obj.ReadTextureOn ()| -  Turn on/off the reading of the texture coordinate file.
 Specify name of geometry FileName.

\item  \verb|obj.ReadTextureOff ()| -  Turn on/off the reading of the texture coordinate file.
 Specify name of geometry FileName.

\item  \verb|obj.SetPartNumber (int )| -  Set/Get the part number to be read.

\item  \verb|int = obj.GetPartNumberMinValue ()| -  Set/Get the part number to be read.

\item  \verb|int = obj.GetPartNumberMaxValue ()| -  Set/Get the part number to be read.

\item  \verb|int = obj.GetPartNumber ()| -  Set/Get the part number to be read.

\end{itemize}
