\section{vtkTreeFieldAggregator}

\subsection{Usage}

 vtkTreeFieldAggregator may be used to assign sizes to all the vertices in the
 tree, based on the sizes of the leaves.  The size of a vertex will equal
 the sum of the sizes of the child vertices.  If you have a data array with
 values for all leaves, you may specify that array, and the values will
 be filled in for interior tree vertices.  If you do not yet have an array,
 you may tell the filter to create a new array, assuming that the size
 of each leaf vertex is 1.  You may optionally set a flag to first take the
 log of all leaf values before aggregating.

To create an instance of class vtkTreeFieldAggregator, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkTreeFieldAggregator
\end{verbatim}
\subsection{Methods}

The class vtkTreeFieldAggregator has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkTreeFieldAggregator class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkTreeFieldAggregator = obj.NewInstance ()|

\item  \verb|vtkTreeFieldAggregator = obj.SafeDownCast (vtkObject o)|

\item  \verb|string = obj.GetField ()| -  The field to aggregate.  If this is a string array, the entries are converted to double.
 TODO: Remove this field and use the ArrayToProcess in vtkAlgorithm.

\item  \verb|obj.SetField (string )| -  The field to aggregate.  If this is a string array, the entries are converted to double.
 TODO: Remove this field and use the ArrayToProcess in vtkAlgorithm.

\item  \verb|double = obj.GetMinValue ()| -  If the value of the vertex is less than MinValue then consider it's value to be minVal.

\item  \verb|obj.SetMinValue (double )| -  If the value of the vertex is less than MinValue then consider it's value to be minVal.

\item  \verb|obj.SetLeafVertexUnitSize (bool )| -  If set, the algorithm will assume a size of 1 for each leaf vertex.

\item  \verb|bool = obj.GetLeafVertexUnitSize ()| -  If set, the algorithm will assume a size of 1 for each leaf vertex.

\item  \verb|obj.LeafVertexUnitSizeOn ()| -  If set, the algorithm will assume a size of 1 for each leaf vertex.

\item  \verb|obj.LeafVertexUnitSizeOff ()| -  If set, the algorithm will assume a size of 1 for each leaf vertex.

\item  \verb|obj.SetLogScale (bool )| -  If set, the leaf values in the tree will be logarithmically scaled (base 10).

\item  \verb|bool = obj.GetLogScale ()| -  If set, the leaf values in the tree will be logarithmically scaled (base 10).

\item  \verb|obj.LogScaleOn ()| -  If set, the leaf values in the tree will be logarithmically scaled (base 10).

\item  \verb|obj.LogScaleOff ()| -  If set, the leaf values in the tree will be logarithmically scaled (base 10).

\end{itemize}
