\section{vtkUGFacetReader}

\subsection{Usage}

 vtkUGFacetReader is a source object that reads Unigraphics facet files.
 Unigraphics is a solid modeling system; facet files are the polygonal
 plot files it uses to create 3D plots.

To create an instance of class vtkUGFacetReader, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkUGFacetReader
\end{verbatim}
\subsection{Methods}

The class vtkUGFacetReader has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkUGFacetReader class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkUGFacetReader = obj.NewInstance ()|

\item  \verb|vtkUGFacetReader = obj.SafeDownCast (vtkObject o)|

\item  \verb|long = obj.GetMTime ()| -  Overload standard modified time function. If locator is modified,
 then this object is modified as well.

\item  \verb|obj.SetFileName (string )| -  Specify Unigraphics file name.

\item  \verb|string = obj.GetFileName ()| -  Specify Unigraphics file name.

\item  \verb|int = obj.GetNumberOfParts ()| -  Special methods for interrogating the data file.

\item  \verb|short = obj.GetPartColorIndex (int partId)| -  Retrieve color index for the parts in the file.

\item  \verb|obj.SetPartNumber (int )| -  Specify the desired part to extract. The part number must range between
 [0,NumberOfParts-1]. If the value is =(-1), then all parts will be 
 extracted. If the value is <(-1), then no parts will be  extracted but 
 the part colors will be updated.

\item  \verb|int = obj.GetPartNumber ()| -  Specify the desired part to extract. The part number must range between
 [0,NumberOfParts-1]. If the value is =(-1), then all parts will be 
 extracted. If the value is <(-1), then no parts will be  extracted but 
 the part colors will be updated.

\item  \verb|obj.SetMerging (int )| -  Turn on/off merging of points/triangles.

\item  \verb|int = obj.GetMerging ()| -  Turn on/off merging of points/triangles.

\item  \verb|obj.MergingOn ()| -  Turn on/off merging of points/triangles.

\item  \verb|obj.MergingOff ()| -  Turn on/off merging of points/triangles.

\item  \verb|obj.SetLocator (vtkIncrementalPointLocator locator)| -  Specify a spatial locator for merging points. By
 default an instance of vtkMergePoints is used.

\item  \verb|vtkIncrementalPointLocator = obj.GetLocator ()| -  Specify a spatial locator for merging points. By
 default an instance of vtkMergePoints is used.

\item  \verb|obj.CreateDefaultLocator ()| -  Create default locator. Used to create one when none is specified.

\end{itemize}
