\section{vtkAbstractParticleWriter}

\subsection{Usage}

 vtkAbstractParticleWriter is an abstract class which is used by
 vtkTemporalStreamTracer to write particles out during simulations.
 This class is abstract and provides a TimeStep and FileName.
 Subclasses of this should provide the necessary IO.

To create an instance of class vtkAbstractParticleWriter, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkAbstractParticleWriter
\end{verbatim}
\subsection{Methods}

The class vtkAbstractParticleWriter has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkAbstractParticleWriter class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkAbstractParticleWriter = obj.NewInstance ()|

\item  \verb|vtkAbstractParticleWriter = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetTimeStep (int )| -  Set/get the TimeStep that is being written

\item  \verb|int = obj.GetTimeStep ()| -  Set/get the TimeStep that is being written

\item  \verb|obj.SetTimeValue (double )| -  Before writing the current data out, set the TimeValue (optional)
 The TimeValue is a float/double value that corresonds to the real
 time of the data, it may not be regular, whereas the TimeSteps 
 are simple increments.

\item  \verb|double = obj.GetTimeValue ()| -  Before writing the current data out, set the TimeValue (optional)
 The TimeValue is a float/double value that corresonds to the real
 time of the data, it may not be regular, whereas the TimeSteps 
 are simple increments.

\item  \verb|obj.SetFileName (string )| -  Set/get the FileName that is being written to

\item  \verb|string = obj.GetFileName ()| -  Set/get the FileName that is being written to

\item  \verb|obj.SetCollectiveIO (int )| -  When running in parallel, this writer may be capable of 
 Collective IO operations (HDF5). By default, this is off.

\item  \verb|int = obj.GetCollectiveIO ()| -  When running in parallel, this writer may be capable of 
 Collective IO operations (HDF5). By default, this is off.

\item  \verb|obj.SetWriteModeToCollective ()| -  When running in parallel, this writer may be capable of 
 Collective IO operations (HDF5). By default, this is off.

\item  \verb|obj.SetWriteModeToIndependent ()| -  When running in parallel, this writer may be capable of 
 Collective IO operations (HDF5). By default, this is off.

\item  \verb|obj.CloseFile ()| -  Close the file after a write. This is optional but
 may protect against data loss in between steps

\end{itemize}
