\section{vtkBYUWriter}

\subsection{Usage}

 vtkBYUWriter writes MOVIE.BYU polygonal files. These files consist 
 of a geometry file (.g), a scalar file (.s), a displacement or 
 vector file (.d), and a 2D texture coordinate file (.t). These files 
 must be specified to the object, the appropriate boolean 
 variables must be true, and data must be available from the input
 for the files to be written.
 WARNING: this writer does not currently write triangle strips. Use
 vtkTriangleFilter to convert strips to triangles.

To create an instance of class vtkBYUWriter, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkBYUWriter
\end{verbatim}
\subsection{Methods}

The class vtkBYUWriter has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkBYUWriter class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkBYUWriter = obj.NewInstance ()|

\item  \verb|vtkBYUWriter = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetGeometryFileName (string )| -  Specify the name of the geometry file to write.

\item  \verb|string = obj.GetGeometryFileName ()| -  Specify the name of the geometry file to write.

\item  \verb|obj.SetDisplacementFileName (string )| -  Specify the name of the displacement file to write.

\item  \verb|string = obj.GetDisplacementFileName ()| -  Specify the name of the displacement file to write.

\item  \verb|obj.SetScalarFileName (string )| -  Specify the name of the scalar file to write.

\item  \verb|string = obj.GetScalarFileName ()| -  Specify the name of the scalar file to write.

\item  \verb|obj.SetTextureFileName (string )| -  Specify the name of the texture file to write.

\item  \verb|string = obj.GetTextureFileName ()| -  Specify the name of the texture file to write.

\item  \verb|obj.SetWriteDisplacement (int )| -  Turn on/off writing the displacement file.

\item  \verb|int = obj.GetWriteDisplacement ()| -  Turn on/off writing the displacement file.

\item  \verb|obj.WriteDisplacementOn ()| -  Turn on/off writing the displacement file.

\item  \verb|obj.WriteDisplacementOff ()| -  Turn on/off writing the displacement file.

\item  \verb|obj.SetWriteScalar (int )| -  Turn on/off writing the scalar file.

\item  \verb|int = obj.GetWriteScalar ()| -  Turn on/off writing the scalar file.

\item  \verb|obj.WriteScalarOn ()| -  Turn on/off writing the scalar file.

\item  \verb|obj.WriteScalarOff ()| -  Turn on/off writing the scalar file.

\item  \verb|obj.SetWriteTexture (int )| -  Turn on/off writing the texture file.

\item  \verb|int = obj.GetWriteTexture ()| -  Turn on/off writing the texture file.

\item  \verb|obj.WriteTextureOn ()| -  Turn on/off writing the texture file.

\item  \verb|obj.WriteTextureOff ()| -  Turn on/off writing the texture file.

\end{itemize}
