\section{vtkSQLiteQuery}

\subsection{Usage}


 This is an implementation of vtkSQLQuery for SQLite databases.  See
 the documentation for vtkSQLQuery for information about what the
 methods do.

 .SECTION Bugs

 Sometimes Execute() will return false (meaning an error) but
 GetLastErrorText() winds up null.  I am not certain why this is
 happening.

 .SECTION Thanks
 Thanks to Andrew Wilson from Sandia National Laboratories for implementing
 this class.


To create an instance of class vtkSQLiteQuery, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkSQLiteQuery
\end{verbatim}
\subsection{Methods}

The class vtkSQLiteQuery has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkSQLiteQuery class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkSQLiteQuery = obj.NewInstance ()|

\item  \verb|vtkSQLiteQuery = obj.SafeDownCast (vtkObject o)|

\item  \verb|bool = obj.SetQuery (string query)| -  Set the SQL query string.  This must be performed before
 Execute() or BindParameter() can be called.

\item  \verb|bool = obj.Execute ()| -  Execute the query.  This must be performed
 before any field name or data access functions
 are used.

\item  \verb|int = obj.GetNumberOfFields ()| -  The number of fields in the query result.

\item  \verb|string = obj.GetFieldName (int i)| -  Return the name of the specified query field.

\item  \verb|int = obj.GetFieldType (int i)| -  Return the type of the field, using the constants defined in vtkType.h.

\item  \verb|bool = obj.NextRow ()| -  Advance row, return false if past end.

\item  \verb|bool = obj.HasError ()| -  Return true if there is an error on the current query.

\item  \verb|bool = obj.BeginTransaction ()| -  Begin, abort (roll back), or commit a transaction.

\item  \verb|bool = obj.RollbackTransaction ()| -  Begin, abort (roll back), or commit a transaction.

\item  \verb|bool = obj.CommitTransaction ()| -  Begin, abort (roll back), or commit a transaction.

\item  \verb|string = obj.GetLastErrorText ()| -  Get the last error text from the query

\item  \verb|bool = obj.BindParameter (int index, int value)| -  The following methods bind a parameter value to a placeholder in
 the SQL string.  See the documentation for vtkSQLQuery for
 further explanation.  The driver makes internal copies of string
 and BLOB parameters so you don't need to worry about keeping them
 in scope until the query finishes executing.

\item  \verb|bool = obj.BindParameter (int index, float value)| -  The following methods bind a parameter value to a placeholder in
 the SQL string.  See the documentation for vtkSQLQuery for
 further explanation.  The driver makes internal copies of string
 and BLOB parameters so you don't need to worry about keeping them
 in scope until the query finishes executing.

\item  \verb|bool = obj.BindParameter (int index, double value)| -  The following methods bind a parameter value to a placeholder in
 the SQL string.  See the documentation for vtkSQLQuery for
 further explanation.  The driver makes internal copies of string
 and BLOB parameters so you don't need to worry about keeping them
 in scope until the query finishes executing.

\item  \verb|bool = obj.BindParameter (int index, string stringValue)| -  Bind a string value -- string must be null-terminated

\item  \verb|bool = obj.ClearParameterBindings ()| -  Bind a blob value.  Not all databases support blobs as a data
 type.  Check vtkSQLDatabase::IsSupported(VTK\_SQL\_FEATURE\_BLOB) to
 make sure.

\end{itemize}
