\section{vtkEnSightWriter}

\subsection{Usage}

 vtkEnSightWriter is a source object that writes binary 
 unstructured grid data files in EnSight format. See EnSight Manual for 
 format details

To create an instance of class vtkEnSightWriter, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkEnSightWriter
\end{verbatim}
\subsection{Methods}

The class vtkEnSightWriter has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkEnSightWriter class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkEnSightWriter = obj.NewInstance ()|

\item  \verb|vtkEnSightWriter = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetProcessNumber (int )|

\item  \verb|int = obj.GetProcessNumber ()|

\item  \verb|obj.SetPath (string )| -  Specify path of EnSight data files to write.

\item  \verb|string = obj.GetPath ()| -  Specify path of EnSight data files to write.

\item  \verb|obj.SetBaseName (string )| -  Specify base name of EnSight data files to write.

\item  \verb|string = obj.GetBaseName ()| -  Specify base name of EnSight data files to write.

\item  \verb|obj.SetFileName (string )| -  Specify the path and base name of the output files.

\item  \verb|string = obj.GetFileName ()| -  Specify the path and base name of the output files.

\item  \verb|obj.SetTimeStep (int )|

\item  \verb|int = obj.GetTimeStep ()|

\item  \verb|obj.SetGhostLevel (int )|

\item  \verb|int = obj.GetGhostLevel ()|

\item  \verb|obj.SetTransientGeometry (bool )|

\item  \verb|bool = obj.GetTransientGeometry ()|

\item  \verb|obj.SetNumberOfBlocks (int )|

\item  \verb|int = obj.GetNumberOfBlocks ()|

\item  \verb|obj.SetBlockIDs (int val)|

\item  \verb|obj.SetInput (vtkUnstructuredGrid input)| -  Specify the input data or filter.

\item  \verb|vtkUnstructuredGrid = obj.GetInput ()| -  Specify the input data or filter.

\item  \verb|obj.WriteCaseFile (int TotalTimeSteps)|

\item  \verb|obj.WriteSOSCaseFile (int NumProcs)|

\item  \verb|obj.SetModelMetadata (vtkModelMetadata model)|

\item  \verb|vtkModelMetadata = obj.GetModelMetadata ()|

\end{itemize}
