\section{vtkCollectPolyData}

\subsection{Usage}

 This filter has code to collect polydat from across processes onto node 0.
 Collection can be turned on or off using the ''PassThrough'' flag.

To create an instance of class vtkCollectPolyData, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkCollectPolyData
\end{verbatim}
\subsection{Methods}

The class vtkCollectPolyData has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkCollectPolyData class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkCollectPolyData = obj.NewInstance ()|

\item  \verb|vtkCollectPolyData = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetController (vtkMultiProcessController )| -  By defualt this filter uses the global controller,
 but this method can be used to set another instead.

\item  \verb|vtkMultiProcessController = obj.GetController ()| -  By defualt this filter uses the global controller,
 but this method can be used to set another instead.

\item  \verb|obj.SetSocketController (vtkSocketController )| -  When this filter is being used in client-server mode,
 this is the controller used to communicate between
 client and server.  Client should not set the other controller.

\item  \verb|vtkSocketController = obj.GetSocketController ()| -  When this filter is being used in client-server mode,
 this is the controller used to communicate between
 client and server.  Client should not set the other controller.

\item  \verb|obj.SetPassThrough (int )| -  To collect or just copy input to output. Off (collect) by default.

\item  \verb|int = obj.GetPassThrough ()| -  To collect or just copy input to output. Off (collect) by default.

\item  \verb|obj.PassThroughOn ()| -  To collect or just copy input to output. Off (collect) by default.

\item  \verb|obj.PassThroughOff ()| -  To collect or just copy input to output. Off (collect) by default.

\end{itemize}
