\section{vtkCollectGraph}

\subsection{Usage}

 This filter has code to collect a graph from across processes onto vertex 0.
 Collection can be turned on or off using the ''PassThrough'' flag.

To create an instance of class vtkCollectGraph, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkCollectGraph
\end{verbatim}
\subsection{Methods}

The class vtkCollectGraph has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkCollectGraph class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkCollectGraph = obj.NewInstance ()|

\item  \verb|vtkCollectGraph = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetController (vtkMultiProcessController )| -  By defualt this filter uses the global controller,
 but this method can be used to set another instead.

\item  \verb|vtkMultiProcessController = obj.GetController ()| -  By defualt this filter uses the global controller,
 but this method can be used to set another instead.

\item  \verb|obj.SetSocketController (vtkSocketController )| -  When this filter is being used in client-server mode,
 this is the controller used to communicate between
 client and server.  Client should not set the other controller.

\item  \verb|vtkSocketController = obj.GetSocketController ()| -  When this filter is being used in client-server mode,
 this is the controller used to communicate between
 client and server.  Client should not set the other controller.

\item  \verb|obj.SetPassThrough (int )| -  To collect or just copy input to output. Off (collect) by default.

\item  \verb|int = obj.GetPassThrough ()| -  To collect or just copy input to output. Off (collect) by default.

\item  \verb|obj.PassThroughOn ()| -  To collect or just copy input to output. Off (collect) by default.

\item  \verb|obj.PassThroughOff ()| -  To collect or just copy input to output. Off (collect) by default.

\item  \verb|obj.SetOutputType (int )| -  Directedness flag, used to signal whether the output graph is directed or undirected.
 DIRECTED\_OUTPUT expects that this filter is generating a directed graph.
 UNDIRECTED\_OUTPUT expects that this filter is generating an undirected graph.
 DIRECTED\_OUTPUT and UNDIRECTED\_OUTPUT flags should only be set on the client
 filter.  Server filters should be set to USE\_INPUT\_TYPE since they have valid 
 input and the directedness is determined from the input type.

\item  \verb|int = obj.GetOutputType ()| -  Directedness flag, used to signal whether the output graph is directed or undirected.
 DIRECTED\_OUTPUT expects that this filter is generating a directed graph.
 UNDIRECTED\_OUTPUT expects that this filter is generating an undirected graph.
 DIRECTED\_OUTPUT and UNDIRECTED\_OUTPUT flags should only be set on the client
 filter.  Server filters should be set to USE\_INPUT\_TYPE since they have valid 
 input and the directedness is determined from the input type.

\end{itemize}
