\section{vtkDummyController}

\subsection{Usage}

 This is a dummy controller which can be used by applications which always
 require a controller but are also compile on systems without threads
 or mpi.

To create an instance of class vtkDummyController, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkDummyController
\end{verbatim}
\subsection{Methods}

The class vtkDummyController has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkDummyController class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkDummyController = obj.NewInstance ()|

\item  \verb|vtkDummyController = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.Finalize ()| -  This method is for setting up the processes.

\item  \verb|obj.Finalize (int )| -  This method always returns 0.

\item  \verb|int = obj.GetLocalProcessId ()| -  Directly calls the single method.

\item  \verb|obj.SingleMethodExecute ()| -  Directly calls the single method.

\item  \verb|obj.MultipleMethodExecute ()| -  Directly calls multiple method 0.

\item  \verb|obj.CreateOutputWindow ()| -  If you don't need any special functionality from the controller, you
 can swap out the dummy communicator for another one.

\item  \verb|vtkCommunicator = obj.GetCommunicator ()| -  If you don't need any special functionality from the controller, you
 can swap out the dummy communicator for another one.

\item  \verb|vtkCommunicator = obj.GetRMICommunicator ()| -  If you don't need any special functionality from the controller, you
 can swap out the dummy communicator for another one.

\item  \verb|obj.SetCommunicator (vtkCommunicator )| -  If you don't need any special functionality from the controller, you
 can swap out the dummy communicator for another one.

\item  \verb|obj.SetRMICommunicator (vtkCommunicator )| -  If you don't need any special functionality from the controller, you
 can swap out the dummy communicator for another one.

\end{itemize}
