\section{vtkExtractCTHPart}

\subsection{Usage}

 vtkExtractCTHPart is a filter that is specialized for creating 
 visualization of a CTH simulation.  First it converts the cell data
 to point data.  It contours the selected volume fraction at a value
 of 0.5.  The user has the option of clipping the part with a plane.
 Clipped surfaces of the part are generated.

To create an instance of class vtkExtractCTHPart, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkExtractCTHPart
\end{verbatim}
\subsection{Methods}

The class vtkExtractCTHPart has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkExtractCTHPart class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkExtractCTHPart = obj.NewInstance ()|

\item  \verb|vtkExtractCTHPart = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.RemoveDoubleVolumeArrayNames ()| -  Names of cell volume fraction arrays to extract.

\item  \verb|obj.RemoveFloatVolumeArrayNames ()| -  Names of cell volume fraction arrays to extract.

\item  \verb|obj.RemoveUnsignedCharVolumeArrayNames ()| -  Names of cell volume fraction arrays to extract.

\item  \verb|int = obj.GetNumberOfVolumeArrayNames ()| -  Names of cell volume fraction arrays to extract.

\item  \verb|string = obj.GetVolumeArrayName (int idx)| -  Names of cell volume fraction arrays to extract.

\item  \verb|obj.RemoveAllVolumeArrayNames ()| -  Names of cell volume fraction arrays to extract.
 for backwards compatibility

\item  \verb|obj.AddDoubleVolumeArrayName (string arrayName)|

\item  \verb|obj.AddFloatVolumeArrayName (string arrayName)|

\item  \verb|obj.AddUnsignedCharVolumeArrayName (string arrayName)|

\item  \verb|obj.AddVolumeArrayName (string arrayName)|

\item  \verb|obj.SetClipPlane (vtkPlane clipPlane)| -  Set, get or maninpulate the implicit clipping plane.

\item  \verb|vtkPlane = obj.GetClipPlane ()| -  Set, get or maninpulate the implicit clipping plane.

\item  \verb|long = obj.GetMTime ()| -  Look at clip plane to compute MTime.

\item  \verb|obj.SetController (vtkMultiProcessController controller)| -  Set the controller used to coordinate parallel processing.

\item  \verb|vtkMultiProcessController = obj.GetController ()| -  Return the controller used to coordinate parallel processing. By default,
 it is the global controller.

\item  \verb|obj.SetVolumeFractionSurfaceValue (double )| -  Set and get the volume fraction surface value. This value should be
 between 0 and 1

\item  \verb|double = obj.GetVolumeFractionSurfaceValueMinValue ()| -  Set and get the volume fraction surface value. This value should be
 between 0 and 1

\item  \verb|double = obj.GetVolumeFractionSurfaceValueMaxValue ()| -  Set and get the volume fraction surface value. This value should be
 between 0 and 1

\item  \verb|double = obj.GetVolumeFractionSurfaceValue ()| -  Set and get the volume fraction surface value. This value should be
 between 0 and 1

\end{itemize}
