\section{vtkInteractorStyleFlight}

\subsection{Usage}

 Left  mouse button press produces forward motion.
 Right mouse button press produces reverse motion.
 Moving mouse during motion steers user in desired direction.
 Keyboard controls are:
 Left/Right/Up/Down Arrows for steering direction
 'A' forward, 'Z' reverse motion
 Ctrl Key causes sidestep instead of steering in mouse and key modes
 Shift key is accelerator in mouse and key modes
 Ctrl and Shift together causes Roll in mouse and key modes

 By default, one ''step'' of motion corresponds to 1/250th of the diagonal
 of bounding box of visible actors, '+' and '-' keys allow user to
 increase or decrease step size.

To create an instance of class vtkInteractorStyleFlight, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkInteractorStyleFlight
\end{verbatim}
\subsection{Methods}

The class vtkInteractorStyleFlight has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkInteractorStyleFlight class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkInteractorStyleFlight = obj.NewInstance ()|

\item  \verb|vtkInteractorStyleFlight = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.JumpTo (double campos[3], double focpos[3])| -  Move the Eye/Camera to a specific location (no intermediate
 steps are taken

\item  \verb|obj.SetMotionStepSize (double )| -  Set the basic unit step size : by default 1/250 of bounding diagonal

\item  \verb|double = obj.GetMotionStepSize ()| -  Set the basic unit step size : by default 1/250 of bounding diagonal

\item  \verb|obj.SetMotionAccelerationFactor (double )| -  Set acceleration factor when shift key is applied : default 10

\item  \verb|double = obj.GetMotionAccelerationFactor ()| -  Set acceleration factor when shift key is applied : default 10

\item  \verb|obj.SetAngleStepSize (double )| -  Set the basic angular unit for turning : default 1 degree

\item  \verb|double = obj.GetAngleStepSize ()| -  Set the basic angular unit for turning : default 1 degree

\item  \verb|obj.SetAngleAccelerationFactor (double )| -  Set angular acceleration when shift key is applied : default 5

\item  \verb|double = obj.GetAngleAccelerationFactor ()| -  Set angular acceleration when shift key is applied : default 5

\item  \verb|obj.SetDisableMotion (int )| -  Disable motion (temporarily - for viewing etc)

\item  \verb|int = obj.GetDisableMotion ()| -  Disable motion (temporarily - for viewing etc)

\item  \verb|obj.DisableMotionOn ()| -  Disable motion (temporarily - for viewing etc)

\item  \verb|obj.DisableMotionOff ()| -  Disable motion (temporarily - for viewing etc)

\item  \verb|obj.SetRestoreUpVector (int )| -  When flying, apply a restorative force to the ''Up'' vector.
 This is activated when the current 'up' is close to the actual 'up'
 (as defined in DefaultUpVector). This prevents excessive twisting forces
 when viewing from arbitrary angles, but keep the horizon level when
 the user is flying over terrain.

\item  \verb|int = obj.GetRestoreUpVector ()| -  When flying, apply a restorative force to the ''Up'' vector.
 This is activated when the current 'up' is close to the actual 'up'
 (as defined in DefaultUpVector). This prevents excessive twisting forces
 when viewing from arbitrary angles, but keep the horizon level when
 the user is flying over terrain.

\item  \verb|obj.RestoreUpVectorOn ()| -  When flying, apply a restorative force to the ''Up'' vector.
 This is activated when the current 'up' is close to the actual 'up'
 (as defined in DefaultUpVector). This prevents excessive twisting forces
 when viewing from arbitrary angles, but keep the horizon level when
 the user is flying over terrain.

\item  \verb|obj.RestoreUpVectorOff ()| -  When flying, apply a restorative force to the ''Up'' vector.
 This is activated when the current 'up' is close to the actual 'up'
 (as defined in DefaultUpVector). This prevents excessive twisting forces
 when viewing from arbitrary angles, but keep the horizon level when
 the user is flying over terrain.

\item  \verb|double = obj. GetDefaultUpVector ()|

\item  \verb|obj.SetDefaultUpVector (double  [3])|

\item  \verb|obj.OnMouseMove ()| -  Concrete implementation of Mouse event bindings for flight

\item  \verb|obj.OnLeftButtonDown ()| -  Concrete implementation of Mouse event bindings for flight

\item  \verb|obj.OnLeftButtonUp ()| -  Concrete implementation of Mouse event bindings for flight

\item  \verb|obj.OnMiddleButtonDown ()| -  Concrete implementation of Mouse event bindings for flight

\item  \verb|obj.OnMiddleButtonUp ()| -  Concrete implementation of Mouse event bindings for flight

\item  \verb|obj.OnRightButtonDown ()| -  Concrete implementation of Mouse event bindings for flight

\item  \verb|obj.OnRightButtonUp ()| -  Concrete implementation of Mouse event bindings for flight

\item  \verb|obj.OnChar ()| -  Concrete implementation of Keyboard event bindings for flight

\item  \verb|obj.OnKeyDown ()| -  Concrete implementation of Keyboard event bindings for flight

\item  \verb|obj.OnKeyUp ()| -  Concrete implementation of Keyboard event bindings for flight

\item  \verb|obj.OnTimer ()| -  Concrete implementation of Keyboard event bindings for flight

\item  \verb|obj.ForwardFly ()| -  Concrete implementation of Keyboard event bindings for flight


\item  \verb|obj.ReverseFly ()| -  Concrete implementation of Keyboard event bindings for flight


\item  \verb|obj.StartForwardFly ()| -  Concrete implementation of Keyboard event bindings for flight



\item  \verb|obj.EndForwardFly ()| -  Concrete implementation of Keyboard event bindings for flight



\item  \verb|obj.StartReverseFly ()| -  Concrete implementation of Keyboard event bindings for flight



\item  \verb|obj.EndReverseFly ()| -  Concrete implementation of Keyboard event bindings for flight



\end{itemize}
