\section{vtkInteractorStyleJoystickActor}

\subsection{Usage}

 The class vtkInteractorStyleJoystickActor allows the user to interact
 with (rotate, zoom, etc.) separate objects in the scene independent of
 each other.  The position of the mouse relative to the center of the
 object determines the speed of the object's motion.  The mouse's velocity
 detemines the acceleration of the object's motion, so the object will
 continue moving even when the mouse is not moving.
 For a 3-button mouse, the left button is for rotation, the right button
 for zooming, the middle button for panning, and ctrl + left button for
 spinning.  (With fewer mouse buttons, ctrl + shift + left button is
 for zooming, and shift + left button is for panning.)

To create an instance of class vtkInteractorStyleJoystickActor, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkInteractorStyleJoystickActor
\end{verbatim}
\subsection{Methods}

The class vtkInteractorStyleJoystickActor has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkInteractorStyleJoystickActor class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkInteractorStyleJoystickActor = obj.NewInstance ()|

\item  \verb|vtkInteractorStyleJoystickActor = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.OnMouseMove ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnLeftButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnLeftButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnMiddleButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnMiddleButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnRightButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnRightButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.Rotate ()|

\item  \verb|obj.Spin ()|

\item  \verb|obj.Pan ()|

\item  \verb|obj.Dolly ()|

\item  \verb|obj.UniformScale ()|

\end{itemize}
