\section{vtkLabelHierarchyCompositeIterator}

\subsection{Usage}

 Iterates over child iterators in a round-robin order. Each iterator may
 have its own count, which is the number of times it is repeated until
 moving to the next iterator.
 
 For example, if you initialize the iterator with
 \begin{verbatim}
 it->AddIterator(A, 1);
 it->AddIterator(B, 3);
 \end{verbatim}
 The order of iterators will be A,B,B,B,A,B,B,B,...

To create an instance of class vtkLabelHierarchyCompositeIterator, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkLabelHierarchyCompositeIterator
\end{verbatim}
\subsection{Methods}

The class vtkLabelHierarchyCompositeIterator has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkLabelHierarchyCompositeIterator class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkLabelHierarchyCompositeIterator = obj.NewInstance ()|

\item  \verb|vtkLabelHierarchyCompositeIterator = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.AddIterator (vtkLabelHierarchyIterator it)| -  Adds a label iterator to this composite iterator.
 The second optional argument is the number of times to repeat the iterator
 before moving to the next one round-robin style. Default is 1.

\item  \verb|obj.AddIterator (vtkLabelHierarchyIterator it, int count)| -  Adds a label iterator to this composite iterator.
 The second optional argument is the number of times to repeat the iterator
 before moving to the next one round-robin style. Default is 1.

\item  \verb|obj.ClearIterators ()| -  Remove all iterators from this composite iterator.

\item  \verb|obj.Begin (vtkIdTypeArray )| -  Initializes the iterator. lastLabels is an array holding labels
 which should be traversed before any other labels in the hierarchy.
 This could include labels placed during a previous rendering or
 a label located under the mouse pointer. You may pass a null pointer.

\item  \verb|obj.Next ()| -  Advance the iterator.

\item  \verb|bool = obj.IsAtEnd ()| -  Returns true if the iterator is at the end.

\item  \verb|vtkIdType = obj.GetLabelId ()| -  Retrieves the current label id.

\item  \verb|vtkLabelHierarchy = obj.GetHierarchy ()| -  Retrieve the current label hierarchy.

\item  \verb|obj.BoxNode ()| -  Not implemented.

\item  \verb|obj.BoxAllNodes (vtkPolyData )|

\end{itemize}
