\section{vtkTexturedActor2D}

\subsection{Usage}

 vtkTexturedActor2D is an Actor2D which has additional support for
 textures, just like vtkActor. To use textures, the geometry must have
 texture coordinates, and the texture must be set with SetTexture().

To create an instance of class vtkTexturedActor2D, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkTexturedActor2D
\end{verbatim}
\subsection{Methods}

The class vtkTexturedActor2D has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkTexturedActor2D class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkTexturedActor2D = obj.NewInstance ()|

\item  \verb|vtkTexturedActor2D = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetTexture (vtkTexture texture)| -  Set/Get the texture object to control rendering texture maps.  This will
 be a vtkTexture object. An actor does not need to have an associated
 texture map and multiple actors can share one texture.

\item  \verb|vtkTexture = obj.GetTexture ()| -  Set/Get the texture object to control rendering texture maps.  This will
 be a vtkTexture object. An actor does not need to have an associated
 texture map and multiple actors can share one texture.

\item  \verb|obj.ReleaseGraphicsResources (vtkWindow win)| -  Release any graphics resources that are being consumed by this actor.
 The parameter window could be used to determine which graphic
 resources to release.

\item  \verb|int = obj.RenderOverlay (vtkViewport viewport)| -  Support the standard render methods.

\item  \verb|int = obj.RenderOpaqueGeometry (vtkViewport viewport)| -  Support the standard render methods.

\item  \verb|int = obj.RenderTranslucentPolygonalGeometry (vtkViewport viewport)| -  Support the standard render methods.

\item  \verb|long = obj.GetMTime ()| -  Return this object's modified time.

\item  \verb|obj.ShallowCopy (vtkProp prop)| -  Shallow copy of this vtkTexturedActor2D. Overrides vtkActor2D method.

\end{itemize}
