\section{vtkInteractorStyleSwitch}

\subsection{Usage}

 The class vtkInteractorStyleSwitch allows handles interactively switching
 between four interactor styles -- joystick actor, joystick camera,
 trackball actor, and trackball camera.  Type 'j' or 't' to select
 joystick or trackball, and type 'c' or 'a' to select camera or actor.
 The default interactor style is joystick camera.

To create an instance of class vtkInteractorStyleSwitch, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkInteractorStyleSwitch
\end{verbatim}
\subsection{Methods}

The class vtkInteractorStyleSwitch has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkInteractorStyleSwitch class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkInteractorStyleSwitch = obj.NewInstance ()|

\item  \verb|vtkInteractorStyleSwitch = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetInteractor (vtkRenderWindowInteractor iren)| -  The sub styles need the interactor too.

\item  \verb|obj.SetAutoAdjustCameraClippingRange (int value)| -  We must override this method in order to pass the setting down to
 the underlying styles

\item  \verb|vtkInteractorStyle = obj.GetCurrentStyle ()| -  Set/Get current style

\item  \verb|obj.SetCurrentStyleToJoystickActor ()| -  Set/Get current style

\item  \verb|obj.SetCurrentStyleToJoystickCamera ()| -  Set/Get current style

\item  \verb|obj.SetCurrentStyleToTrackballActor ()| -  Set/Get current style

\item  \verb|obj.SetCurrentStyleToTrackballCamera ()| -  Set/Get current style

\item  \verb|obj.OnChar ()| -  Only care about the char event, which is used to switch between
 different styles.

\item  \verb|obj.SetDefaultRenderer (vtkRenderer )| -  Overridden from vtkInteractorObserver because the interactor styles
 used by this class must also be updated.

\item  \verb|obj.SetCurrentRenderer (vtkRenderer )| -  Overridden from vtkInteractorObserver because the interactor styles
 used by this class must also be updated.

\end{itemize}
