\section{vtkViewTheme}

\subsection{Usage}

 This may be set on any subclass of vtkView.  The view class will attempt
 to use the values set in the theme to customize the view.  Views will not
 generally use every aspect of the theme.
 NOTICE: This class will be deprecated in favor of a more robust
 solution based on style sheets.  Do not become overly-dependent on the
 functionality of themes.

To create an instance of class vtkViewTheme, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkViewTheme
\end{verbatim}
\subsection{Methods}

The class vtkViewTheme has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkViewTheme class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkViewTheme = obj.NewInstance ()|

\item  \verb|vtkViewTheme = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetPointSize (double )| -  The size of points or vertices

\item  \verb|double = obj.GetPointSize ()| -  The size of points or vertices

\item  \verb|obj.SetLineWidth (double )| -  The width of lines or edges

\item  \verb|double = obj.GetLineWidth ()| -  The width of lines or edges

\item  \verb|obj.SetPointColor (double , double , double )| -  The color and opacity of points or vertices when not mapped through
 a lookup table.

\item  \verb|obj.SetPointColor (double  a[3])| -  The color and opacity of points or vertices when not mapped through
 a lookup table.

\item  \verb|double = obj. GetPointColor ()| -  The color and opacity of points or vertices when not mapped through
 a lookup table.

\item  \verb|obj.SetPointOpacity (double )| -  The color and opacity of points or vertices when not mapped through
 a lookup table.

\item  \verb|double = obj.GetPointOpacity ()| -  The color and opacity of points or vertices when not mapped through
 a lookup table.

\item  \verb|obj.SetPointHueRange (double mn, double mx)| -  The ranges to use in the point lookup table.
 You may also do this by accessing the point lookup table directly
 with GetPointLookupTable() and calling these methods.

\item  \verb|obj.SetPointHueRange (double rng[2])| -  The ranges to use in the point lookup table.
 You may also do this by accessing the point lookup table directly
 with GetPointLookupTable() and calling these methods.

\item  \verb|obj.GetPointHueRange (double rng[2])| -  The ranges to use in the point lookup table.
 You may also do this by accessing the point lookup table directly
 with GetPointLookupTable() and calling these methods.

\item  \verb|obj.SetPointSaturationRange (double mn, double mx)|

\item  \verb|obj.SetPointSaturationRange (double rng[2])|

\item  \verb|obj.GetPointSaturationRange (double rng[2])|

\item  \verb|obj.SetPointValueRange (double mn, double mx)|

\item  \verb|obj.SetPointValueRange (double rng[2])|

\item  \verb|obj.GetPointValueRange (double rng[2])|

\item  \verb|obj.SetPointAlphaRange (double mn, double mx)|

\item  \verb|obj.SetPointAlphaRange (double rng[2])|

\item  \verb|obj.GetPointAlphaRange (double rng[2])|

\item  \verb|vtkScalarsToColors = obj.GetPointLookupTable ()| -  Set/Get the point lookup table.

\item  \verb|obj.SetPointLookupTable (vtkScalarsToColors lut)| -  Set/Get the point lookup table.

\item  \verb|obj.SetScalePointLookupTable (bool )| -  Whether to scale the lookup table to fit the range of the data.

\item  \verb|bool = obj.GetScalePointLookupTable ()| -  Whether to scale the lookup table to fit the range of the data.

\item  \verb|obj.ScalePointLookupTableOn ()| -  Whether to scale the lookup table to fit the range of the data.

\item  \verb|obj.ScalePointLookupTableOff ()| -  Whether to scale the lookup table to fit the range of the data.

\item  \verb|obj.SetCellColor (double , double , double )| -  The color and opacity of cells or edges when not mapped through
 a lookup table.

\item  \verb|obj.SetCellColor (double  a[3])| -  The color and opacity of cells or edges when not mapped through
 a lookup table.

\item  \verb|double = obj. GetCellColor ()| -  The color and opacity of cells or edges when not mapped through
 a lookup table.

\item  \verb|obj.SetCellOpacity (double )| -  The color and opacity of cells or edges when not mapped through
 a lookup table.

\item  \verb|double = obj.GetCellOpacity ()| -  The color and opacity of cells or edges when not mapped through
 a lookup table.

\item  \verb|obj.SetCellHueRange (double mn, double mx)| -  The ranges to use in the cell lookup table.
 You may also do this by accessing the cell lookup table directly
 with GetCellLookupTable() and calling these methods.

\item  \verb|obj.SetCellHueRange (double rng[2])| -  The ranges to use in the cell lookup table.
 You may also do this by accessing the cell lookup table directly
 with GetCellLookupTable() and calling these methods.

\item  \verb|obj.GetCellHueRange (double rng[2])| -  The ranges to use in the cell lookup table.
 You may also do this by accessing the cell lookup table directly
 with GetCellLookupTable() and calling these methods.

\item  \verb|obj.SetCellSaturationRange (double mn, double mx)|

\item  \verb|obj.SetCellSaturationRange (double rng[2])|

\item  \verb|obj.GetCellSaturationRange (double rng[2])|

\item  \verb|obj.SetCellValueRange (double mn, double mx)|

\item  \verb|obj.SetCellValueRange (double rng[2])|

\item  \verb|obj.GetCellValueRange (double rng[2])|

\item  \verb|obj.SetCellAlphaRange (double mn, double mx)|

\item  \verb|obj.SetCellAlphaRange (double rng[2])|

\item  \verb|obj.GetCellAlphaRange (double rng[2])|

\item  \verb|vtkScalarsToColors = obj.GetCellLookupTable ()| -  Set/Get the cell lookup table.

\item  \verb|obj.SetCellLookupTable (vtkScalarsToColors lut)| -  Set/Get the cell lookup table.

\item  \verb|obj.SetScaleCellLookupTable (bool )| -  Whether to scale the lookup table to fit the range of the data.

\item  \verb|bool = obj.GetScaleCellLookupTable ()| -  Whether to scale the lookup table to fit the range of the data.

\item  \verb|obj.ScaleCellLookupTableOn ()| -  Whether to scale the lookup table to fit the range of the data.

\item  \verb|obj.ScaleCellLookupTableOff ()| -  Whether to scale the lookup table to fit the range of the data.

\item  \verb|obj.SetOutlineColor (double , double , double )| -  The color of any outlines in the view.

\item  \verb|obj.SetOutlineColor (double  a[3])| -  The color of any outlines in the view.

\item  \verb|double = obj. GetOutlineColor ()| -  The color of any outlines in the view.

\item  \verb|obj.SetSelectedPointColor (double , double , double )| -  The color of selected points or vertices.

\item  \verb|obj.SetSelectedPointColor (double  a[3])| -  The color of selected points or vertices.

\item  \verb|double = obj. GetSelectedPointColor ()| -  The color of selected points or vertices.

\item  \verb|obj.SetSelectedPointOpacity (double )| -  The color of selected points or vertices.

\item  \verb|double = obj.GetSelectedPointOpacity ()| -  The color of selected points or vertices.

\item  \verb|obj.SetSelectedCellColor (double , double , double )| -  The color of selected cells or edges.

\item  \verb|obj.SetSelectedCellColor (double  a[3])| -  The color of selected cells or edges.

\item  \verb|double = obj. GetSelectedCellColor ()| -  The color of selected cells or edges.

\item  \verb|obj.SetSelectedCellOpacity (double )| -  The color of selected cells or edges.

\item  \verb|double = obj.GetSelectedCellOpacity ()| -  The color of selected cells or edges.

\item  \verb|obj.SetBackgroundColor (double , double , double )| -  The view background color.

\item  \verb|obj.SetBackgroundColor (double  a[3])| -  The view background color.

\item  \verb|double = obj. GetBackgroundColor ()| -  The view background color.

\item  \verb|obj.SetBackgroundColor2 (double , double , double )| -  The second background color (for gradients).

\item  \verb|obj.SetBackgroundColor2 (double  a[3])| -  The second background color (for gradients).

\item  \verb|double = obj. GetBackgroundColor2 ()| -  The second background color (for gradients).

\item  \verb|obj.SetPointTextProperty (vtkTextProperty tprop)| -  The text property to use for labelling points/vertices.

\item  \verb|vtkTextProperty = obj.GetPointTextProperty ()| -  The text property to use for labelling points/vertices.

\item  \verb|obj.SetCellTextProperty (vtkTextProperty tprop)| -  The text property to use for labelling edges/cells.

\item  \verb|vtkTextProperty = obj.GetCellTextProperty ()| -  The text property to use for labelling edges/cells.

\item  \verb|obj.SetVertexLabelColor (double r, double g, double b)| -  The color to use for labelling graph vertices.
 This is deprecated. Use GetPointTextProperty()->SetColor() instead.

\item  \verb|obj.SetVertexLabelColor (double c[3])| -  The color to use for labelling graph vertices.
 This is deprecated. Use GetPointTextProperty()->SetColor() instead.

\item  \verb|obj.GetVertexLabelColor (double c[3])| -  The color to use for labelling graph edges.
 This is deprecated. Use GetCellTextProperty()->SetColor() instead.

\item  \verb|obj.SetEdgeLabelColor (double r, double g, double b)| -  The color to use for labelling graph edges.
 This is deprecated. Use GetCellTextProperty()->SetColor() instead.

\item  \verb|obj.SetEdgeLabelColor (double c[3])| -  The color to use for labelling graph edges.
 This is deprecated. Use GetCellTextProperty()->SetColor() instead.

\item  \verb|obj.GetEdgeLabelColor (double c[3])| -  Convenience methods for creating some default view themes.
 The return reference is reference-counted, so you will have to call
 Delete() on the reference when you are finished with it.

\item  \verb|bool = obj.LookupMatchesPointTheme (vtkScalarsToColors s2c)| -  Whether a given lookup table matches the point or cell theme of this
 theme.

\item  \verb|bool = obj.LookupMatchesCellTheme (vtkScalarsToColors s2c)| -  Whether a given lookup table matches the point or cell theme of this
 theme.

\end{itemize}
