\section{vtkActorCollection}

\subsection{Usage}

 vtkActorCollection represents and provides methods to manipulate a list of
 actors (i.e., vtkActor and subclasses). The list is unsorted and duplicate
 entries are not prevented.

To create an instance of class vtkActorCollection, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkActorCollection
\end{verbatim}
\subsection{Methods}

The class vtkActorCollection has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkActorCollection class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkActorCollection = obj.NewInstance ()|

\item  \verb|vtkActorCollection = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.AddItem (vtkActor a)| -  Add an actor to the list.

\item  \verb|vtkActor = obj.GetNextActor ()| -  Get the next actor in the list.

\item  \verb|vtkActor = obj.GetLastActor ()| -  Get the last actor in the list.

\item  \verb|vtkActor = obj.GetNextItem ()| -  Access routines that are provided for compatibility with previous
 version of VTK.  Please use the GetNextActor(), GetLastActor() variants
 where possible.

\item  \verb|vtkActor = obj.GetLastItem ()| -  Access routines that are provided for compatibility with previous
 version of VTK.  Please use the GetNextActor(), GetLastActor() variants
 where possible.

\item  \verb|obj.ApplyProperties (vtkProperty p)| -  Apply properties to all actors in this collection.

\end{itemize}
