\section{vtkShader}

\subsection{Usage}

 vtkShader is a base class for interfacing VTK to hardware shader
 libraries. vtkShader interprets a vtkXMLDataElement that describes a
 particular shader. Descendants of this class inherit this functionality and
 additionally interface to specific shader libraries like NVidia's Cg and
 OpenGL2.0 (GLSL) to perform operations, on individual shaders.
 
 During each render, the vtkShaderProgram calls Compile(),
 PassShaderVariables(), Bind() and after the actor has been rendered,
 calls Unbind(), in that order.

To create an instance of class vtkShader, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkShader
\end{verbatim}
\subsection{Methods}

The class vtkShader has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkShader class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkShader = obj.NewInstance ()|

\item  \verb|vtkShader = obj.SafeDownCast (vtkObject o)|

\item  \verb|int = obj.Compile ()| -  Called to compile the shader code.
 The subclasses must only compile the code in this method.
 Returns if the compile was successful.
 Subclasses should compile the code only if it was not
 already compiled.

\item  \verb|obj.PassShaderVariables (vtkActor actor, vtkRenderer ren)| -  Called to pass VTK actor/property/light values and other
 Shader variables over to the shader. This is called by the ShaderProgram
 during each render.

\item  \verb|obj.Bind ()| -  Called to unbind the shader. As with Bind(), this is only applicable
 to Cg.

\item  \verb|obj.Unbind ()| -  Release any graphics resources that are being consumed by this actor.
 The parameter window could be used to determine which graphic
 resources to release.

\item  \verb|obj.ReleaseGraphicsResources (vtkWindow )| -  Get/Set the XMLShader representation for this shader.
 A shader is not valid without a XMLShader.

\item  \verb|obj.SetXMLShader (vtkXMLShader )| -  Get/Set the XMLShader representation for this shader.
 A shader is not valid without a XMLShader.

\item  \verb|vtkXMLShader = obj.GetXMLShader ()| -  Get/Set the XMLShader representation for this shader.
 A shader is not valid without a XMLShader.

\item  \verb|int = obj.HasShaderVariable (string name)| -  Indicates if a variable by the given name exists.

\item  \verb|obj.AddShaderVariable (string name, int num\_of\_elements, int values)| -  Methods to add shader variables to this shader.
 The shader variable type must match with that declared in
 the Material xml, otherwise, the variable is not made available 
 to the shader.

\item  \verb|obj.AddShaderVariable (string name, int num\_of\_elements, float values)| -  Methods to add shader variables to this shader.
 The shader variable type must match with that declared in
 the Material xml, otherwise, the variable is not made available 
 to the shader.

\item  \verb|obj.AddShaderVariable (string name, int num\_of\_elements, double values)| -  Methods to add shader variables to this shader.
 The shader variable type must match with that declared in
 the Material xml, otherwise, the variable is not made available 
 to the shader.

\item  \verb|int = obj.GetShaderVariableSize (string name)| -  Get number of elements in a Shader variable. Return 0 if
 failed to find the shader variable.

\item  \verb|int = obj.GetShaderVariableType (string name)| -  Returns the type of a Shader variable with the given name.
 Return 0 on error.

\item  \verb|int = obj.GetShaderVariable (string name, int values)| -  Methods to get the value of shader variables with the given name.
 Values must be at least the size of the shader variable (obtained
 by GetShaderVariableSize(). Returns if the operation was successful.

\item  \verb|int = obj.GetShaderVariable (string name, float values)| -  Methods to get the value of shader variables with the given name.
 Values must be at least the size of the shader variable (obtained
 by GetShaderVariableSize(). Returns if the operation was successful.

\item  \verb|int = obj.GetShaderVariable (string name, double values)| -  Methods to get the value of shader variables with the given name.
 Values must be at least the size of the shader variable (obtained
 by GetShaderVariableSize(). Returns if the operation was successful.

\item  \verb|int = obj.GetScope ()| -  Returns the scope of the shader i.e. if it's a vertex or fragment shader.
 (vtkXMLShader::SCOPE\_VERTEX or vtkXMLShader::SCOPE\_FRAGMENT).

\end{itemize}
