\section{vtkFollower}

\subsection{Usage}

 vtkFollower is a subclass of vtkActor that always follows its specified 
 camera. More specifically it will not change its position or scale,
 but it will continually update its orientation so that it is right side
 up and facing the camera. This is typically used for text labels in a
 scene. All of the adjustments that can be made to an actor also will
 take effect with a follower.  So, if you change the orientation of the
 follower by 90 degrees, then it will follow the camera, but be off by 
 90 degrees.

To create an instance of class vtkFollower, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkFollower
\end{verbatim}
\subsection{Methods}

The class vtkFollower has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkFollower class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkFollower = obj.NewInstance ()|

\item  \verb|vtkFollower = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetCamera (vtkCamera )| -  Set/Get the camera to follow. If this is not set, then the follower
 won't know who to follow.

\item  \verb|vtkCamera = obj.GetCamera ()| -  Set/Get the camera to follow. If this is not set, then the follower
 won't know who to follow.

\item  \verb|int = obj.RenderOpaqueGeometry (vtkViewport viewport)| -  This causes the actor to be rendered. It in turn will render the actor's
 property, texture map and then mapper. If a property hasn't been
 assigned, then the actor will create one automatically. 

\item  \verb|int = obj.RenderTranslucentPolygonalGeometry (vtkViewport viewport)| -  This causes the actor to be rendered. It in turn will render the actor's
 property, texture map and then mapper. If a property hasn't been
 assigned, then the actor will create one automatically. 

\item  \verb|obj.Render (vtkRenderer ren)| -  This causes the actor to be rendered. It in turn will render the actor's
 property, texture map and then mapper. If a property hasn't been
 assigned, then the actor will create one automatically. 

\item  \verb|int = obj.HasTranslucentPolygonalGeometry ()| -  Does this prop have some translucent polygonal geometry?

\item  \verb|obj.GetMatrix (vtkMatrix4x4 m)| -  Copy the follower's composite 4x4 matrix into the matrix provided.

\item  \verb|obj.GetMatrix (double m[16])| -  Copy the follower's composite 4x4 matrix into the matrix provided.

\item  \verb|vtkMatrix4x4 = obj.GetMatrix ()| -  Shallow copy of a follower. Overloads the virtual vtkProp method.

\item  \verb|obj.ShallowCopy (vtkProp prop)| -  Shallow copy of a follower. Overloads the virtual vtkProp method.

\end{itemize}
