\section{vtkParallelCoordinatesInteractorStyle}

\subsection{Usage}

 vtkParallelCoordinatesInteractorStyle allows the user to interactively manipulate
 (rotate, pan, zoomm etc.) the camera.
 Several events are overloaded from its superclass
 vtkParallelCoordinatesInteractorStyle, hence the mouse bindings are 
 different. (The bindings
 keep the camera's view plane normal perpendicular to the x-y plane.) In
 summary the mouse events are as follows:
 + Left Mouse button triggers window level events
 + CTRL Left Mouse spins the camera around its view plane normal
 + SHIFT Left Mouse pans the camera
 + CTRL SHIFT Left Mouse dollys (a positional zoom) the camera
 + Middle mouse button pans the camera
 + Right mouse button dollys the camera.
 + SHIFT Right Mouse triggers pick events

 Note that the renderer's actors are not moved; instead the camera is moved.

To create an instance of class vtkParallelCoordinatesInteractorStyle, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkParallelCoordinatesInteractorStyle
\end{verbatim}
\subsection{Methods}

The class vtkParallelCoordinatesInteractorStyle has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkParallelCoordinatesInteractorStyle class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkParallelCoordinatesInteractorStyle = obj.NewInstance ()|

\item  \verb|vtkParallelCoordinatesInteractorStyle = obj.SafeDownCast (vtkObject o)|

\item  \verb|int = obj. GetCursorStartPosition ()| -  Get the cursor positions in pixel coords

\item  \verb|int = obj. GetCursorCurrentPosition ()| -  Get the cursor positions in pixel coords

\item  \verb|int = obj. GetCursorLastPosition ()| -  Get the cursor positions in pixel coords

\item  \verb|obj.GetCursorStartPosition (vtkViewport viewport, double pos[2])| -  Get the cursor positions in a given coordinate system

\item  \verb|obj.GetCursorCurrentPosition (vtkViewport viewport, double pos[2])| -  Get the cursor positions in a given coordinate system

\item  \verb|obj.GetCursorLastPosition (vtkViewport viewport, double pos[2])| -  Get the cursor positions in a given coordinate system

\item  \verb|obj.OnMouseMove ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnLeftButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnLeftButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnMiddleButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnMiddleButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnRightButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnRightButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnLeave ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.StartInspect (int x, int y)|

\item  \verb|obj.Inspect (int x, int y)|

\item  \verb|obj.EndInspect ()|

\item  \verb|obj.StartZoom ()|

\item  \verb|obj.Zoom ()|

\item  \verb|obj.EndZoom ()|

\item  \verb|obj.StartPan ()|

\item  \verb|obj.Pan ()|

\item  \verb|obj.EndPan ()|

\item  \verb|obj.OnChar ()| -  Override the ''fly-to'' (f keypress) for images.

\end{itemize}
