\section{vtkPainter}

\subsection{Usage}

 This defines the interface for a Painter. Painters are helpers used
 by Mapper to perform the rendering. The mapper sets up a chain of painters
 and passes the render request to the painter. Every painter may have a 
 delegate painter to which the render request is forwarded. The Painter may
 modify the request or data before passing it to the delegate painter. 
 All the information to control the rendering must be passed to the painter
 using the vtkInformation object. A concrete painter may read special keys
 from the vtkInformation object and affect the rendering.


To create an instance of class vtkPainter, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkPainter
\end{verbatim}
\subsection{Methods}

The class vtkPainter has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkPainter class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkPainter = obj.NewInstance ()|

\item  \verb|vtkPainter = obj.SafeDownCast (vtkObject o)|

\item  \verb|vtkInformation = obj.GetInformation ()| -  Get/Set the information object associated with this painter.

\item  \verb|obj.SetInformation (vtkInformation )| -  Get/Set the information object associated with this painter.

\item  \verb|vtkPainter = obj.GetDelegatePainter ()| -  Set/Get the painter to which this painter should propagare its draw calls.

\item  \verb|obj.SetDelegatePainter (vtkPainter )| -  Set/Get the painter to which this painter should propagare its draw calls.

\item  \verb|obj.Register (vtkObjectBase o)| -  Take part in garbage collection.

\item  \verb|obj.UnRegister (vtkObjectBase o)| -  Take part in garbage collection.

\item  \verb|obj.Render (vtkRenderer renderer, vtkActor actor, long typeflags, bool forceCompileOnly)| -  Generates rendering primitives of appropriate type(s). Multiple types 
 of primitives can be requested by or-ring the primitive flags. 
 Default implementation calls UpdateDelegatePainter() to update the 
 deletagate painter and then calls RenderInternal().
 forceCompileOnly is passed to the display list painters.

\item  \verb|obj.ReleaseGraphicsResources (vtkWindow )| -  Release any graphics resources that are being consumed by this painter.
 The parameter window could be used to determine which graphic
 resources to release. 
 The call is propagated to the delegate painter, if any.

\item  \verb|obj.SetProgress (double )| -  Set/Get the execution progress of a process object.

\item  \verb|double = obj.GetProgressMinValue ()| -  Set/Get the execution progress of a process object.

\item  \verb|double = obj.GetProgressMaxValue ()| -  Set/Get the execution progress of a process object.

\item  \verb|double = obj.GetProgress ()| -  Set/Get the execution progress of a process object.

\item  \verb|double = obj.GetTimeToDraw ()| -  Get the time required to draw the geometry last time it was rendered.
 Default implementation adds the current TimeToDraw with that of the
 delegate painter.

\item  \verb|obj.UpdateBounds (double bounds[6])| -  Expand or shrink the estimated bounds of the object based on the
 geometric transformations performed in the painter. If the painter
 does not modify the geometry, the bounds are passed through.

\item  \verb|obj.SetInput (vtkDataObject )| -  Set the data object to paint. Currently we only support one data object per
 painter chain.

\item  \verb|vtkDataObject = obj.GetInput ()| -  Set the data object to paint. Currently we only support one data object per
 painter chain.

\item  \verb|vtkDataObject = obj.GetOutput ()|

\end{itemize}
