\section{vtkLabelSizeCalculator}

\subsection{Usage}

 This filter takes an input dataset, an array to process
 (which must be a string array), and a text property.
 It creates a new output array (named ''LabelSize'' by default) with
 4 components per tuple that contain the width, height, horizontal
 offset, and descender height (in that order) of each string in
 the array.

 Use the inherited SelectInputArrayToProcess to indicate a string array.
 In no input array is specified, the first of the following that
 is a string array is used: point scalars, cell scalars, field scalars.

 The second input array to process is an array specifying the type of
 each label. Different label types may have different font properties.
 This array must be a vtkIntArray.
 Any type that does not map to a font property that was set will
 be set to the type 0's type property.

To create an instance of class vtkLabelSizeCalculator, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkLabelSizeCalculator
\end{verbatim}
\subsection{Methods}

The class vtkLabelSizeCalculator has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkLabelSizeCalculator class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkLabelSizeCalculator = obj.NewInstance ()|

\item  \verb|vtkLabelSizeCalculator = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetFontProperty (vtkTextProperty fontProp, int type)| -  Get/Set the font used compute label sizes.
 This defaults to ''Arial'' at 12 points.
 If type is provided, it refers to the type of the text label provided
 in the optional label type array. The default type is type 0.

\item  \verb|vtkTextProperty = obj.GetFontProperty (int type)| -  Get/Set the font used compute label sizes.
 This defaults to ''Arial'' at 12 points.
 If type is provided, it refers to the type of the text label provided
 in the optional label type array. The default type is type 0.

\item  \verb|obj.SetLabelSizeArrayName (string )| -  The name of the output array containing text label sizes
 This defaults to ''LabelSize''

\item  \verb|string = obj.GetLabelSizeArrayName ()| -  The name of the output array containing text label sizes
 This defaults to ''LabelSize''

\end{itemize}
