\section{vtkInteractorStyleTrackballCamera}

\subsection{Usage}

 vtkInteractorStyleTrackballCamera allows the user to interactively
 manipulate (rotate, pan, etc.) the camera, the viewpoint of the scene.  In
 trackball interaction, the magnitude of the mouse motion is proportional
 to the camera motion associated with a particular mouse binding. For
 example, small left-button motions cause small changes in the rotation of
 the camera around its focal point. For a 3-button mouse, the left button
 is for rotation, the right button for zooming, the middle button for
 panning, and ctrl + left button for spinning.  (With fewer mouse buttons,
 ctrl + shift + left button is for zooming, and shift + left button is for
 panning.)

To create an instance of class vtkInteractorStyleTrackballCamera, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkInteractorStyleTrackballCamera
\end{verbatim}
\subsection{Methods}

The class vtkInteractorStyleTrackballCamera has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkInteractorStyleTrackballCamera class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkInteractorStyleTrackballCamera = obj.NewInstance ()|

\item  \verb|vtkInteractorStyleTrackballCamera = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.OnMouseMove ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnLeftButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnLeftButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnMiddleButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnMiddleButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnRightButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnRightButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnMouseWheelForward ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnMouseWheelBackward ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.Rotate ()|

\item  \verb|obj.Spin ()|

\item  \verb|obj.Pan ()|

\item  \verb|obj.Dolly ()|

\item  \verb|obj.SetMotionFactor (double )| -  Set the apparent sensitivity of the interactor style to mouse motion.

\item  \verb|double = obj.GetMotionFactor ()| -  Set the apparent sensitivity of the interactor style to mouse motion.

\end{itemize}
