\section{vtkInteractorStyleTrackballActor}

\subsection{Usage}

 vtkInteractorStyleTrackballActor allows the user to interact with (rotate,
 pan, etc.) objects in the scene indendent of each other.  In trackball
 interaction, the magnitude of the mouse motion is proportional to the
 actor motion associated with a particular mouse binding. For example,
 small left-button motions cause small changes in the rotation of the
 actor around its center point.

 The mouse bindings are as follows. For a 3-button mouse, the left button
 is for rotation, the right button for zooming, the middle button for
 panning, and ctrl + left button for spinning.  (With fewer mouse buttons,
 ctrl + shift + left button is for zooming, and shift + left button is for
 panning.)

To create an instance of class vtkInteractorStyleTrackballActor, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkInteractorStyleTrackballActor
\end{verbatim}
\subsection{Methods}

The class vtkInteractorStyleTrackballActor has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkInteractorStyleTrackballActor class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkInteractorStyleTrackballActor = obj.NewInstance ()|

\item  \verb|vtkInteractorStyleTrackballActor = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.OnMouseMove ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnLeftButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnLeftButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnMiddleButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnMiddleButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnRightButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnRightButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.Rotate ()|

\item  \verb|obj.Spin ()|

\item  \verb|obj.Pan ()|

\item  \verb|obj.Dolly ()|

\item  \verb|obj.UniformScale ()|

\end{itemize}
