\section{vtkGaussianBlurPass}

\subsection{Usage}

 Blur the image renderered by its delegate. Blurring uses a Gaussian low-pass
 filter with a 5x5 kernel.

 This pass expects an initialized depth buffer and color buffer.
 Initialized buffers means they have been cleared with farest z-value and
 background color/gradient/transparent color.
 An opaque pass may have been performed right after the initialization.

 The delegate is used once.

 Its delegate is usually set to a vtkCameraPass or to a post-processing pass.
 
 This pass requires a OpenGL context that supports texture objects (TO),
 framebuffer objects (FBO) and GLSL. If not, it will emit an error message
 and will render its delegate and return.

 .SECTION Implementation
 As the filter is separable, it first blurs the image horizontally and then
 vertically. This reduces the number of texture sampling to 5 per pass.
 In addition, as texture sampling can already blend texel values in linear
 mode, by adjusting the texture coordinate accordingly, only 3 texture
 sampling are actually necessary.
 Reference: OpenGL Bloom Toturial by Philip Rideout, section
 Exploit Hardware Filtering  http://prideout.net/bloom/index.php\#Sneaky

To create an instance of class vtkGaussianBlurPass, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkGaussianBlurPass
\end{verbatim}
\subsection{Methods}

The class vtkGaussianBlurPass has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkGaussianBlurPass class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkGaussianBlurPass = obj.NewInstance ()|

\item  \verb|vtkGaussianBlurPass = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.ReleaseGraphicsResources (vtkWindow w)| -  Release graphics resources and ask components to release their own
 resources.
 

\end{itemize}
