\section{vtkInteractorStyleRubberBand2D}

\subsection{Usage}

 vtkInteractorStyleRubberBand2D manages interaction in a 2D view.
 Camera rotation is not allowed with this interactor style.
 The style also allows draws a rubber band using the left button.
 All camera changes invoke InteractionBeginEvent when the button
 is pressed, InteractionEvent when the mouse (or wheel) is moved,
 and InteractionEndEvent when the button is released.  The bindings
 are as follows:
 Left mouse - Select (invokes a SelectionChangedEvent).
 Right mouse - Zoom.
 Middle mouse - Pan.
 Scroll wheel - Zoom.

To create an instance of class vtkInteractorStyleRubberBand2D, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkInteractorStyleRubberBand2D
\end{verbatim}
\subsection{Methods}

The class vtkInteractorStyleRubberBand2D has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkInteractorStyleRubberBand2D class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkInteractorStyleRubberBand2D = obj.NewInstance ()|

\item  \verb|vtkInteractorStyleRubberBand2D = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.OnLeftButtonDown ()|

\item  \verb|obj.OnLeftButtonUp ()|

\item  \verb|obj.OnMiddleButtonDown ()|

\item  \verb|obj.OnMiddleButtonUp ()|

\item  \verb|obj.OnRightButtonDown ()|

\item  \verb|obj.OnRightButtonUp ()|

\item  \verb|obj.OnMouseMove ()|

\item  \verb|obj.OnMouseWheelForward ()|

\item  \verb|obj.OnMouseWheelBackward ()|

\item  \verb|obj.SetRenderOnMouseMove (bool )| -  Whether to invoke a render when the mouse moves.

\item  \verb|bool = obj.GetRenderOnMouseMove ()| -  Whether to invoke a render when the mouse moves.

\item  \verb|obj.RenderOnMouseMoveOn ()| -  Whether to invoke a render when the mouse moves.

\item  \verb|obj.RenderOnMouseMoveOff ()| -  Whether to invoke a render when the mouse moves.

\item  \verb|int = obj.GetInteraction ()| -  Current interaction state

\end{itemize}
