\section{vtkInteractorStyleTerrain}

\subsection{Usage}

 vtkInteractorStyleTerrain is used to manipulate a camera which is viewing
 a scene with a natural view up, e.g., terrain. The camera in such a
 scene is manipulated by specifying azimuth (angle around the view
 up vector) and elevation (the angle from the horizon).

 The mouse binding for this class is as follows. Left mouse click followed
 rotates the camera around the focal point using both elevation and azimuth
 invocations on the camera. Left mouse motion in the horizontal direction
 results in azimuth motion; left mouse motion in the vertical direction
 results in elevation motion. Therefore, diagonal motion results in a
 combination of azimuth and elevation. (If the shift key is held during
 motion, then only one of elevation or azimuth is invoked, depending on the
 whether the mouse motion is primarily horizontal or vertical.) Middle
 mouse button pans the camera across the scene (again the shift key has a
 similar effect on limiting the motion to the vertical or horizontal
 direction. The right mouse is used to dolly (e.g., a type of zoom) towards
 or away from the focal point.

 The class also supports some keypress events. The ''r'' key resets the
 camera.  The ''e'' key invokes the exit callback and by default exits the
 program. The ''f'' key sets a new camera focal point and flys towards that
 point. The ''u'' key invokes the user event. The ''3'' key toggles between 
 stereo and non-stero mode. The ''l'' key toggles on/off a latitude/longitude
 markers that can be used to estimate/control position.
 

To create an instance of class vtkInteractorStyleTerrain, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkInteractorStyleTerrain
\end{verbatim}
\subsection{Methods}

The class vtkInteractorStyleTerrain has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkInteractorStyleTerrain class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkInteractorStyleTerrain = obj.NewInstance ()|

\item  \verb|vtkInteractorStyleTerrain = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.OnMouseMove ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnLeftButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnLeftButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnMiddleButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnMiddleButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnRightButtonDown ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnRightButtonUp ()| -  Event bindings controlling the effects of pressing mouse buttons
 or moving the mouse.

\item  \verb|obj.OnChar ()| -  Override the ''fly-to'' (f keypress) for images.

\item  \verb|obj.Rotate ()|

\item  \verb|obj.Pan ()|

\item  \verb|obj.Dolly ()|

\item  \verb|obj.SetLatLongLines (int )| -  Turn on/off the latitude/longitude lines.

\item  \verb|int = obj.GetLatLongLines ()| -  Turn on/off the latitude/longitude lines.

\item  \verb|obj.LatLongLinesOn ()| -  Turn on/off the latitude/longitude lines.

\item  \verb|obj.LatLongLinesOff ()| -  Turn on/off the latitude/longitude lines.

\end{itemize}
