\section{vtkHierarchicalGraphView}

\subsection{Usage}

 Takes a graph and a hierarchy (currently a tree) and lays out the graph 
 vertices based on their categorization within the hierarchy.

 .SEE ALSO
 vtkGraphLayoutView

 .SECTION Thanks
 Thanks to the turtle with jets for feet, without you this class wouldn't 
 have been possible.

To create an instance of class vtkHierarchicalGraphView, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkHierarchicalGraphView
\end{verbatim}
\subsection{Methods}

The class vtkHierarchicalGraphView has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkHierarchicalGraphView class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkHierarchicalGraphView = obj.NewInstance ()|

\item  \verb|vtkHierarchicalGraphView = obj.SafeDownCast (vtkObject o)|

\item  \verb|vtkDataRepresentation = obj.SetHierarchyFromInputConnection (vtkAlgorithmOutput conn)| -  Set the tree and graph representations to the appropriate input ports.

\item  \verb|vtkDataRepresentation = obj.SetHierarchyFromInput (vtkDataObject input)| -  Set the tree and graph representations to the appropriate input ports.

\item  \verb|vtkDataRepresentation = obj.SetGraphFromInputConnection (vtkAlgorithmOutput conn)| -  Set the tree and graph representations to the appropriate input ports.

\item  \verb|vtkDataRepresentation = obj.SetGraphFromInput (vtkDataObject input)| -  Set the tree and graph representations to the appropriate input ports.

\item  \verb|obj.SetGraphEdgeLabelArrayName (string name)| -  The array to use for edge labeling.  Default is ''label''.

\item  \verb|string = obj.GetGraphEdgeLabelArrayName ()| -  The array to use for edge labeling.  Default is ''label''.

\item  \verb|obj.SetGraphEdgeLabelVisibility (bool vis)| -  Whether to show edge labels.  Default is off.

\item  \verb|bool = obj.GetGraphEdgeLabelVisibility ()| -  Whether to show edge labels.  Default is off.

\item  \verb|obj.GraphEdgeLabelVisibilityOn ()| -  Whether to show edge labels.  Default is off.

\item  \verb|obj.GraphEdgeLabelVisibilityOff ()| -  Whether to show edge labels.  Default is off.

\item  \verb|obj.SetGraphEdgeColorArrayName (string name)| -  The array to use for coloring edges.  Default is ''color''.

\item  \verb|string = obj.GetGraphEdgeColorArrayName ()| -  The array to use for coloring edges.  Default is ''color''.

\item  \verb|obj.SetGraphEdgeColorToSplineFraction ()| -  Set the color to be the spline fraction

\item  \verb|obj.SetColorGraphEdgesByArray (bool vis)| -  Whether to color edges.  Default is off.

\item  \verb|bool = obj.GetColorGraphEdgesByArray ()| -  Whether to color edges.  Default is off.

\item  \verb|obj.ColorGraphEdgesByArrayOn ()| -  Whether to color edges.  Default is off.

\item  \verb|obj.ColorGraphEdgesByArrayOff ()| -  Whether to color edges.  Default is off.

\item  \verb|obj.SetBundlingStrength (double strength)| -  Set the bundling strength.

\item  \verb|double = obj.GetBundlingStrength ()| -  Set the bundling strength.

\item  \verb|obj.SetGraphVisibility (bool b)| -  Whether the graph edges are visible (default off).

\item  \verb|bool = obj.GetGraphVisibility ()| -  Whether the graph edges are visible (default off).

\item  \verb|obj.GraphVisibilityOn ()| -  Whether the graph edges are visible (default off).

\item  \verb|obj.GraphVisibilityOff ()| -  Whether the graph edges are visible (default off).

\item  \verb|obj.SetGraphEdgeLabelFontSize (int size)| -  The size of the font used for edge labeling

\item  \verb|int = obj.GetGraphEdgeLabelFontSize ()| -  The size of the font used for edge labeling

\end{itemize}
