\section{vtkUnstructuredGridPartialPreIntegration}

\subsection{Usage}


 vtkUnstructuredGridPartialPreIntegration performs piecewise linear ray
 integration.  This will give the same results as
 vtkUnstructuredGridLinearRayIntegration (with potentially a error due to
 table lookup quantization), but should be notably faster.  The algorithm
 used is given by Moreland and Angel, ''A Fast High Accuracy Volume
 Renderer for Unstructured Data.''

 This class is thread safe only after the first instance is created.


To create an instance of class vtkUnstructuredGridPartialPreIntegration, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkUnstructuredGridPartialPreIntegration
\end{verbatim}
\subsection{Methods}

The class vtkUnstructuredGridPartialPreIntegration has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkUnstructuredGridPartialPreIntegration class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkUnstructuredGridPartialPreIntegration = obj.NewInstance ()|

\item  \verb|vtkUnstructuredGridPartialPreIntegration = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.Initialize (vtkVolume volume, vtkDataArray scalars)|

\item  \verb|obj.Integrate (vtkDoubleArray intersectionLengths, vtkDataArray nearIntersections, vtkDataArray farIntersections, float color[4])|

\end{itemize}
