\section{vtkVolumeProMapper}

\subsection{Usage}

 vtkVolumeProMapper is the superclass for VolumePRO volume rendering mappers.
 Any functionality that is general across all VolumePRO implementations is
 placed here in this class. Subclasses of this class are for the specific
 board implementations. Subclasses of that are for underlying graphics 
 languages. Users should not create subclasses directly - 
 a vtkVolumeProMapper will automatically create the object of the right 
 type.

 If you do not have the VolumePRO libraries when building this object, then
 the New method will create a default renderer that will not render.
 You can check the NumberOfBoards ivar to see if it is a real rendering class.
 To build with the VolumePRO board see vtkVolumeProVP1000Mapper.h 
 for instructions.

 For more information on the VolumePRO hardware, please see:

   http://www.terarecon.com/products/volumepro\_prod.html

 If you encounter any problems with this class, please inform Kitware, Inc.
 at kitware@kitware.com.



To create an instance of class vtkVolumeProMapper, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkVolumeProMapper
\end{verbatim}
\subsection{Methods}

The class vtkVolumeProMapper has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkVolumeProMapper class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkVolumeProMapper = obj.NewInstance ()|

\item  \verb|vtkVolumeProMapper = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.Render (vtkRenderer , vtkVolume )| -  Set the blend mode

\item  \verb|obj.SetBlendMode (int )| -  Set the blend mode

\item  \verb|int = obj.GetBlendModeMinValue ()| -  Set the blend mode

\item  \verb|int = obj.GetBlendModeMaxValue ()| -  Set the blend mode

\item  \verb|int = obj.GetBlendMode ()| -  Set the blend mode

\item  \verb|obj.SetBlendModeToComposite ()| -  Set the blend mode

\item  \verb|obj.SetBlendModeToMaximumIntensity ()| -  Set the blend mode

\item  \verb|obj.SetBlendModeToMinimumIntensity ()| -  Set the blend mode

\item  \verb|string = obj.GetBlendModeAsString (void )| -  Set the blend mode

\item  \verb|obj.SetSubVolume (int , int , int , int , int , int )| -  Set the subvolume

\item  \verb|obj.SetSubVolume (int  a[6])| -  Set the subvolume

\item  \verb|int = obj. GetSubVolume ()| -  Set the subvolume

\item  \verb|obj.SetCursor (int )| -  Turn the cursor on / off

\item  \verb|int = obj.GetCursorMinValue ()| -  Turn the cursor on / off

\item  \verb|int = obj.GetCursorMaxValue ()| -  Turn the cursor on / off

\item  \verb|int = obj.GetCursor ()| -  Turn the cursor on / off

\item  \verb|obj.CursorOn ()| -  Turn the cursor on / off

\item  \verb|obj.CursorOff ()| -  Turn the cursor on / off

\item  \verb|obj.SetCursorType (int )| -  Set the type of the cursor

\item  \verb|int = obj.GetCursorTypeMinValue ()| -  Set the type of the cursor

\item  \verb|int = obj.GetCursorTypeMaxValue ()| -  Set the type of the cursor

\item  \verb|int = obj.GetCursorType ()| -  Set the type of the cursor

\item  \verb|obj.SetCursorTypeToCrossHair ()| -  Set the type of the cursor

\item  \verb|obj.SetCursorTypeToPlane ()| -  Set the type of the cursor

\item  \verb|string = obj.GetCursorTypeAsString (void )| -  Set the type of the cursor

\item  \verb|obj.SetCursorPosition (double , double , double )| -  Set/Get the cursor position

\item  \verb|obj.SetCursorPosition (double  a[3])| -  Set/Get the cursor position

\item  \verb|double = obj. GetCursorPosition ()| -  Set/Get the cursor position

\item  \verb|obj.SetCursorXAxisColor (double , double , double )| -  Set/Get the cursor color

\item  \verb|obj.SetCursorXAxisColor (double  a[3])| -  Set/Get the cursor color

\item  \verb|double = obj. GetCursorXAxisColor ()| -  Set/Get the cursor color

\item  \verb|obj.SetCursorYAxisColor (double , double , double )| -  Set/Get the cursor color

\item  \verb|obj.SetCursorYAxisColor (double  a[3])| -  Set/Get the cursor color

\item  \verb|double = obj. GetCursorYAxisColor ()| -  Set/Get the cursor color

\item  \verb|obj.SetCursorZAxisColor (double , double , double )| -  Set/Get the cursor color

\item  \verb|obj.SetCursorZAxisColor (double  a[3])| -  Set/Get the cursor color

\item  \verb|double = obj. GetCursorZAxisColor ()| -  Set/Get the cursor color

\item  \verb|obj.SetSuperSampling (int )| -  Turn supersampling on/off

\item  \verb|int = obj.GetSuperSamplingMinValue ()| -  Turn supersampling on/off

\item  \verb|int = obj.GetSuperSamplingMaxValue ()| -  Turn supersampling on/off

\item  \verb|int = obj.GetSuperSampling ()| -  Turn supersampling on/off

\item  \verb|obj.SuperSamplingOn ()| -  Turn supersampling on/off

\item  \verb|obj.SuperSamplingOff ()| -  Turn supersampling on/off

\item  \verb|obj.SetSuperSamplingFactor (double x, double y, double z)| -  Set the supersampling factors

\item  \verb|obj.SetSuperSamplingFactor (double f[3])| -  Set the supersampling factors

\item  \verb|double = obj. GetSuperSamplingFactor ()| -  Set the supersampling factors

\item  \verb|obj.SetCutPlane (int )| -  Turn on / off the cut plane

\item  \verb|int = obj.GetCutPlaneMinValue ()| -  Turn on / off the cut plane

\item  \verb|int = obj.GetCutPlaneMaxValue ()| -  Turn on / off the cut plane

\item  \verb|int = obj.GetCutPlane ()| -  Turn on / off the cut plane

\item  \verb|obj.CutPlaneOn ()| -  Turn on / off the cut plane

\item  \verb|obj.CutPlaneOff ()| -  Turn on / off the cut plane

\item  \verb|obj.SetCutPlaneEquation (double , double , double , double )| -  Set/Get the cut plane equation

\item  \verb|obj.SetCutPlaneEquation (double  a[4])| -  Set/Get the cut plane equation

\item  \verb|double = obj. GetCutPlaneEquation ()| -  Set/Get the cut plane equation

\item  \verb|obj.SetCutPlaneThickness (double )| -  Set / Get the cut plane thickness

\item  \verb|double = obj.GetCutPlaneThicknessMinValue ()| -  Set / Get the cut plane thickness

\item  \verb|double = obj.GetCutPlaneThicknessMaxValue ()| -  Set / Get the cut plane thickness

\item  \verb|double = obj.GetCutPlaneThickness ()| -  Set / Get the cut plane thickness

\item  \verb|obj.SetCutPlaneFallOffDistance (int )| -  Set / Get the cut plane falloff value for intensities

\item  \verb|int = obj.GetCutPlaneFallOffDistanceMinValue ()| -  Set / Get the cut plane falloff value for intensities

\item  \verb|int = obj.GetCutPlaneFallOffDistanceMaxValue ()| -  Set / Get the cut plane falloff value for intensities

\item  \verb|int = obj.GetCutPlaneFallOffDistance ()| -  Set / Get the cut plane falloff value for intensities

\item  \verb|obj.SetGradientOpacityModulation (int )| -  Set/Get the gradient magnitude opacity modulation 

\item  \verb|int = obj.GetGradientOpacityModulationMinValue ()| -  Set/Get the gradient magnitude opacity modulation 

\item  \verb|int = obj.GetGradientOpacityModulationMaxValue ()| -  Set/Get the gradient magnitude opacity modulation 

\item  \verb|int = obj.GetGradientOpacityModulation ()| -  Set/Get the gradient magnitude opacity modulation 

\item  \verb|obj.GradientOpacityModulationOn ()| -  Set/Get the gradient magnitude opacity modulation 

\item  \verb|obj.GradientOpacityModulationOff ()| -  Set/Get the gradient magnitude opacity modulation 

\item  \verb|obj.SetGradientDiffuseModulation (int )| -  Set/Get the gradient magnitude diffuse modulation 

\item  \verb|int = obj.GetGradientDiffuseModulationMinValue ()| -  Set/Get the gradient magnitude diffuse modulation 

\item  \verb|int = obj.GetGradientDiffuseModulationMaxValue ()| -  Set/Get the gradient magnitude diffuse modulation 

\item  \verb|int = obj.GetGradientDiffuseModulation ()| -  Set/Get the gradient magnitude diffuse modulation 

\item  \verb|obj.GradientDiffuseModulationOn ()| -  Set/Get the gradient magnitude diffuse modulation 

\item  \verb|obj.GradientDiffuseModulationOff ()| -  Set/Get the gradient magnitude diffuse modulation 

\item  \verb|obj.SetGradientSpecularModulation (int )| -  Set/Get the gradient magnitude specular modulation 

\item  \verb|int = obj.GetGradientSpecularModulationMinValue ()| -  Set/Get the gradient magnitude specular modulation 

\item  \verb|int = obj.GetGradientSpecularModulationMaxValue ()| -  Set/Get the gradient magnitude specular modulation 

\item  \verb|int = obj.GetGradientSpecularModulation ()| -  Set/Get the gradient magnitude specular modulation 

\item  \verb|obj.GradientSpecularModulationOn ()| -  Set/Get the gradient magnitude specular modulation 

\item  \verb|obj.GradientSpecularModulationOff ()| -  Set/Get the gradient magnitude specular modulation 

\item  \verb|int = obj.GetNoHardware ()| -  Conveniece methods for debugging

\item  \verb|int = obj.GetWrongVLIVersion ()| -  Conveniece methods for debugging

\item  \verb|int = obj.GetNumberOfBoards ()| -  Access methods for some board info

\item  \verb|int = obj.GetMajorBoardVersion ()| -  Access methods for some board info

\item  \verb|int = obj.GetMinorBoardVersion ()| -  Access methods for some board info

\item  \verb|int = obj.GetAvailableBoardMemory ()| -  Access methods for some board info

\item  \verb|obj.GetLockSizesForBoardMemory (int , int , int , int )| -  Access methods for some board info

\item  \verb|obj.SetIntermixIntersectingGeometry (int )| -  Specify whether any geometry intersects the volume.

\item  \verb|int = obj.GetIntermixIntersectingGeometryMinValue ()| -  Specify whether any geometry intersects the volume.

\item  \verb|int = obj.GetIntermixIntersectingGeometryMaxValue ()| -  Specify whether any geometry intersects the volume.

\item  \verb|int = obj.GetIntermixIntersectingGeometry ()| -  Specify whether any geometry intersects the volume.

\item  \verb|obj.IntermixIntersectingGeometryOn ()| -  Specify whether any geometry intersects the volume.

\item  \verb|obj.IntermixIntersectingGeometryOff ()| -  Specify whether any geometry intersects the volume.

\item  \verb|obj.SetAutoAdjustMipmapLevels (int )| -  If set to 1, this mapper will select a mipmap level to use based
 on the AllocatedRenderTime of the volume and the amount of time used
 by the previous render.

\item  \verb|int = obj.GetAutoAdjustMipmapLevelsMinValue ()| -  If set to 1, this mapper will select a mipmap level to use based
 on the AllocatedRenderTime of the volume and the amount of time used
 by the previous render.

\item  \verb|int = obj.GetAutoAdjustMipmapLevelsMaxValue ()| -  If set to 1, this mapper will select a mipmap level to use based
 on the AllocatedRenderTime of the volume and the amount of time used
 by the previous render.

\item  \verb|int = obj.GetAutoAdjustMipmapLevels ()| -  If set to 1, this mapper will select a mipmap level to use based
 on the AllocatedRenderTime of the volume and the amount of time used
 by the previous render.

\item  \verb|obj.AutoAdjustMipmapLevelsOn ()| -  If set to 1, this mapper will select a mipmap level to use based
 on the AllocatedRenderTime of the volume and the amount of time used
 by the previous render.

\item  \verb|obj.AutoAdjustMipmapLevelsOff ()| -  If set to 1, this mapper will select a mipmap level to use based
 on the AllocatedRenderTime of the volume and the amount of time used
 by the previous render.

\item  \verb|obj.SetMinimumMipmapLevel (int )| -  Specify the minimum mipmap level to use -- the highest resolution.
 Defaults to 0. This is the mipmap level that is used when interaction
 stops.

\item  \verb|int = obj.GetMinimumMipmapLevelMinValue ()| -  Specify the minimum mipmap level to use -- the highest resolution.
 Defaults to 0. This is the mipmap level that is used when interaction
 stops.

\item  \verb|int = obj.GetMinimumMipmapLevelMaxValue ()| -  Specify the minimum mipmap level to use -- the highest resolution.
 Defaults to 0. This is the mipmap level that is used when interaction
 stops.

\item  \verb|int = obj.GetMinimumMipmapLevel ()| -  Specify the minimum mipmap level to use -- the highest resolution.
 Defaults to 0. This is the mipmap level that is used when interaction
 stops.

\item  \verb|obj.SetMaximumMipmapLevel (int )| -  Specify the maximum mipmap level to use -- the lowest resolution.
 Defaults to 4. It will not help to set the level larger than
 this unless your volume is very large because for each successive mipmap
 level, the number of voxels along each axis is cut in half.

\item  \verb|int = obj.GetMaximumMipmapLevelMinValue ()| -  Specify the maximum mipmap level to use -- the lowest resolution.
 Defaults to 4. It will not help to set the level larger than
 this unless your volume is very large because for each successive mipmap
 level, the number of voxels along each axis is cut in half.

\item  \verb|int = obj.GetMaximumMipmapLevelMaxValue ()| -  Specify the maximum mipmap level to use -- the lowest resolution.
 Defaults to 4. It will not help to set the level larger than
 this unless your volume is very large because for each successive mipmap
 level, the number of voxels along each axis is cut in half.

\item  \verb|int = obj.GetMaximumMipmapLevel ()| -  Specify the maximum mipmap level to use -- the lowest resolution.
 Defaults to 4. It will not help to set the level larger than
 this unless your volume is very large because for each successive mipmap
 level, the number of voxels along each axis is cut in half.

\item  \verb|obj.SetMipmapLevel (int )| -  Choose a mipmap level. If AutoAdjustMipmapLevels is off, then this
 specifies the mipmap level to use during interaction. If
 AutoAdjustMipmapLevels is on, then this specifies the initial mipmap
 level to use.

\item  \verb|int = obj.GetMipmapLevelMinValue ()| -  Choose a mipmap level. If AutoAdjustMipmapLevels is off, then this
 specifies the mipmap level to use during interaction. If
 AutoAdjustMipmapLevels is on, then this specifies the initial mipmap
 level to use.

\item  \verb|int = obj.GetMipmapLevelMaxValue ()| -  Choose a mipmap level. If AutoAdjustMipmapLevels is off, then this
 specifies the mipmap level to use during interaction. If
 AutoAdjustMipmapLevels is on, then this specifies the initial mipmap
 level to use.

\item  \verb|int = obj.GetMipmapLevel ()| -  Choose a mipmap level. If AutoAdjustMipmapLevels is off, then this
 specifies the mipmap level to use during interaction. If
 AutoAdjustMipmapLevels is on, then this specifies the initial mipmap
 level to use.

\end{itemize}
