\section{vtkRayCastImageDisplayHelper}

\subsection{Usage}

 This is a helper class for drawing images created from ray casting on the screen.
 This is the abstract device-independent superclass.

To create an instance of class vtkRayCastImageDisplayHelper, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkRayCastImageDisplayHelper
\end{verbatim}
\subsection{Methods}

The class vtkRayCastImageDisplayHelper has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkRayCastImageDisplayHelper class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkRayCastImageDisplayHelper = obj.NewInstance ()|

\item  \verb|vtkRayCastImageDisplayHelper = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.RenderTexture (vtkVolume vol, vtkRenderer ren, int imageMemorySize[2], int imageViewportSize[2], int imageInUseSize[2], int imageOrigin[2], float requestedDepth, string image)|

\item  \verb|obj.RenderTexture (vtkVolume vol, vtkRenderer ren, int imageMemorySize[2], int imageViewportSize[2], int imageInUseSize[2], int imageOrigin[2], float requestedDepth, short image)|

\item  \verb|obj.RenderTexture (vtkVolume vol, vtkRenderer ren, vtkFixedPointRayCastImage image, float requestedDepth)|

\item  \verb|obj.SetPreMultipliedColors (int )|

\item  \verb|int = obj.GetPreMultipliedColorsMinValue ()|

\item  \verb|int = obj.GetPreMultipliedColorsMaxValue ()|

\item  \verb|int = obj.GetPreMultipliedColors ()|

\item  \verb|obj.PreMultipliedColorsOn ()|

\item  \verb|obj.PreMultipliedColorsOff ()|

\item  \verb|obj.SetPixelScale (float )| -  Set / Get the pixel scale to be applied to the image before display.
 Can be set to scale the incoming pixel values - for example the
 fixed point mapper uses the unsigned short API but with 15 bit
 values so needs a scale of 2.0.

\item  \verb|float = obj.GetPixelScale ()| -  Set / Get the pixel scale to be applied to the image before display.
 Can be set to scale the incoming pixel values - for example the
 fixed point mapper uses the unsigned short API but with 15 bit
 values so needs a scale of 2.0.

\end{itemize}
