\section{vtkParallelCoordinatesRepresentation}

\subsection{Usage}

  A parallel coordinates plot represents each variable in a multivariate
  data set as a separate axis.  Individual samples of that data set are
  represented as a polyline that pass through each variable axis at 
  positions that correspond to data values.  vtkParallelCoordinatesRepresentation
  generates this plot when added to a vtkParallelCoordinatesView, which handles 
  interaction and highlighting.  Sample polylines can alternatively
  be represented as s-curves by enabling the UseCurves flag.  

  There are three selection modes: lasso, angle, and function. Lasso selection
  picks sample lines that pass through a polyline.  Angle selection picks sample 
  lines that have similar slope to a line segment.  Function selection picks
  sample lines that are near a linear function defined on two variables.  This
  function specified by passing two (x,y) variable value pairs.

  All primitives are plotted in normalized view coordinates [0,1].


To create an instance of class vtkParallelCoordinatesRepresentation, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkParallelCoordinatesRepresentation
\end{verbatim}
\subsection{Methods}

The class vtkParallelCoordinatesRepresentation has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkParallelCoordinatesRepresentation class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkParallelCoordinatesRepresentation = obj.NewInstance ()|

\item  \verb|vtkParallelCoordinatesRepresentation = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.ApplyViewTheme (vtkViewTheme theme)| -  Apply the theme to this view.  CellColor is used for line coloring
 and titles.  EdgeLabelColor is used for axis color. CellOpacity is 
 used for line opacity.

\item  \verb|string = obj.GetHoverText (vtkView view, int x, int y)| -  Returns the hover text at an x,y location.

\item  \verb|int = obj.SetPositionAndSize (double position, double size)| -  Change the position of the plot

\item  \verb|int = obj.GetPositionAndSize (double position, double size)| -  Change the position of the plot

\item  \verb|obj.SetAxisTitles (vtkStringArray )| -  Set/Get the axis titles

\item  \verb|obj.SetAxisTitles (vtkAlgorithmOutput )| -  Set/Get the axis titles

\item  \verb|obj.SetPlotTitle (string )| -  Set the title for the entire plot

\item  \verb|int = obj.GetNumberOfAxes ()| -  Get the number of axes in the plot

\item  \verb|int = obj.GetNumberOfSamples ()|

\item  \verb|obj.SetNumberOfAxisLabels (int num)| -  Set/Get the number of labels to display on each axis

\item  \verb|int = obj.GetNumberOfAxisLabels ()| -  Set/Get the number of labels to display on each axis

\item  \verb|int = obj.SwapAxisPositions (int position1, int position2)| -  Move an axis to a particular screen position.  Using these
 methods requires an Update() before they will work properly.

\item  \verb|int = obj.SetXCoordinateOfPosition (int position, double xcoord)| -  Move an axis to a particular screen position.  Using these
 methods requires an Update() before they will work properly.

\item  \verb|double = obj.GetXCoordinateOfPosition (int axis)| -  Move an axis to a particular screen position.  Using these
 methods requires an Update() before they will work properly.

\item  \verb|obj.GetXCoordinatesOfPositions (double coords)| -  Move an axis to a particular screen position.  Using these
 methods requires an Update() before they will work properly.

\item  \verb|int = obj.GetPositionNearXCoordinate (double xcoord)| -  Move an axis to a particular screen position.  Using these
 methods requires an Update() before they will work properly.

\item  \verb|obj.SetUseCurves (int )| -  Whether or not to display using curves

\item  \verb|int = obj.GetUseCurves ()| -  Whether or not to display using curves

\item  \verb|obj.UseCurvesOn ()| -  Whether or not to display using curves

\item  \verb|obj.UseCurvesOff ()| -  Whether or not to display using curves

\item  \verb|obj.SetCurveResolution (int )| -  Resolution of the curves displayed, enabled by setting UseCurves

\item  \verb|int = obj.GetCurveResolution ()| -  Resolution of the curves displayed, enabled by setting UseCurves

\item  \verb|double = obj.GetLineOpacity ()| -  Access plot properties

\item  \verb|double = obj.GetFontSize ()| -  Access plot properties

\item  \verb|double = obj. GetLineColor ()| -  Access plot properties

\item  \verb|double = obj. GetAxisColor ()| -  Access plot properties

\item  \verb|double = obj. GetAxisLabelColor ()| -  Access plot properties

\item  \verb|obj.SetLineOpacity (double )| -  Access plot properties

\item  \verb|obj.SetFontSize (double )| -  Access plot properties

\item  \verb|obj.SetLineColor (double , double , double )| -  Access plot properties

\item  \verb|obj.SetLineColor (double  a[3])| -  Access plot properties

\item  \verb|obj.SetAxisColor (double , double , double )| -  Access plot properties

\item  \verb|obj.SetAxisColor (double  a[3])| -  Access plot properties

\item  \verb|obj.SetAxisLabelColor (double , double , double )| -  Access plot properties

\item  \verb|obj.SetAxisLabelColor (double  a[3])| -  Access plot properties

\item  \verb|obj.SetAngleBrushThreshold (double )| -  Maximum angle difference (in degrees) of selection using angle/function brushes

\item  \verb|double = obj.GetAngleBrushThreshold ()| -  Maximum angle difference (in degrees) of selection using angle/function brushes

\item  \verb|obj.SetFunctionBrushThreshold (double )| -  Maximum angle difference (in degrees) of selection using angle/function brushes

\item  \verb|double = obj.GetFunctionBrushThreshold ()| -  Maximum angle difference (in degrees) of selection using angle/function brushes

\item  \verb|int = obj.GetRangeAtPosition (int position, double range[2])| -  Set/get the value range of the axis at a particular screen position

\item  \verb|int = obj.SetRangeAtPosition (int position, double range[2])| -  Set/get the value range of the axis at a particular screen position

\item  \verb|obj.ResetAxes ()| -  Reset the axes to their default positions and orders

\item  \verb|obj.LassoSelect (int brushClass, int brushOperator, vtkPoints brushPoints)| -  Do a selection of the lines.  See the main description for how to use these functions.  
 RangeSelect is currently stubbed out.

\item  \verb|obj.AngleSelect (int brushClass, int brushOperator, double p1, double p2)| -  Do a selection of the lines.  See the main description for how to use these functions.  
 RangeSelect is currently stubbed out.

\item  \verb|obj.FunctionSelect (int brushClass, int brushOperator, double p1, double p2, double q1, double q2)| -  Do a selection of the lines.  See the main description for how to use these functions.  
 RangeSelect is currently stubbed out.

\item  \verb|obj.RangeSelect (int brushClass, int brushOperator, double p1, double p2)| -  Do a selection of the lines.  See the main description for how to use these functions.  
 RangeSelect is currently stubbed out.

\end{itemize}
