\section{vtkInteractorStyleAreaSelectHover}

\subsection{Usage}

 The vtkInteractorStyleAreaSelectHover specifically works with pipelines
 that create a hierarchical tree.  Such pipelines will have a vtkAreaLayout
 filter which must be passed to this interactor style for it to function
 correctly.
 This interactor style allows only 2D panning and zooming,
 rubber band selection and provides a balloon containing the name of the
 vertex hovered over.

To create an instance of class vtkInteractorStyleAreaSelectHover, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkInteractorStyleAreaSelectHover
\end{verbatim}
\subsection{Methods}

The class vtkInteractorStyleAreaSelectHover has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkInteractorStyleAreaSelectHover class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkInteractorStyleAreaSelectHover = obj.NewInstance ()|

\item  \verb|vtkInteractorStyleAreaSelectHover = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetLayout (vtkAreaLayout layout)| -  Must be set to the vtkAreaLayout used to compute the bounds of
 each vertex.

\item  \verb|vtkAreaLayout = obj.GetLayout ()| -  Must be set to the vtkAreaLayout used to compute the bounds of
 each vertex.

\item  \verb|obj.SetLabelField (string )| -  The name of the field to use when displaying text in the hover balloon.

\item  \verb|string = obj.GetLabelField ()| -  The name of the field to use when displaying text in the hover balloon.

\item  \verb|obj.SetUseRectangularCoordinates (bool )| -  Determine whether or not to use rectangular coordinates instead of
 polar coordinates.

\item  \verb|bool = obj.GetUseRectangularCoordinates ()| -  Determine whether or not to use rectangular coordinates instead of
 polar coordinates.

\item  \verb|obj.UseRectangularCoordinatesOn ()| -  Determine whether or not to use rectangular coordinates instead of
 polar coordinates.

\item  \verb|obj.UseRectangularCoordinatesOff ()| -  Determine whether or not to use rectangular coordinates instead of
 polar coordinates.

\item  \verb|obj.OnMouseMove ()| -  Overridden from vtkInteractorStyleImage to provide the desired
 interaction behavior.

\item  \verb|obj.SetInteractor (vtkRenderWindowInteractor rwi)| -  Set the interactor that this interactor style works with.

\item  \verb|obj.SetHighLightColor (double r, double g, double b)| -  Set the color used to highlight the hovered vertex.

\item  \verb|obj.SetHighLightWidth (double lw)| -  The width of the line around the hovered vertex.

\item  \verb|double = obj.GetHighLightWidth ()| -  The width of the line around the hovered vertex.

\item  \verb|vtkIdType = obj.GetIdAtPos (int x, int y)| -  Obtain the tree vertex id at the position specified.

\end{itemize}
