\section{vtkVolumeRayCastMIPFunction}

\subsection{Usage}

 vtkVolumeRayCastMIPFunction is a volume ray cast function that
 computes the maximum value encountered along the ray. This is
 either the maximum scalar value, or the maximum opacity, as
 defined by the MaximizeMethod. The color and opacity returned
 by this function is based on the color, scalar opacity, and
 gradient opacity transfer functions defined in the vtkVolumeProperty
 of the vtkVolume.


To create an instance of class vtkVolumeRayCastMIPFunction, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkVolumeRayCastMIPFunction
\end{verbatim}
\subsection{Methods}

The class vtkVolumeRayCastMIPFunction has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkVolumeRayCastMIPFunction class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkVolumeRayCastMIPFunction = obj.NewInstance ()|

\item  \verb|vtkVolumeRayCastMIPFunction = obj.SafeDownCast (vtkObject o)|

\item  \verb|float = obj.GetZeroOpacityThreshold (vtkVolume vol)| -  Get the scalar value below which all scalar values have zero opacity.

\item  \verb|obj.SetMaximizeMethod (int )| -  Set the MaximizeMethod to either ScalarValue or Opacity.

\item  \verb|int = obj.GetMaximizeMethodMinValue ()| -  Set the MaximizeMethod to either ScalarValue or Opacity.

\item  \verb|int = obj.GetMaximizeMethodMaxValue ()| -  Set the MaximizeMethod to either ScalarValue or Opacity.

\item  \verb|int = obj.GetMaximizeMethod ()| -  Set the MaximizeMethod to either ScalarValue or Opacity.

\item  \verb|obj.SetMaximizeMethodToScalarValue ()| -  Set the MaximizeMethod to either ScalarValue or Opacity.

\item  \verb|obj.SetMaximizeMethodToOpacity ()| -  Set the MaximizeMethod to either ScalarValue or Opacity.

\item  \verb|string = obj.GetMaximizeMethodAsString (void )| -  Set the MaximizeMethod to either ScalarValue or Opacity.

\end{itemize}
