\section{vtkInteractorStyleTreeMapHover}

\subsection{Usage}

 The vtkInteractorStyleTreeMapHover specifically works with pipelines
 that create a tree map.  Such pipelines will have a vtkTreeMapLayout
 filter and a vtkTreeMapToPolyData filter, both of which must be passed
 to this interactor style for it to function correctly.
 This interactor style allows only 2D panning and zooming, and additionally
 provides a balloon containing the name of the vertex hovered over,
 and allows the user to highlight a vertex by clicking on it.

To create an instance of class vtkInteractorStyleTreeMapHover, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkInteractorStyleTreeMapHover
\end{verbatim}
\subsection{Methods}

The class vtkInteractorStyleTreeMapHover has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkInteractorStyleTreeMapHover class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()|

\item  \verb|int = obj.IsA (string name)|

\item  \verb|vtkInteractorStyleTreeMapHover = obj.NewInstance ()|

\item  \verb|vtkInteractorStyleTreeMapHover = obj.SafeDownCast (vtkObject o)|

\item  \verb|obj.SetLayout (vtkTreeMapLayout layout)| -  Must be set to the vtkTreeMapLayout used to compute the bounds of each vertex
 for the tree map.

\item  \verb|vtkTreeMapLayout = obj.GetLayout ()| -  Must be set to the vtkTreeMapLayout used to compute the bounds of each vertex
 for the tree map.

\item  \verb|obj.SetTreeMapToPolyData (vtkTreeMapToPolyData filter)| -  Must be set to the vtkTreeMapToPolyData used to convert the tree map
 into polydata.

\item  \verb|vtkTreeMapToPolyData = obj.GetTreeMapToPolyData ()| -  Must be set to the vtkTreeMapToPolyData used to convert the tree map
 into polydata.

\item  \verb|obj.SetLabelField (string )| -  The name of the field to use when displaying text in the hover balloon.

\item  \verb|string = obj.GetLabelField ()| -  The name of the field to use when displaying text in the hover balloon.

\item  \verb|obj.OnMouseMove ()| -  Overridden from vtkInteractorStyleImage to provide the desired
 interaction behavior.

\item  \verb|obj.OnLeftButtonUp ()| -  Overridden from vtkInteractorStyleImage to provide the desired
 interaction behavior.

\item  \verb|obj.HighLightItem (vtkIdType id)| -  Highlights a specific vertex.

\item  \verb|obj.HighLightCurrentSelectedItem ()| -  Highlights a specific vertex.

\item  \verb|obj.SetInteractor (vtkRenderWindowInteractor rwi)|

\item  \verb|obj.SetHighLightColor (double r, double g, double b)| -  Set the color used to highlight the hovered vertex.

\item  \verb|obj.SetSelectionLightColor (double r, double g, double b)| -  Set the color used to highlight the selected vertex.

\item  \verb|obj.SetHighLightWidth (double lw)| -  The width of the line around the hovered vertex.

\item  \verb|double = obj.GetHighLightWidth ()| -  The width of the line around the hovered vertex.

\item  \verb|obj.SetSelectionWidth (double lw)| -  The width of the line around the selected vertex.

\item  \verb|double = obj.GetSelectionWidth ()| -  The width of the line around the selected vertex.

\end{itemize}
