\section{vtkHandleWidget}

\subsection{Usage}

 The vtkHandleWidget is used to position a handle.  A handle is a widget
 with a position (in display and world space). Various appearances are
 available depending on its associated representation. The widget provides
 methods for translation, including constrained translation along
 coordinate axes. To use this widget, create and associate a representation
 with the widget.

 .SECTION Event Bindings
 By default, the widget responds to the following VTK events (i.e., it
 watches the vtkRenderWindowInteractor for these events):
 \begin{verbatim}
   LeftButtonPressEvent - select focal point of widget
   LeftButtonReleaseEvent - end selection
   MiddleButtonPressEvent - translate widget
   MiddleButtonReleaseEvent - end translation
   RightButtonPressEvent - scale widget
   RightButtonReleaseEvent - end scaling
   MouseMoveEvent - interactive movement across widget
 \end{verbatim}

 Note that the event bindings described above can be changed using this
 class's vtkWidgetEventTranslator. This class translates VTK events 
 into the vtkHandleWidget's widget events:
 \begin{verbatim}
   vtkWidgetEvent::Select -- focal point is being selected
   vtkWidgetEvent::EndSelect -- the selection process has completed
   vtkWidgetEvent::Translate -- translate the widget
   vtkWidgetEvent::EndTranslate -- end widget translation
   vtkWidgetEvent::Scale -- scale the widget
   vtkWidgetEvent::EndScale -- end scaling the widget
   vtkWidgetEvent::Move -- a request for widget motion
 \end{verbatim}

 In turn, when these widget events are processed, the vtkHandleWidget
 invokes the following VTK events on itself (which observers can listen for):
 \begin{verbatim}
   vtkCommand::StartInteractionEvent (on vtkWidgetEvent::Select)
   vtkCommand::EndInteractionEvent (on vtkWidgetEvent::EndSelect)
   vtkCommand::InteractionEvent (on vtkWidgetEvent::Move)
 \end{verbatim}


To create an instance of class vtkHandleWidget, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkHandleWidget
\end{verbatim}
\subsection{Methods}

The class vtkHandleWidget has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkHandleWidget class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()| -  Standard VTK class macros.

\item  \verb|int = obj.IsA (string name)| -  Standard VTK class macros.

\item  \verb|vtkHandleWidget = obj.NewInstance ()| -  Standard VTK class macros.

\item  \verb|vtkHandleWidget = obj.SafeDownCast (vtkObject o)| -  Standard VTK class macros.

\item  \verb|obj.SetRepresentation (vtkHandleRepresentation r)| -  Create the default widget representation if one is not set. By default
 an instance of vtkPointHandleRepresenation3D is created.

\item  \verb|obj.CreateDefaultRepresentation ()| -  Create the default widget representation if one is not set. By default
 an instance of vtkPointHandleRepresenation3D is created.

\item  \verb|obj.SetEnableAxisConstraint (int )| -  Enable / disable axis constrained motion of the handles. By default the
 widget responds to the shift modifier to constrain the handle along the
 axis closest aligned with the motion vector.

\item  \verb|int = obj.GetEnableAxisConstraint ()| -  Enable / disable axis constrained motion of the handles. By default the
 widget responds to the shift modifier to constrain the handle along the
 axis closest aligned with the motion vector.

\item  \verb|obj.EnableAxisConstraintOn ()| -  Enable / disable axis constrained motion of the handles. By default the
 widget responds to the shift modifier to constrain the handle along the
 axis closest aligned with the motion vector.

\item  \verb|obj.EnableAxisConstraintOff ()| -  Enable / disable axis constrained motion of the handles. By default the
 widget responds to the shift modifier to constrain the handle along the
 axis closest aligned with the motion vector.

\item  \verb|obj.SetAllowHandleResize (int )| -  Allow resizing of handles ? By default the right mouse button scales
 the handle size.

\item  \verb|int = obj.GetAllowHandleResize ()| -  Allow resizing of handles ? By default the right mouse button scales
 the handle size.

\item  \verb|obj.AllowHandleResizeOn ()| -  Allow resizing of handles ? By default the right mouse button scales
 the handle size.

\item  \verb|obj.AllowHandleResizeOff ()| -  Allow resizing of handles ? By default the right mouse button scales
 the handle size.

\item  \verb|int = obj.GetWidgetState ()| -  Get the widget state.

\end{itemize}
