\section{vtkPlaybackRepresentation}

\subsection{Usage}

 This class is used to represent the vtkPlaybackWidget. Besides defining
 geometry, this class defines a series of virtual method stubs that are
 meant to be subclassed by applications for controlling playback.

To create an instance of class vtkPlaybackRepresentation, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkPlaybackRepresentation
\end{verbatim}
\subsection{Methods}

The class vtkPlaybackRepresentation has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkPlaybackRepresentation class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()| -  Standard VTK class methods.

\item  \verb|int = obj.IsA (string name)| -  Standard VTK class methods.

\item  \verb|vtkPlaybackRepresentation = obj.NewInstance ()| -  Standard VTK class methods.

\item  \verb|vtkPlaybackRepresentation = obj.SafeDownCast (vtkObject o)| -  Standard VTK class methods.

\item  \verb|vtkProperty2D = obj.GetProperty ()| -  By obtaining this property you can specify the properties of the 
 representation.

\item  \verb|obj.Play ()| -  Virtual callbacks that subclasses should implement.

\item  \verb|obj.Stop ()| -  Virtual callbacks that subclasses should implement.

\item  \verb|obj.ForwardOneFrame ()| -  Virtual callbacks that subclasses should implement.

\item  \verb|obj.BackwardOneFrame ()| -  Virtual callbacks that subclasses should implement.

\item  \verb|obj.JumpToBeginning ()| -  Virtual callbacks that subclasses should implement.

\item  \verb|obj.JumpToEnd ()| -  Satisfy the superclasses' API.

\item  \verb|obj.BuildRepresentation ()| -  Satisfy the superclasses' API.

\item  \verb|obj.GetSize (double size[2])| -  These methods are necessary to make this representation behave as
 a vtkProp.

\item  \verb|obj.GetActors2D (vtkPropCollection )| -  These methods are necessary to make this representation behave as
 a vtkProp.

\item  \verb|obj.ReleaseGraphicsResources (vtkWindow )| -  These methods are necessary to make this representation behave as
 a vtkProp.

\item  \verb|int = obj.RenderOverlay (vtkViewport )| -  These methods are necessary to make this representation behave as
 a vtkProp.

\item  \verb|int = obj.RenderOpaqueGeometry (vtkViewport )| -  These methods are necessary to make this representation behave as
 a vtkProp.

\item  \verb|int = obj.RenderTranslucentPolygonalGeometry (vtkViewport )| -  These methods are necessary to make this representation behave as
 a vtkProp.

\item  \verb|int = obj.HasTranslucentPolygonalGeometry ()| -  These methods are necessary to make this representation behave as
 a vtkProp.

\end{itemize}
