\section{vtkFocalPlanePointPlacer}

\subsection{Usage}

 


To create an instance of class vtkFocalPlanePointPlacer, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkFocalPlanePointPlacer
\end{verbatim}
\subsection{Methods}

The class vtkFocalPlanePointPlacer has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkFocalPlanePointPlacer class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()| -  Standard methods for instances of this class.

\item  \verb|int = obj.IsA (string name)| -  Standard methods for instances of this class.

\item  \verb|vtkFocalPlanePointPlacer = obj.NewInstance ()| -  Standard methods for instances of this class.

\item  \verb|vtkFocalPlanePointPlacer = obj.SafeDownCast (vtkObject o)| -  Standard methods for instances of this class.

\item  \verb|int = obj.ComputeWorldPosition (vtkRenderer ren, double displayPos[2], double worldPos[3], double worldOrient[9])|

\item  \verb|int = obj.ComputeWorldPosition (vtkRenderer ren, double displayPos[2], double refWorldPos[3], double worldPos[3], double worldOrient[9])| -  Given a renderer, a display position, and a reference
 world position, compute a new world position. The
 orientation will be the standard coordinate axes, and the
 computed world position will be created by projecting
 the display point onto a plane that is parallel to
 the focal plane and runs through the reference world
 position. This method is typically used to move existing
 points.

\item  \verb|int = obj.ValidateWorldPosition (double worldPos[3])| -  Validate a world position. All world positions
 are valid so these methods always return 1.

\item  \verb|int = obj.ValidateWorldPosition (double worldPos[3], double worldOrient[9])| -  Validate a world position. All world positions
 are valid so these methods always return 1.

\item  \verb|obj.SetOffset (double )| -  Optionally specify a signed offset from the focal plane for the points to
 be placed at.  If negative, the constraint plane is offset closer to the 
 camera. If positive, its further away from the camera.

\item  \verb|double = obj.GetOffset ()| -  Optionally specify a signed offset from the focal plane for the points to
 be placed at.  If negative, the constraint plane is offset closer to the 
 camera. If positive, its further away from the camera.

\item  \verb|obj.SetPointBounds (double , double , double , double , double , double )| -  Optionally Restrict the points to a set of bounds. The placer will
 invalidate points outside these bounds.

\item  \verb|obj.SetPointBounds (double  a[6])| -  Optionally Restrict the points to a set of bounds. The placer will
 invalidate points outside these bounds.

\item  \verb|double = obj. GetPointBounds ()| -  Optionally Restrict the points to a set of bounds. The placer will
 invalidate points outside these bounds.

\end{itemize}
