\section{vtkOrientedPolygonalHandleRepresentation3D}

\subsection{Usage}

 This class serves as the geometrical representation of a vtkHandleWidget. 
 The handle can be represented by an arbitrary polygonal data (vtkPolyData),
 set via SetHandle(vtkPolyData *). The actual position of the handle 
 will be initially assumed to be (0,0,0). You can specify an offset from
 this position if desired. This class differs from 
 vtkPolygonalHandleRepresentation3D in that the handle will always remain
 front facing, ie it maintains a fixed orientation with respect to the 
 camera. This is done by using vtkFollowers internally to render the actors.

To create an instance of class vtkOrientedPolygonalHandleRepresentation3D, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkOrientedPolygonalHandleRepresentation3D
\end{verbatim}
\subsection{Methods}

The class vtkOrientedPolygonalHandleRepresentation3D has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkOrientedPolygonalHandleRepresentation3D class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()| -  Standard methods for instances of this class.

\item  \verb|int = obj.IsA (string name)| -  Standard methods for instances of this class.

\item  \verb|vtkOrientedPolygonalHandleRepresentation3D = obj.NewInstance ()| -  Standard methods for instances of this class.

\item  \verb|vtkOrientedPolygonalHandleRepresentation3D = obj.SafeDownCast (vtkObject o)| -  Standard methods for instances of this class.

\end{itemize}
