\section{vtkDistanceRepresentation2D}

\subsection{Usage}

 The vtkDistanceRepresentation2D is a representation for the
 vtkDistanceWidget. This representation consists of a measuring line (axis)
 and two vtkHandleWidgets to place the end points of the line. Note that
 this particular widget draws its representation in the overlay plane.

To create an instance of class vtkDistanceRepresentation2D, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkDistanceRepresentation2D
\end{verbatim}
\subsection{Methods}

The class vtkDistanceRepresentation2D has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkDistanceRepresentation2D class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()| -  Standard VTK methods.

\item  \verb|int = obj.IsA (string name)| -  Standard VTK methods.

\item  \verb|vtkDistanceRepresentation2D = obj.NewInstance ()| -  Standard VTK methods.

\item  \verb|vtkDistanceRepresentation2D = obj.SafeDownCast (vtkObject o)| -  Standard VTK methods.

\item  \verb|double = obj.GetDistance ()| -  Methods to Set/Get the coordinates of the two points defining
 this representation. Note that methods are available for both
 display and world coordinates.

\item  \verb|obj.GetPoint1WorldPosition (double pos[3])| -  Methods to Set/Get the coordinates of the two points defining
 this representation. Note that methods are available for both
 display and world coordinates.

\item  \verb|obj.GetPoint2WorldPosition (double pos[3])| -  Methods to Set/Get the coordinates of the two points defining
 this representation. Note that methods are available for both
 display and world coordinates.

\item  \verb|obj.SetPoint1WorldPosition (double pos[3])| -  Methods to Set/Get the coordinates of the two points defining
 this representation. Note that methods are available for both
 display and world coordinates.

\item  \verb|obj.SetPoint2WorldPosition (double pos[3])| -  Methods to Set/Get the coordinates of the two points defining
 this representation. Note that methods are available for both
 display and world coordinates.

\item  \verb|obj.SetPoint1DisplayPosition (double pos[3])|

\item  \verb|obj.SetPoint2DisplayPosition (double pos[3])|

\item  \verb|obj.GetPoint1DisplayPosition (double pos[3])|

\item  \verb|obj.GetPoint2DisplayPosition (double pos[3])|

\item  \verb|vtkAxisActor2D = obj.GetAxis ()| -  Retrieve the vtkAxisActor2D used to draw the measurement axis. With this
 properties can be set and so on.

\item  \verb|obj.BuildRepresentation ()| -  Method to satisfy superclasses' API.

\item  \verb|obj.ReleaseGraphicsResources (vtkWindow w)| -  Methods required by vtkProp superclass.

\item  \verb|int = obj.RenderOverlay (vtkViewport viewport)| -  Methods required by vtkProp superclass.

\item  \verb|int = obj.RenderOpaqueGeometry (vtkViewport viewport)| -  Methods required by vtkProp superclass.

\end{itemize}
