\section{vtkBoxWidget2}

\subsection{Usage}

 This 3D widget interacts with a vtkBoxRepresentation class (i.e., it
 handles the events that drive its corresponding representation). The
 representation is assumed to represent a region of interest that is
 represented by an arbitrarily oriented hexahedron (or box) with interior
 face angles of 90 degrees (i.e., orthogonal faces). The representation
 manifests seven handles that can be moused on and manipulated, plus the
 six faces can also be interacted with. The first six handles are placed on
 the six faces, the seventh is in the center of the box. In addition, a
 bounding box outline is shown, the ''faces'' of which can be selected for
 object rotation or scaling. A nice feature of vtkBoxWidget2, like any 3D
 widget, will work with the current interactor style. That is, if
 vtkBoxWidget2 does not handle an event, then all other registered
 observers (including the interactor style) have an opportunity to process
 the event. Otherwise, the vtkBoxWidget will terminate the processing of
 the event that it handles.

 To use this widget, you generally pair it with a vtkBoxRepresentation
 (or a subclass). Variuos options are available in the representation for 
 controlling how the widget appears, and how the widget functions.

 .SECTION Event Bindings
 By default, the widget responds to the following VTK events (i.e., it
 watches the vtkRenderWindowInteractor for these events):
 \begin{verbatim}
 If one of the seven handles are selected:
   LeftButtonPressEvent - select the appropriate handle 
   LeftButtonReleaseEvent - release the currently selected handle 
   MouseMoveEvent - move the handle
 If one of the faces is selected:
   LeftButtonPressEvent - select a box face
   LeftButtonReleaseEvent - release the box face
   MouseMoveEvent - rotate the box
 In all the cases, independent of what is picked, the widget responds to the 
 following VTK events:
   MiddleButtonPressEvent - translate the widget
   MiddleButtonReleaseEvent - release the widget
   RightButtonPressEvent - scale the widget's representation
   RightButtonReleaseEvent - stop scaling the widget
   MouseMoveEvent - scale (if right button) or move (if middle button) the widget
 \end{verbatim}

 Note that the event bindings described above can be changed using this
 class's vtkWidgetEventTranslator. This class translates VTK events 
 into the vtkBoxWidget2's widget events:
 \begin{verbatim}
   vtkWidgetEvent::Select -- some part of the widget has been selected
   vtkWidgetEvent::EndSelect -- the selection process has completed
   vtkWidgetEvent::Scale -- some part of the widget has been selected
   vtkWidgetEvent::EndScale -- the selection process has completed
   vtkWidgetEvent::Translate -- some part of the widget has been selected
   vtkWidgetEvent::EndTranslate -- the selection process has completed
   vtkWidgetEvent::Move -- a request for motion has been invoked
 \end{verbatim}

 In turn, when these widget events are processed, the vtkBoxWidget2
 invokes the following VTK events on itself (which observers can listen for):
 \begin{verbatim}
   vtkCommand::StartInteractionEvent (on vtkWidgetEvent::Select)
   vtkCommand::EndInteractionEvent (on vtkWidgetEvent::EndSelect)
   vtkCommand::InteractionEvent (on vtkWidgetEvent::Move)
 \end{verbatim}

To create an instance of class vtkBoxWidget2, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkBoxWidget2
\end{verbatim}
\subsection{Methods}

The class vtkBoxWidget2 has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkBoxWidget2 class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()| -  Standard class methods for type information and printing.

\item  \verb|int = obj.IsA (string name)| -  Standard class methods for type information and printing.

\item  \verb|vtkBoxWidget2 = obj.NewInstance ()| -  Standard class methods for type information and printing.

\item  \verb|vtkBoxWidget2 = obj.SafeDownCast (vtkObject o)| -  Standard class methods for type information and printing.

\item  \verb|obj.SetRepresentation (vtkBoxRepresentation r)| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, rotation, and scaling can all be enabled and
 disabled.

\item  \verb|obj.SetTranslationEnabled (int )| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, rotation, and scaling can all be enabled and
 disabled.

\item  \verb|int = obj.GetTranslationEnabled ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, rotation, and scaling can all be enabled and
 disabled.

\item  \verb|obj.TranslationEnabledOn ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, rotation, and scaling can all be enabled and
 disabled.

\item  \verb|obj.TranslationEnabledOff ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, rotation, and scaling can all be enabled and
 disabled.

\item  \verb|obj.SetScalingEnabled (int )| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, rotation, and scaling can all be enabled and
 disabled.

\item  \verb|int = obj.GetScalingEnabled ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, rotation, and scaling can all be enabled and
 disabled.

\item  \verb|obj.ScalingEnabledOn ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, rotation, and scaling can all be enabled and
 disabled.

\item  \verb|obj.ScalingEnabledOff ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, rotation, and scaling can all be enabled and
 disabled.

\item  \verb|obj.SetRotationEnabled (int )| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, rotation, and scaling can all be enabled and
 disabled.

\item  \verb|int = obj.GetRotationEnabled ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, rotation, and scaling can all be enabled and
 disabled.

\item  \verb|obj.RotationEnabledOn ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, rotation, and scaling can all be enabled and
 disabled.

\item  \verb|obj.RotationEnabledOff ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, rotation, and scaling can all be enabled and
 disabled.

\item  \verb|obj.CreateDefaultRepresentation ()| -  Create the default widget representation if one is not set. By default,
 this is an instance of the vtkBoxRepresentation class.

\end{itemize}
