\section{vtkAffineRepresentation}

\subsection{Usage}

 This class defines an API for affine transformation widget
 representations. These representations interact with vtkAffineWidget. The
 basic functionality of the affine representation is to maintain a
 transformation matrix.

 This class may be subclassed so that alternative representations can
 be created.  The class defines an API and a default implementation that
 the vtkAffineWidget interacts with to render itself in the scene.

To create an instance of class vtkAffineRepresentation, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkAffineRepresentation
\end{verbatim}
\subsection{Methods}

The class vtkAffineRepresentation has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkAffineRepresentation class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()| -  Standard methods for instances of this class.

\item  \verb|int = obj.IsA (string name)| -  Standard methods for instances of this class.

\item  \verb|vtkAffineRepresentation = obj.NewInstance ()| -  Standard methods for instances of this class.

\item  \verb|vtkAffineRepresentation = obj.SafeDownCast (vtkObject o)| -  Standard methods for instances of this class.

\item  \verb|obj.GetTransform (vtkTransform t)| -  Retrieve a linear transform characterizing the affine transformation
 generated by this widget. This method copies its internal transform into
 the transform provided. The transform is relative to the initial placement
 of the representation (i.e., when PlaceWidget() is invoked).

\item  \verb|obj.SetTolerance (int )| -  The tolerance representing the distance to the widget (in pixels)
 in which the cursor is considered near enough to the widget to
 be active.

\item  \verb|int = obj.GetToleranceMinValue ()| -  The tolerance representing the distance to the widget (in pixels)
 in which the cursor is considered near enough to the widget to
 be active.

\item  \verb|int = obj.GetToleranceMaxValue ()| -  The tolerance representing the distance to the widget (in pixels)
 in which the cursor is considered near enough to the widget to
 be active.

\item  \verb|int = obj.GetTolerance ()| -  The tolerance representing the distance to the widget (in pixels)
 in which the cursor is considered near enough to the widget to
 be active.

\item  \verb|obj.ShallowCopy (vtkProp prop)| -  Methods to make this class properly act like a vtkWidgetRepresentation.

\end{itemize}
