\section{vtkSphereWidget2}

\subsection{Usage}

 This 3D widget interacts with a vtkSphereRepresentation class (i.e., it
 handles the events that drive its corresponding representation). It can be
 used to position a point on a sphere (for example, to place a light or
 camera), or to position a sphere in a scene, including translating and
 scaling the sphere.

 A nice feature of vtkSphereWidget2, like any 3D widget, is that it will
 work in combination with the current interactor style (or any other
 interactor observer). That is, if vtkSphereWidget2 does not handle an
 event, then all other registered observers (including the interactor
 style) have an opportunity to process the event. Otherwise, the
 vtkSphereWidget2 will terminate the processing of the event that it
 handles.

 To use this widget, you generally pair it with a vtkSphereRepresentation
 (or a subclass). Variuos options are available in the representation for
 controlling how the widget appears, and how the widget functions.

 .SECTION Event Bindings
 By default, the widget responds to the following VTK events (i.e., it
 watches the vtkRenderWindowInteractor for these events):
 \begin{verbatim}
 If the handle or sphere are selected:
   LeftButtonPressEvent - select the handle or sphere
   LeftButtonReleaseEvent - release the handle ot sphere
   MouseMoveEvent - move the handle or translate the sphere
 In all the cases, independent of what is picked, the widget responds to the 
 following VTK events:
   MiddleButtonPressEvent - translate the representation
   MiddleButtonReleaseEvent - stop translating the representation
   RightButtonPressEvent - scale the widget's representation
   RightButtonReleaseEvent - stop scaling the representation
   MouseMoveEvent - scale (if right button) or move (if middle button) the widget
 \end{verbatim}

 Note that the event bindings described above can be changed using this
 class's vtkWidgetEventTranslator. This class translates VTK events 
 into the vtkSphereWidget2's widget events:
 \begin{verbatim}
   vtkWidgetEvent::Select -- some part of the widget has been selected
   vtkWidgetEvent::EndSelect -- the selection process has completed
   vtkWidgetEvent::Scale -- some part of the widget has been selected
   vtkWidgetEvent::EndScale -- the selection process has completed
   vtkWidgetEvent::Translate -- some part of the widget has been selected
   vtkWidgetEvent::EndTranslate -- the selection process has completed
   vtkWidgetEvent::Move -- a request for motion has been invoked
 \end{verbatim}

 In turn, when these widget events are processed, the vtkSphereWidget2
 invokes the following VTK events on itself (which observers can listen for):
 \begin{verbatim}
   vtkCommand::StartInteractionEvent (on vtkWidgetEvent::Select)
   vtkCommand::EndInteractionEvent (on vtkWidgetEvent::EndSelect)
   vtkCommand::InteractionEvent (on vtkWidgetEvent::Move)
 \end{verbatim}

To create an instance of class vtkSphereWidget2, simply
invoke its constructor as follows
\begin{verbatim}
  obj = vtkSphereWidget2
\end{verbatim}
\subsection{Methods}

The class vtkSphereWidget2 has several methods that can be used.
  They are listed below.
Note that the documentation is translated automatically from the VTK sources,
and may not be completely intelligible.  When in doubt, consult the VTK website.
In the methods listed below, \verb|obj| is an instance of the vtkSphereWidget2 class.
\begin{itemize}
\item  \verb|string = obj.GetClassName ()| -  Standard class methods for type information and printing.

\item  \verb|int = obj.IsA (string name)| -  Standard class methods for type information and printing.

\item  \verb|vtkSphereWidget2 = obj.NewInstance ()| -  Standard class methods for type information and printing.

\item  \verb|vtkSphereWidget2 = obj.SafeDownCast (vtkObject o)| -  Standard class methods for type information and printing.

\item  \verb|obj.SetRepresentation (vtkSphereRepresentation r)| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, and scaling can all be enabled and disabled.

\item  \verb|obj.SetTranslationEnabled (int )| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, and scaling can all be enabled and disabled.

\item  \verb|int = obj.GetTranslationEnabled ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, and scaling can all be enabled and disabled.

\item  \verb|obj.TranslationEnabledOn ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, and scaling can all be enabled and disabled.

\item  \verb|obj.TranslationEnabledOff ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, and scaling can all be enabled and disabled.

\item  \verb|obj.SetScalingEnabled (int )| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, and scaling can all be enabled and disabled.

\item  \verb|int = obj.GetScalingEnabled ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, and scaling can all be enabled and disabled.

\item  \verb|obj.ScalingEnabledOn ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, and scaling can all be enabled and disabled.

\item  \verb|obj.ScalingEnabledOff ()| -  Control the behavior of the widget (i.e., how it processes
 events). Translation, and scaling can all be enabled and disabled.

\item  \verb|obj.CreateDefaultRepresentation ()| -  Create the default widget representation if one is not set. By default,
 this is an instance of the vtkSphereRepresentation class.

\end{itemize}
